### 2016-07-25 ms.tex
Intro sketch in ms.tex, initial references from lit review in .bib

\documentclass{emulateapj}
\usepackage{amsmath} 
\usepackage{apjfonts} 
\usepackage{amssymb} 
\usepackage{xspace}
\usepackage{hyperref} 
\usepackage{natbib} 
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsf}
\usepackage{subfigure}
\bibliographystyle{apj_ads}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\comment}[1]{{\color{red} #1}}
\newcommand{\change}[1]{{\color{blue} #1}}
\newcommand{\todo}[1]{{\bf\color{blue} #1}}
%%%%%%%%%% User defined symbol %%%%%%
\def\gsim{\gtrsim}
\def\lsim{\lesssim}    
\def\Msun{M_\odot}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document} 
\shorttitle{LensFinder}
\shortauthors{Avestruz, Li, Lightman}
\submitted{The Astrophysical Journal} 
\slugcomment{The Astrophysical Journal, submitted}

\title{LensFinder: A Strong Lensing Identification Pipeline}

\author{Camille Avestruz\altaffilmark{1-3}\thanks{E-mail:
    avestruz@uchicago.edu}, Nan Li\altaffilmark{2,3,4}, and Matthew Lightman\altaffilmark{5} }

\affil{
$^1${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^2${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^3${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.};
  \href{mailto:avestruz@uchicago.edu}{avestruz@uchicago.edu}\\
}

\keywords{cosmology: theory --- galaxies: clusters: general ---
  galaxies: clusters --- methods : numerical }

%-------------------------------------------------%
\begin{abstract} 
  Giant arcs trace... cosmology... mass distribution.  Advent of DES,
  LSST, etc. need an efficient way to identify strong lens images.  We
  present LensFinder, open source image processing and deep learning.
  Tests with mock images from ... ...  Image processing improves by....
\end{abstract}
%-------------------------------------------------%

%-------------------------------------------------%
\section{Introduction}
%-------------------------------------------------%

% Gravitational lensing as a geometric (?) test of cosmology.  Also
% probes underlying matter distribution in galaxy clusters, sensitive
% to things like recent accretion and environment.

% Arc identification can be done visually (e.g. that zooniverse
% thing).  But, in the advent of optical surveys, DES and LSST, we
% will be limited by our ability to automatically process the large
% amounts of data.

% Arc finding must optimize for completeness and purity.  Completeness
% (no false negatives), purity (minimal false positives).  Purity can
% be double checked in a smaller subsample of the data visually.  And,
% spectroscopic follow up is expensive.

% Machine learning to automate.  Previous works (StrongML),
% More+... Here, we focus on the improvement from preprocessing the
% images and describe the pipeline, which is publicly available.

% Image preprocessing.... same technology to validate watermarks

Our paper is organized as follows.  In Section~\ref{sec:methods} we
briefly describe ...  We present our results in
Section~\ref{sec:results}, and our summary and discussions in
Section~\ref{sec:conclusions}.

%-------------------------------------------------%
\section{Methodology}
\label{sec:methods}
%-------------------------------------------------%

%-------------------------------------------------%
\subsection{Image Processing Pipeline}
%-------------------------------------------------%

%-------------------------------------------------%
\subsection{Deep Learning Algorithm}
%-------------------------------------------------%

%-------------------------------------------------%
\subsection{Mock Test Images}
%-------------------------------------------------%

%-------------------------------------------------%
\section{Results}
\label{sec:results}
%-------------------------------------------------%

%-------------------------------------------------%
\section{Summary and Discussions}
\label{sec:conclusions}
%-------------------------------------------------%

We summarize key points below:

%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item

\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%

These results indicate that...

\acknowledgments CA acknowledges support from the Kavli Institute of
Cosmological Physics, the Enrico Fermi Institute at the University of
Chicago, and the University of Chicago Provost's Office.
\lastpagefootnotes

\bibliography{ms}

\end{document}

### 2016-07-28 ms.tex
Added a few more explicit points to cover in intro (2 paragraphs)

@@
 
-\title{LensFinder: A Strong Lensing Identification Pipeline}
+\title{MachLLensFinder - I: A Machine Learning Strong Lensing
+  Identification Pipeline}
 
@@
 
-\keywords{cosmology: theory --- galaxies: clusters: general ---
-  galaxies: clusters --- methods : numerical }
+\keywords{gravitational lensing --- methods : numerical --- methods: data analysis --- methods: statistical --- galaxies: elliptical --- surveys  }
 
@@
 \begin{abstract} 
+  Gravitational lensing offers a direct probe of the underlying mass
+  distribution of lensing systems, a window to the high redshift
+  universe, and a geometric probe of cosmological models.  The advent
+  of large scale surveys such as LSST and Euclid has prompted a need
+  for automatic and efficient identification of strong lensing
+  systems.  In this first paper of a series, we present LensFinderML,
+  a strong lensing identification pipeline that will be publicly
+  released as open source software.
+
 Giant arcs trace... cosmology... mass distribution.  Advent of DES,
 LSST, etc. need an efficient way to identify strong lens images.  We
-  present LensFinder, open source image processing and deep learning.
-  Tests with mock images from ... ...  Image processing improves by....
+present {\sc{MACHLLENSFINDER}} (MACHine Learning LENSFINDER), an open source
+image processing and deep learning.  This first paper focuses on image
+Processing Techniques for Giant Arc Identification Tests with mock
+images from ... ...  Image processing improves by....
 \end{abstract}
@@
 % to things like recent accretion and environment.
+Gravitational lensing deflections due to gravity... \citep[see][for a
+  review]{kneibandnatarajan_11}.  Strong lensing visible ... giant
+arcs, multiple images, and arclets.  Galaxy clusters as strong lens,
+deep gravitational potential well, can see by eye.  Strong lensing
+signatures probe underlying dark matter distribution of galaxy
+clusters, magnify the background galaxy population allowing us to
+probe formation at epochs further back in time, and geometric test of
+cosmology.
 
@@
 % will be limited by our ability to automatically process the large
-% amounts of data.
+% amounts of data.  Wide field surveys - SPT in millimeter, Herschel
+% in submillimeter; high resolution spectroscopic imaging with ALMA;
+% optical surveys DES, HSC, LSST, and Euclid (Oguri \& Marshall 2010).
+The geometric test of cosmology requires a comparison of predicted arc
+abundances and observed abundances.  In the advent of large surveys,
+such as DES and LSST, we will be limited by our ability to
+automatically process the large amounts of data and select likely
+strong lensing clusters for follow up spectroscopic measurements to
+positively identify background galaxy images.  Image identification
+has had an onslaught of new works (wc).
+
+% Serentipitous discoveries confirmed the theory (cite Einstein)
+% Cite first discoveries of different shapes of strong lensing images
+% While some serendipitous systems found recently (gladders+),
+% Describe the uptick in amount of data
+% End with need to scale with the volume of data
+Early strong lensing images were serendipitous discoveries
+(e.g. multiple quasars \citep{walsh_etal79}, arcs in clusters
+\citep{lyndsandpetrosian_86}, ...).  As the number of images with
+potential lensing systems increased, infrastructure emerged for both
+automated and visual inspection.
+
+% Image identification works: visual, ``robot'' identification -
+% ArcFinder, RingFinder..., and citizen science (space warps).
+% Many of these rely on some explicit aspect of the image's morphology (give example), filtering, ... ....
+% Specifics of the methodology how the instrument affects the strong lensing signal, and the objects of interest.
+
+Automated lensed image identification has fallen under the term
+``robot'' identification, where images are fed into some kind of image
+processing pipeline that enhances and extracts characteristic features
+as parameters that are fed into some kind of cutoff or pattern
+recognition piece.  ArcFinder
+... .... \citep{seidelandbartelmann_07}. For multiply imaged quasars,
+Ringfinder ... ... ...\citep{gavazzi_etal14}.  Each pipeline
+.... ... and relies on the image morphology where ... ...  Note, that
+the method best applied to ... ... and the objects of interest.  The
+human eye is one of the best discriminators of.... SpaceWarps is an
+example of citizen science... visual identification
+\citep{marshall_etal16,more_etal16}.  However, scalability, training
+....
 
@@
 % be double checked in a smaller subsample of the data visually.  And,
-% spectroscopic follow up is expensive.
+% spectroscopic follow up is expensive.  Also, scalability of the
+% strong lens finding method matters - example with the citizen
+% science.
+In general, lensed image finding must optimize for completeness and
+purity.  In the application of arc abundance comparisons with
+cosmological predictions, completeness is important; we must be able
+to understand the reasons and frequency of false negatives.  Since
+spectroscopic confirmation of background lensed images is expensive,
+purity is key; we must minimize false positives that would waste
+follow up telescope time.
 
@@
 % images and describe the pipeline, which is publicly available.
+% Depending on the image type, different preprocessing is likely
+% necessary (rings, multiply lensed quasars, etc.) Our goal is to
+% create an open source pipeline that is general enough for the user
+% to select or add appropriate image processing techniques to augment
+% the features of the lensed image, train and test data with different
+% machine learning techniques, and to select the sequence of methods
+% that maximizes completeness with optimal purity.
 
-% Image preprocessing.... same technology to validate watermarks
+% No need to explicitly extract morphological parameters to a pattern
+% finding, simply transform the image according to the appropriate
+% image preprocessing function, and directly feed this into the
+% machine learning ...
+
+% This is the first in a series of LensFinder papers where we present
+% our initial pipeline results with a test... of .... Image
+% preprocessing.... same technology to validate watermarks
 

### 2016-08-04 ms.tex
Latest changes, some new sketch in Methodology section.

@@
 %-------------------------------------------------%
+\subsubsection{Histogram Oriented Gradients}
+%-------------------------------------------------%
+Histogram oriented gradients (HOG) is a feature extraction method that
+computes centered horizontal and vertical gradients with no smoothing.
+Originally created for human detection, .... This computes the
+gradient orientation and magnitudes in an image by first dividing the
+image into $n\times n$ blocks of X\% overlap.  The gradient
+orientation is then quantized into m bins. ``(optional) global image
+normalisation computing the gradient image in x and y computing
+gradient histograms normalising across blocks flattening into a
+feature vector''\citep{dalalandtriggs_05}.
+
+% Need to look into edge orientation histograms, scale-invariant
+% feature transform descriptors, shape contexts.
+
+% NEED TO FEED THE DESCRIPTORS TO SOMETHING WITH SUPERVISED LEARNING.
+% (e.g. SVM, Neural network).
+
+%-------------------------------------------------%
+\subsection{Logistic Regression}
+%-------------------------------------------------%
+
+% Regularization coefficient:
+% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html
+
+%-------------------------------------------------%
 \subsection{Deep Learning Algorithm}

### 2016-11-05 ms.tex
added grid search results

@@
 
+**Results of Grid search across the parameters of the pipeline**
+
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
+%-------------------------------------------------%
+\subsection{Optimized pipeline parameters}
+%-------------------------------------------------%
+
+\begin{table}
+\caption{Grid Search of Pipeline Parameters}
+\begin{center}
+\begin{tabular}{cccccc}
+\hline \\ [-0.2cm]
+N$_{orient}$ & Pixels/Cell & Cells/Block & LogReg$_{\text{coeff}}$ & HOG size & Score \\ [0.2cm]
+\hline \\ [-0.2cm]
+\multicolumn{6}{c}{(a) HST-like data} \\ [0.2cm]
+\hline \\ [-0.2cm]
+9 & (4, 4) & (3, 3) & 50. & &$0.76181\pm0.00491$\\ [0.2cm]
+9 & (4, 4) & (1, 1) & 50. & &$0.83403\pm0.00547$\\ [0.2cm]
+9 & (8, 8) & (3, 3) & 50. & &$0.85417\pm0.00851$\\ [0.2cm] 
+9 & (8, 8) & (1, 1) & 50. & &$0.86389\pm0.00687$\\ [0.2cm] 
+9 & (16, 16) & (1, 1) & 50. & & $0.88542\pm0.00680$ \\ [0.2cm]
+9 & (16, 16) & (3, 3) & 10. & &$0.89306\pm0.00687$ \\ [0.2cm]
+8 & (16, 16) & (3, 3) & 50. & &$0.90000\pm0.00170$ \\ [0.2cm]
+9 & (16, 16) & (3, 3) & 50. & &$0.90139\pm0.00804$ \\ [0.2cm]
+\hline \\ [-0.2cm]
+\multicolumn{6}{c}{(b) LSST-like data} \\ [0.2cm]
+\hline \\ [-0.2cm]
+& & & & &\\
+& & & & &\\ [0.2cm]
+\hline
+\end{tabular}
+\end{center}
+\label{tab:gridsearch}
+\tablecomments{Panel (a) shows the results of a grid search across a
+  range of HOG parameters and regression coefficient with training and
+  test sets of size 1440 with the HST-like mock dataset.  Panel (b)
+  shows the corresponding results for training and test sets of size
+  5760 with the LSST mock dataset.  We explore different HOG
+  parameters in each dataset due to resolution and image size
+  differences.}
+\end{table}
+
+We run a grid search across parameters that should reasonably sample
+the arc edges in either the HST- or LSST-like mock observations.
+Recall, the HST-like images are $300\times300$ pixels per image, while
+the LSST-like mock observations are $45\times45$ pixels per image.  In
+general, must run a grid search in order to best optimize the pipeline
+parameters.
+
+We must first estimate the size of a cell that will contain a coherent
+arc feature.  To first order approximation, subdivisions of cells that
+are 1/100th the area of the entire image should contain coherent arc
+edges that span an elongated shape within arc-containing cells.
+Therefore, we perturb the pixels per cell parameter about (30, 30) for
+the HST-like images, and (4, 4) for the LSST-like images.
+
+Next, the cells per block parameter determines the normalization of
+each cell with respect to the neighboring cell.  In general, this will
+downweight arc-like edges in cells that neighbor very bright cells,
+such as cells that cover the BCG.  We therefore vary the cells per
+block parameter between (1, 1) and (3, 3).
+
+The number of orientations will determine the sampling of rounded
+edges.  For example, if we only have two orientations, an arc-like
+feature in a cell will appear as .... However, contributions from a
+cluster or line-of-sight galaxy in the same cell will ... the
+normalizations in the histogram.  The resolution of the overall image
+will also limit the additional information that an increase in
+$N_\text{orientations}$ will provide.  For the LSST-like data,
+$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$ only
+results in a $???\%$ improvement.  In the case of the HST-like data,
+$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$
+results in a $???\%$ improvement.
+
+Note, we also include the size of the extracted features, e.g. the
+length of the HOG.  Larger features will increase the amount of time
+required to train a model, and also impact memory restrictions on the
+size of the training set.  The logistic regression coefficient will
+also increase the training time.  We discuss the score dependence on
+logistic regression coefficient in Section\ref{sec:unregularizedfit}.
+
+\subsection{Scores vs. regularization on larger train/test set with comparable grid search in parameterization}\label{sec:unregularizedfit}
+
+\subsection{False positives/negatives and why... something about likely images given cosmology}
+
+\subsection{ROC curve}
+
+\subsection{Effects of BCG contamination}
 

### 2016-11-07 ms.tex
More text in results added

@@
 \author{Camille Avestruz\altaffilmark{1-3}\thanks{E-mail:
-    avestruz@uchicago.edu}, Nan Li\altaffilmark{2,3,4}, and Matthew Lightman\altaffilmark{5} }
+    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, and Matthew Lightman\altaffilmark{5} }
 
@@
 $^2${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
-$^3${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.};
+$^3${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.};\\
+$^4${High Energy Physics Division, Argonne National Laboratory,
+Lemont, IL 60439};\\
+$^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
   \href{mailto:avestruz@uchicago.edu}{avestruz@uchicago.edu}\\
@@
   universe, and a geometric probe of cosmological models.  The advent
-  of large scale surveys such as LSST and Euclid has prompted a need
-  for automatic and efficient identification of strong lensing
-  systems.  In this first paper of a series, we present LensFinderML,
-  a strong lensing identification pipeline that will be publicly
-  released as open source software.
+  of large scale surveys such as the Large Synoptic Sky Telescope and
+  Euclid has prompted a need for automatic and efficient
+  identification of strong lensing systems.  In this first paper of a
+  series, we present LensFinderML, a strong lensing identification
+  pipeline that will be publicly released as open source software.
 
@@
 LSST, etc. need an efficient way to identify strong lens images.  We
-present {\sc{MACHLLENSFINDER}} (MACHine Learning LENSFINDER), an open source
-image processing and deep learning.  This first paper focuses on image
-Processing Techniques for Giant Arc Identification Tests with mock
-images from ... ...  Image processing improves by....
+present {\sc{MACHLLENSFINDER}} (MACHine Learning LENSFINDER), an open
+source image processing and deep learning.  This first paper focuses
+on image Processing Techniques for Giant Arc Identification Tests with
+mock images from the Hubble Space Telescope and LSST.  Image
+processing improves by....
 \end{abstract}
@@
 %-------------------------------------------------%
-\subsection{Image Processing Pipeline}
+\subsection{Mock Images}
 %-------------------------------------------------%
 
-**Results of Grid search across the parameters of the pipeline**
+% Summary of HST and LSST images
+We use mock {\em Hubble Space Telescope} (HST) and {\em Large Synoptic
+  Sky Telescope} (LSST) images generated with PICS (Pipeline for
+Images of Cosmological Strong lensing) \citep{li_etal16}.  These
+images include cluster-member galaxies and foreground stars.  Half of
+the images used are strong lensing systems.  Here, lensed galaxy
+images are ray-traced images of actual galaxies extracted from deep
+Hubble Space Telescope observations.  The final mock images are
+``observed'' with a realistic point spread function corresponding to
+modeled detector artifacts for bright stars.  See \cite{li_etal16} for
+more details.
+
+Figure ~\ref{fig:mockimages} illustrates a sample mock lensed and
+unlensed images from each telescope.  From left to right, the top
+panel images respectively correspond to a mock HST lensing and
+non-lensing system. The mock HST images are $n_\text{pix}\times
+n_\text{pix}=300\times300$ in size.  For the HST-like dataset, many
+giant arcs are visually obvious.
+
+The bottom panel images respectively correspond to a mock LSST lensing
+and non-lensing system.  These images are $n_\text{pix}\times
+n_\text{pix}=45\times45$.  The ground based noise and limited
+resolution of the LSST-like dataset make visual giant arc
+identification difficult.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]\label{fig:mockimages}
+\begin{center}
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1_color.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_9_lensed_imgs_1_color.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/lsst_9_unlensed_imgs_1_color.pdf}
+\caption{Top panel: Example mock HST images, with $n_\text{pix}\times
+  n_\text{pix}=300\times300$.  The left corresponds to a strong
+  gravitational lensing system with a visibly obvious giant arc.  The
+  right corresponds to a non-lensing system.  Bottom panel: Example
+  mock LSST images, with $n_\text{pix}\times n_\text{pix}=45\times45$.
+  The resolution and noise of a ground based telescope is noticeably
+  worse.  The left corresponds to a strong gravitational lensing
+  system, and the right to a non-lensing system.  However, visual
+  identification of giant arcs in the LSST images is very difficult.}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %-------------------------------------------------%
-\subsubsection{Histogram Oriented Gradients}
+\subsection{Strong Arc Lensing Identification Pipeline}
+%-------------------------------------------------%
+
+To perform our analysis, we have used a variety of tools from {\em
+  Scikit-learn} \citep{pedregosa_etal12}.  We outline the
+identification pipeline in Figure~\ref{fig:pipeline}.  The first step
+of our pipeline consists of a feature extraction stage, where our
+feature vector is a {\em histogram of oriented gradients}
+\citep{dalalandtriggs_05}.  We describe the method in
+Section~\ref{sec:hog}.  We then use a machine learning algorithm to
+train a classifier model on a subset of our images.  We have explored
+both {\em Logistic Regression} (LR) and {\em Support Vector Machine}
+(SVM) machine learning algorithms.  We test our trained model on an
+independent subset of the images to assess the model performance.
+
+Both the feature extrator, HOG, and the classifier contain a range of
+parameters, which must be tested and optimized for peak model
+performance.  We use {\em GridSearchCV} from {\em Scikit-learn} to
+select appropriate parameters, and discuss these results in
+Section~\ref{sec:gridsearch}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:pipeline}
+\begin{center}
+\includegraphics[scale=0.55]{figures/supervised_classification_workflow.png}
+\caption{** Cartoon of pipeline ** Mention that median filtering generates
+visual artifacts that confuse the model. http://www.nltk.org/book/ch06.html}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
+\subsection{Feature Extractor: Histogram Oriented Gradients}\label{sec:hog}
 %-------------------------------------------------%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]\label{fig:hogvisual}
+\begin{center}
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\hspace{-20pt}
+\caption{Visualized HOG feature vectors of the sample lensed HST-like
+  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
+  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
+  and (1, 1) cells per block.  Right: The HOG visualization of the
+  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
+  and (1, 1) cells per block.  Note, fewer pixels per cell will better
+  resolve the arc feature.  The brightest lines align with prominent
+  edges.}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %-------------------------------------------------%
-\subsection{Logistic Regression}
+\subsection{Machine Learning Algorithm: Logistic Regression}
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-\subsection{Deep Learning Algorithm}
+\subsection{Machine Learning Algorithm: Support Vector Machine}
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-\subsection{Mock Test Images}
+%\subsection{Deep Learning Algorithm}
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-\subsection{Optimized pipeline parameters}
+\subsection{Optimized pipeline parameters}\label{sec:gridsearch}
 %-------------------------------------------------%
@@
 \hline \\ [-0.2cm]
-N$_{orient}$ & Pixels/Cell & Cells/Block & LogReg$_{\text{coeff}}$ & HOG size & Score \\ [0.2cm]
+N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & HOG size & Score \\ [0.2cm]
 \hline \\ [-0.2cm]
@@
 will also limit the additional information that an increase in
-$N_\text{orientations}$ will provide.  For the LSST-like data,
-$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$ only
+$N_\text{orient}$ will provide.  For the LSST-like data,
+$N_\text{orient}=9$ compared with $N_\text{orient}=5$ only
 results in a $???\%$ improvement.  In the case of the HST-like data,
-$N_\text{orientations}=9$ compared with $N_\text{orientations}=5$
+$N_\text{orient}=9$ compared with $N_\text{orient}=5$
 results in a $???\%$ improvement.
@@
 Note, we also include the size of the extracted features, e.g. the
-length of the HOG.  Larger features will increase the amount of time
-required to train a model, and also impact memory restrictions on the
-size of the training set.  The logistic regression coefficient will
-also increase the training time.  We discuss the score dependence on
-logistic regression coefficient in Section\ref{sec:unregularizedfit}.
+length of the HOG feature vector.  A longer feature vector will
+increase the amount of time required to train the model.
+Additionally, for fixed memory restrictions, there is a tradeoff
+between the length of the feature vector and the size of the training
+set.  The logistic regression coefficient will also increase the
+training time, \todo{since larger coefficients correspond to a more
+  singular matrix}.  We discuss the score dependence on logistic
+regression coefficient in Section\ref{sec:unregularizedfit}.
 
-\subsection{Scores vs. regularization on larger train/test set with comparable grid search in parameterization}\label{sec:unregularizedfit}
+%-------------------------------------------------%
+\subsection{Effects of Regularization on Model Performance}\label{sec:unregularizedfit}
+%-------------------------------------------------%
 
-\subsection{False positives/negatives and why... something about likely images given cosmology}
+% Scores vs. regularization on larger train/test set with comparable
+% grid search in parameterization
 
-\subsection{ROC curve}
+%-------------------------------------------------%
+\subsection{Failed identifications}
+%-------------------------------------------------%
 
+%-------------------------------------------------%
+\subsection{Receiver Operatic Characteristic}
+%-------------------------------------------------%
+
+In this section, we discuss the Receiver Operating Characteristic
+(ROC) curve, which shows the true positive rate as a function of false
+positive rate for a given model and test set.  The true positive rate
+is defined as the number of true positives divided by the total number
+of positives (completeness of the positive identifications).  The
+false positive rate is defined as the number of false positives
+divided by the total number of negatives (impurity of the
+identifications).  The ROC curve illustrates the performance of our
+trained model as we vary the discrimination threshold.
+
+The classifier model assigns a score to each test image, which is a
+probability that the image is a strong lensing system.  To construct
+the ROC curve, the test images are ranked by probability and the
+discrimination threshold varied.
+
+For very high discrimination threshold, we have maximal purity, but a
+low completeness (bottom left region of the ROC).  FOr a very low
+discrimination threshold, we have maximal completeness, but minimal
+purity (top right region of the ROC).  The ideal model would have a
+data point on the ROC curve that sits on the top left corner,
+i.e. $(x, y) = (0, 1)$.
+
+In the context of strong lensing systems, we wish to maximize the true
+positive rate so we have a representative count of the fraction of
+strong lensing systems in an observed volume of the universe.  We also
+want to minimize the false positive rate.  Positively identified
+strong lensing systems will require expensive spectroscopic follow-up
+for validation.  The steepness of the ROC curve indicates how well the
+model will optimize the two, and we can characterize the steepness by
+the area under the curve (AUC).  A perfect model would have an AUC of
+1, with data points along $(x=0, 0\leq y\leq1)$, and $(0\leq x\leq 1,
+y=1)$.
+
+Figure~\ref{fig:ROC} shows the \todo{ROC curve for XYZ(???) models,
+with the AUC value indicated in the legend.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:ROC}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/ROC.pdf}
+\caption{ROC curve for a model trained on the HST-like data with the
+  Logistic Regression algorithm.  Here, we use the parameters: CPB=(1,
+  1), $N_\text{orien}=9$, PPC=(16, 16), $C_\text{reg}=100.$.  The AUC
+  is 0.966.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
 \subsection{Effects of BCG contamination}
+%-------------------------------------------------%
+
+Previous works to identify strong lensing systems have often removed
+the BCG from images to better identify lensed galaxies.  Here, we
 

### 2016-11-10 ms.tex
added more text to results, particularly in the ROC curve

@@
   same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
-  and (1, 1) cells per block.  Note, fewer pixels per cell will better
-  resolve the arc feature.  The brightest lines align with prominent
-  edges.}
+  and (1, 1) cells per block.  The brightest lines align with
+  prominent edges.  Note, while fewer pixels per cell will better
+  resolve the arc feature, the ``edge'' corresponding to the arc is
+  less prominent.  }
 \end{center}
@@
 %-------------------------------------------------%
-\subsection{Machine Learning Algorithm: Logistic Regression}
+\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:logreg}
 %-------------------------------------------------%
+
+Logisitic regression is a linear classifier, which finds the optimal
+hyperplane between two classes of data points.  This hyperplane
+defines the optimal model.  We must regularize the model to prevent
+overfitting.
+
+In regularization, the goal is to minimize a cost function with
+respect to ....  Larger values of $C_\text{LogReg}$ correspond to
+increasing model complexity.  Figure~\ref{fig:regularization} shows
+the accuracy of a model for selected HOG parameters as a function of
+the regularization parameter, $C_\text{LogReg}$.  We plot the
+regularization dependency for HOG parameterization of
+$N_\text{orient}=9$, $PPC=(16, 16)$, $CPB=(1,1)$.
+
+The accuracy of a model can be defined as either the score of the
+model on a test set, or the AUC for the ROC curve.
 
@@
 %-------------------------------------------------%
-\subsection{Effects of Regularization on Model Performance}\label{sec:unregularizedfit}
-%-------------------------------------------------%
-
-% Scores vs. regularization on larger train/test set with comparable
-% grid search in parameterization
-
-%-------------------------------------------------%
-\subsection{Failed identifications}
-%-------------------------------------------------%
-
-%-------------------------------------------------%
 \subsection{Receiver Operatic Characteristic}
@@
 
-Figure~\ref{fig:ROC} shows the \todo{ROC curve for XYZ(???) models,
-with the AUC value indicated in the legend.}
+Figure~\ref{fig:ROC} shows the ROC curves for three different HOG
+parameterizations for the HST-like dataset in red, green, and blue.
+The parameters and corresponding AUC for each curve are labeled in the
+legend.  The models for the HST-like dataset perform well, and have
+AUCs very close to 1.  On the other hand, the model for our LSST-like
+dataset does not perform well.  The dashed diagonal like corresponds
+to a model that is as good as a random classifier, e.g. a coin-flip
+for each test image.  The LSST-like ROC curve does marginally better,
+and the $AUC=0.527$ is within the statistical noise of the sample.
+
+We train the model corresponding to each curve with the logistic
+regression regularization parameter, $C_\text{LogReg}$, that best
+describes the training dataset without overfitting.  We discuss the
+choice of regularization parameter in
+Section~\ref{sec:regularizedfit}.
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/ROC.pdf}
-\caption{ROC curve for a model trained on the HST-like data with the
-  Logistic Regression algorithm.  Here, we use the parameters: CPB=(1,
-  1), $N_\text{orien}=9$, PPC=(16, 16), $C_\text{reg}=100.$.  The AUC
-  is 0.966.}
+\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
+\caption{Red, green, blue: ROC curves for a models trained on the
+  HST-like data with the Logistic Regression algorithm.  The magenta
+  shows the ROC curve for the LSST-like data.  The corresponding
+  parameters are labeled, N for number of orientations, ppc for
+  pixels-per-cell, cpb for cells-per-block, and C for best
+  regularization parameter.  }
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
+\subsection{Effects of Regularization on Model Performance}\label{sec:regularizedfit}
+%-------------------------------------------------%
+
+% Logistic regression and regularization
+As described in Section~\ref{sec:logreg}, logistic regression trains a
+model with complexity determined by the regularization parameter.  The
+regularization parameter ultimately defines the model performance.
+Figure~\ref{fig:regularization} shows the model performance as a function of
+regularization parameter.
+
+% Scores vs. regularization on larger train/test set with comparable
+% grid search in parameterization
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:regularization}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
+\caption{}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
+\subsection{Failed identifications}\label{sec:failedids}
+%-------------------------------------------------%
 

### 2016-11-12 ms.tex
Added stubs for noBCG and FalseIDs subsections

@@
 \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
 \caption{Visualized HOG feature vectors of the sample lensed HST-like
@@
 As described in Section~\ref{sec:logreg}, logistic regression trains a
-model with complexity determined by the regularization parameter.  The
-regularization parameter ultimately defines the model performance.
-Figure~\ref{fig:regularization} shows the model performance as a function of
-regularization parameter.
+model with complexity determined by the regularization parameter,
+$C_\text{LogReg}$.  Increasing model complexity (larger
+$C_\text{LogReg}$), will better describe features in the training
+set[wc?].  However, an overly complex model will overfit the training
+set at the expense of its performance on any independent test set.
+The regularization parameter ultimately defines the model performance,
+and we must perform a parameter search to identify the optimal value
+for $C_\text{LogReg}$.
+
+Figure~\ref{fig:regularization} shows the model performance as a
+function of regularization parameter.  The left panel shows the
+accuracy, or score, of the model as a function of regularization
+parameter.  The right panel shows the AUC of the model as a function
+of regularization parameter.  The solid and dotted lines respectively
+correspond to the model performance on the test and training set.
+
+For either characterization of the model, the model performance on the
+training set increases and asymptotes with $C_\text{LogReg}$.  With
+increasing model complexity, the model better fits the data set it has
+been trained on.  This is analogous to fitting a seventh order
+polynomial to seven data points, where the fitting function will go
+through every point.
+
+EDITING HERE
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:regularization}
+\begin{figure*}[t]\label{fig:regularization}
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
-\caption{}
+\includegraphics[width=\columnwidth]{figures/regularized_accuracy.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/regularized_AUC.pdf}
+\caption{Left: Accuracy of the model with varying regularization.
+  Each color corresponds to a model trained for features extracted
+  with a different set of HOG parameters.  The dotted (solid) lines
+  show the performance of the model on the training (test) set.
+  Right: AUC of the model with varying regularization.  Linestyles and
+  colors are similar to those in the left panel.  AUC is a better
+  characterization of model performance, since the accuracy is
+  determined for fixed classification threshold [wc?], but peak model
+  performance can occur at a different classification threshold.}
 \end{center}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+The best ROC curve, HST:N5ppc32cpb4C100, illustrates that we can lower
+the classification threshold and improve the true positive rate by
+$\sim10\%$ and sacrifice an increase in false positive rate by
+$\lsim5\%$.  In this section, we examine the ``borderline'' images,
+which transition from negative classification to positive calculation
+in the steepest part of the AUC curve.  Borderline images correspond
+to candidates for spectroscopic follow-up.  The model is less
+confident about this subset of images, and these would therefore be
+good candidates for follow-up human classification and/or
+spectroscopic follow-up (CITE HERE???).
+
+\todo{Figure ~\ref{fig:falseids} shows a random sample of 10 borderline
+images.  Common features...????}
+
 %-------------------------------------------------%
@@
 
-Previous works to identify strong lensing systems have often removed
-the BCG from images to better identify lensed galaxies.  Here, we
+Previous works to identify strong lensing systems have often modeled
+out the BCG from images to better identify lensed images (???CITE
+HERE???).  Here, we test the effects of the BCG by training and
+testing models on mock data where the BCG has not been included.  By
+construction, these results show the maximal improvement that can be
+obtained from BCG subtraction.
+
+Figure~\ref{fig:ROCnobcg} shows the \todo{ROC curve for models of HOG
+  feature vectors of mock data with no BCG.  The feature vectors are
+  the same HOG parameters as in Figure~\ref{fig:ROC} }.  \todo{The
+  grid search over parameter space was similar to that for data with
+  the BCG.}
+
+???????
 

### 2016-12-16 ms.tex
added Nan's section on simulated images for training/testing set

@@
 \newcommand{\comment}[1]{{\color{red} #1}}
-\newcommand{\change}[1]{{\color{blue} #1}}
+\newcommand{\change}[1]{{\it\color{purple} #1}}
 \newcommand{\todo}[1]{{\bf\color{blue} #1}}
@@
 distribution of lensing systems, a window to the high redshift
-  universe, and a geometric probe of cosmological models.  The advent
-  of large scale surveys such as the Large Synoptic Sky Telescope and
-  Euclid has prompted a need for automatic and efficient
-  identification of strong lensing systems.  In this first paper of a
-  series, we present LensFinderML, a strong lensing identification
-  pipeline that will be publicly released as open source software.
-
-Giant arcs trace... cosmology... mass distribution.  Advent of DES,
-LSST, etc. need an efficient way to identify strong lens images.  We
-present {\sc{MACHLLENSFINDER}} (MACHine Learning LENSFINDER), an open
-source image processing and deep learning.  This first paper focuses
-on image Processing Techniques for Giant Arc Identification Tests with
-mock images from the Hubble Space Telescope and LSST.  Image
-processing improves by....
+universe, and a geometric probe of cosmological models.  The advent of
+large scale surveys such as the Large Synoptic Sky Telescope and
+Euclid has prompted a need for automatic and efficient identification
+of strong lensing systems.  We present \change{LensFinderML}, a strong
+lensing identification pipeline that will be publicly released as open
+source software.  In this first application, we employ a fast feature
+extraction method, Histogram of Oriented Gradients (HOG), to capture
+edge features that are characteristic of strong gravitational arcs.
+We use logistic regression to train a supervised classifier model on
+the HOG of \change{HST- and LSST}-like images.  Our best performing
+models reach a completeness rate of \change{XX\%} and purity rate of
+\change{XX\%} for an HST-like sample.  However, for one orbit of LSST,
+our model cannot distinguish between strong lensing systems and
+non-strong lensing systems.  In absence of the brightest cluster
+galaxy in LSST-like data, our trained model reaches a completeness of
+\change{XX\%} and purity of \change{XX\%}.  Our results show one the
+most efficient and effective methods for automated strong lensing
+identification in space-based surveys.  The results also emphasize the
+need for further development and testing of additional tools to
+exploit[wc?]  ground-based surveys.
 \end{abstract}
@@
 %-------------------------------------------------%
+\subsection{Creating Simulated Images for Training Set and Testing Set}
+
+We use mock Hubble Space Telescope (HST) and Large Synoptic Sky
+Telescope (LSST) images generated with PICS (Pipeline for Images of
+Cosmological Strong lensing) (Li et al. 2016) and LensPOP (Thomas
+Colletti 2013) as training set and testing set. In these images, the
+lensed images include the images of lens galaxies, lensed images, and
+galaxies on the line of sight; the unlensed images include the images
+of lens galaxies and the galaxies on the line of sight.
+
+To produce simulated lensed galaxies, we first set mass models of the
+lenses to be the Singular Isothermal Ellipsoid (SIE):
+
+\begin{equation}
+\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}}.
+\end{equation}
+
+Where, $\theta_{\rm E}$ is the Einstein Radius, $q$ is axis
+ratio. Einstein radius can be calculated according to the redshift of
+the lens, the redshift of the source, and the velocity dispersion of
+the lens galaxy.
+\begin{equation}
+\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
+\end{equation}
+where, $c$ is the speed of light, $\sigma_v$ is the velocity
+dispersion of the lens galaxy, $D_{ls}$ and $D_{s}$ are the angular
+diameter distance from the source plane to the lens plane and from the
+source plane to the observer separately.
+
+To rotate the lenses with a random orientation angles, we adopt the
+transformation below:
+
+\begin{eqnarray}
+\label{eq:rotation}
+\begin{bmatrix}
+
+    x_{1}\prime      \\
+    x_{2}\prime 
+\end{bmatrix}
+= 
+\begin{bmatrix}
+    \cos \phi  &  -\sin \phi      \\
+    \sin \phi  &  ~\cos \phi      
+\end{bmatrix} 
+\begin{bmatrix}
+    x_1      \\
+    x_2      
+\end{bmatrix} .
+\end{eqnarray}
+
+$\phi$ is the orientation angle.  According to above equations, we
+need $\sigma_v$, $q$, $\phi$, redshift of the lens $z_l$, and redshift
+of the source $z_s$ to derivative the lensing maps completely.
+Velocity dispersion, ellipticity, and orientation are randomly chosen
+from typical ranges of a galaxy, where $\sigma_v = [200, 320] km/s$,
+$q = [0.5, 1.0]$, and $\phi = [0, 360]$. The redshift of the lens is
+fixed at $z_l = 0.2$, and the redshift of the source is fixed at $z_s
+= 1.0$. The images of source galaxies are extracted from the CANDELS
+survey. We selected 33 bright galaxies, and relocated them to
+projected positions, which are close to the caustic of the lensing
+system, and the projected position of the lens is fixed in the center
+of the field of view of each image. Once we have the lens, source, and
+the parameters of the image simulation, i.e., $300 \times 300 {\rm
+  pixels}^2$ and 0.03 arcsec per pixel per side, settled, the lensed
+images can be produced by performing ray-tracing simulations.
+
+The light distributions of the lens galaxies  are modeled as the elliptical Sersic profile,
+
+\begin{equation}
+I(R) = I_{\rm eff}~{\rm exp} \left\lbrace -b_{n} \left[ \left(
+  \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ] \right\rbrace
+\end{equation}
+
+Where, $R = \sqrt[]{x_1^2 /q+x_2^2 q }$, $R_{\rm eff}$ is the
+effective radius in units of arcsecond, $I_{\rm eff}$ is the intensity
+at the effective radius, $n$ is the index of the Sersic profile, $q$
+is the ellipticity, and We perform the similar transformation as
+Eq. \ref{eq:rotation} to orient the sources.  We assume that the
+distribution of light is following that of mass, so ellipticity and
+orientation are the same as the SIE model. Matching the velocity
+dispersion with the COSMOS morphological
+catalog \footnote{\url{https://arxiv.org/pdf/1501.04977v2.pdf}}, we
+assign effective radius, effective luminosity, and index to the light
+profile.  We also assume the light center is on top of the mass
+center, the noiseless images of lenses can be drawn. The galaxies on
+the line of sight are constructed by cutting light-cones from the
+Hubble Ultra Deep Field.  Stacking all these images together and
+collaborating the magnitude of each component, we create primarily
+simulated lensed images.
+
+The final part is mock observing. To produce HST-like images, we do
+not need to do anything further than stacking and magnitude
+calibrating, because noise and PSF are involved when we are extracting
+galaxies on the line of sight. To produce LSST-like images, we perform
+re-binning, convolving with PSF, and adding noise serially; this
+process is implemented in LensPop. We created single-epoch-LSST-like
+images and stacked -LSST-like images for investigating the performance
+and usability of our pipeline in LSST data. Figure 2.1 illustrates a
+sample mock lensed and unlensed images from each telescope. From left
+to right, the top panel images respectively correspond to a mock HST
+lensing and non-lensing system. The mock HST images are 300 × 300 in
+size, and the pixel size is 0.03 arcsecond. For the HST-like data-set,
+many giant arcs are visually obvious. The middle panel images
+respectively correspond to a mock single-epoch LSST lensing and
+non-lensing systems. The bottom panel images respectively correspond
+to a mock stacked LSST lensing and non-lensing systems. These images
+are 45 × 45; the pixel size is 0.2 arcsecond. The ground based noise,
+PSF, and limited resolution of the LSST-like data-set make visual
+giant arc identification difficult. But when in the stacked LSST
+images, the quality is better, because more data improves the signal
+to noise ratio better.
+
+In the training sets, we also generate unlensed images, the procedure
+is similar to mock lensed images but getting rid of the part of
+ray-tracing. 10000 lensed images and 10000 unlensed images are merged
+to construct one training set. Furthermore, for investigating the
+influence of BCG galaxies on the performance of our lens
+identification pipeline in LSST data, we build another training sets
+of the images without BCG galaxies.
 
@@
 
+% HST model performance
 Figure~\ref{fig:ROC} shows the ROC curves for three different HOG
@@
 legend.  The models for the HST-like dataset perform well, and have
-AUCs very close to 1.  On the other hand, the model for our LSST-like
-dataset does not perform well.  The dashed diagonal like corresponds
-to a model that is as good as a random classifier, e.g. a coin-flip
-for each test image.  The LSST-like ROC curve does marginally better,
-and the $AUC=0.527$ is within the statistical noise of the sample.
+AUCs very close to 1.
 
-We train the model corresponding to each curve with the logistic
+% LSST model performance
+On the other hand, the model for our LSST-like dataset (solid magenta)
+does not perform well.  The dashed diagonal like corresponds to a
+model that is as good as a random classifier, e.g. a coin-flip, for
+each test image.  The LSST-like ROC curve does marginally better, and
+the $AUC=0.527$ is within the statistical noise of the sample.
+
+% No BCG LSST
+One possible method of improving the detection of strong lensing
+systems is to model out the BCG.  The dotted magenta ROC curve
+corresponds to a model trained and tested on LSST-like data where the
+BCG has not been added to the mock image.  This model results in an
+AUC of 0.64, performing better than random.  In other words, if we
+were to perfectly model out the BCG contribution in LSST-like data, we
+could improve the performance by $\sim10\%$.
+
+% Choosing C
+The ROCs correspond to models that have been trained with logistic
 regression regularization parameter, $C_\text{LogReg}$, that best
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:ROC}
+\begin{figure}[t]\label{fig:ROCHST}
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
+\includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
 \caption{Red, green, blue: ROC curves for a models trained on the
   HST-like data with the Logistic Regression algorithm.  The magenta
-  shows the ROC curve for the LSST-like data.  The corresponding
-  parameters are labeled, N for number of orientations, ppc for
-  pixels-per-cell, cpb for cells-per-block, and C for best
-  regularization parameter.  }
+  solid (dotted) curve show the ROC curve for the LSST-like data with
+  (without) the BCG.  The corresponding parameters are labeled: N for
+  number of orientations, ppc for pixels-per-cell, cpb for
+  cells-per-block, and C for best regularization parameter.  The AUC
+  for each model is also labeled in the legend, where an AUC close to
+  1 is a near-ideal model, and an AUC close to 0.5 is a model that
+  performs as well as a coin-flip.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:ROCLSST}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/ROC_LSST_HOG.png}
+\caption{Red, green, blue: ROC curves for a models trained on the
+  HST-like data with the Logistic Regression algorithm.  The magenta
+  solid (dotted) curve show the ROC curve for the LSST-like data with
+  (without) the BCG.  The corresponding parameters are labeled: N for
+  number of orientations, ppc for pixels-per-cell, cpb for
+  cells-per-block, and C for best regularization parameter.  The AUC
+  for each model is also labeled in the legend, where an AUC close to
+  1 is a near-ideal model, and an AUC close to 0.5 is a model that
+  performs as well as a coin-flip.}
 \end{center}
@@
 
+%  Our running over C - score and AUC as characterizations
 Figure~\ref{fig:regularization} shows the model performance as a
@@
 accuracy, or score, of the model as a function of regularization
-parameter.  The right panel shows the AUC of the model as a function
-of regularization parameter.  The solid and dotted lines respectively
+parameter.  The accuracy is simply the percentage of correct
+predictions, true positives and true negatives, out of a given set.
+The right panel shows the AUC of the model as a function of
+regularization parameter.  The solid and dotted lines respectively
 correspond to the model performance on the test and training set.
 
+% Training behavior with C
 For either characterization of the model, the model performance on the
@@
 increasing model complexity, the model better fits the data set it has
-been trained on.  This is analogous to fitting a seventh order
+been trained on.  [wc???] This is analogous to fitting a seventh order
 polynomial to seven data points, where the fitting function will go
-through every point.
+through every point but will not likely predict additional points.
 
-EDITING HERE
+% Test behavior with C
+We use the model performance on a test set to determine the best value
+for $C_\text{LogReg}$ that will not overfit the training data.  With
+increasing model complexity, we are able to better able to capture
+features that are generally characteristic of strong lensing systems
+with arcs.  However, past a certain $C_\text{LogReg}$, the model
+performance on the test set decreases, as it has overfit the training
+set.
 
@@
 
-\item
+\item Publicly released pipeline will be... swap out feature
+  extraction, machine learning algorithm, perform parameter searches,
+  and train a model with best parameters.
+
+\item HOG efficiently extracts features that well-describe strong
+  lensing systems with an arc. Performance of the model... SVM doesn't
+  make a difference.
+
+\item Ground based... noise... Model out BCG.
 
@@
 These results indicate that...
+
+% Caveat of the mock data set
+One major caveat ... training and test mock images... LOS galaxies all
+from Hubble Ultra Deep field.  Success measured by performance on the
+small sample of systems observed with HST.
+
+%
 

### 2016-12-19 ms.tex
Only two or three paragraphs to go in the intro, and citations

@@
 \begin{document} 
-\shorttitle{LensFinder}
+\shorttitle{MachLensFinder}
 \shortauthors{Avestruz, Li, Lightman}
@@
 
-\title{MachLLensFinder - I: A Machine Learning Strong Lensing
+\title{MachLensFinder - I: An automated Strong Lensing
   Identification Pipeline}
 
-\author{Camille Avestruz\altaffilmark{1-3}\thanks{E-mail:
+\author{Camille Avestruz\altaffilmark{1-3,$\dagger$}\thanks{E-mail:
     avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, and Matthew Lightman\altaffilmark{5} }
@@
 $^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
+$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
   \href{mailto:avestruz@uchicago.edu}{avestruz@uchicago.edu}\\
@@
 Euclid has prompted a need for automatic and efficient identification
-of strong lensing systems.  We present \change{LensFinderML}, a strong
-lensing identification pipeline that will be publicly released as open
-source software.  In this first application, we employ a fast feature
-extraction method, Histogram of Oriented Gradients (HOG), to capture
-edge features that are characteristic of strong gravitational arcs.
-We use logistic regression to train a supervised classifier model on
-the HOG of \change{HST- and LSST}-like images.  Our best performing
-models reach a completeness rate of \change{XX\%} and purity rate of
-\change{XX\%} for an HST-like sample.  However, for one orbit of LSST,
-our model cannot distinguish between strong lensing systems and
-non-strong lensing systems.  In absence of the brightest cluster
-galaxy in LSST-like data, our trained model reaches a completeness of
-\change{XX\%} and purity of \change{XX\%}.  Our results show one the
-most efficient and effective methods for automated strong lensing
-identification in space-based surveys.  The results also emphasize the
-need for further development and testing of additional tools to
-exploit[wc?]  ground-based surveys.
+of strong lensing systems.  We present {\em MachLensFinder}, a
+strong lensing identification pipeline that will be publicly released
+as open source software.  In this first application, we employ a fast
+feature extraction method, Histogram of Oriented Gradients (HOG), to
+capture edge patterns that are characteristic of strong gravitational
+arcs in galaxy-galaxy lensing.  We use logistic regression to train a
+supervised classifier model on the HOG of \change{HST- and LSST}-like
+images.  Our best performing models reach a completeness rate of
+\change{XX\%} and purity rate of \change{XX\%} for an HST-like sample.
+However, for one orbit of LSST, our model cannot distinguish between
+strong lensing systems and non-strong lensing systems.  In absence of
+the brightest cluster galaxy in LSST-like data, our trained model
+reaches a completeness of \change{XX\%} and purity of \change{XX\%}.
+Our results show one the most efficient and effective methods for
+automated strong lensing identification in space-based surveys.  The
+results also emphasize the need for further development and testing of
+additional tools to maximize use of ground-based surveys.
 \end{abstract}
@@
 % to things like recent accretion and environment.
-Gravitational lensing deflections due to gravity... \citep[see][for a
-  review]{kneibandnatarajan_11}.  Strong lensing visible ... giant
-arcs, multiple images, and arclets.  Galaxy clusters as strong lens,
-deep gravitational potential well, can see by eye.  Strong lensing
-signatures probe underlying dark matter distribution of galaxy
-clusters, magnify the background galaxy population allowing us to
-probe formation at epochs further back in time, and geometric test of
-cosmology.
+Gravitational lensing occurs when intermediate fluctuations in the
+matter density field deflect light from background sources
+\citep[see][for a review]{kneibandnatarajan_11}.  In particular, the
+deep gravitational potential wells of galaxy clusters provide a strong
+lens, with lensed images that can be seen by eye.  Strong
+gravitational lensing can manifest as visible giant arcs magnifying
+high redshift galaxies \citep{lyndsandpetrosian_86,gladders_??},
+multiply imaged quasars \citep{walsh_etal79}, and arclets.  Lensing
+signatures probe the underlying dark matter distribution of galaxy
+clusters \citep{warrenanddye_03}, probe high redshift galaxy formation
+\citep{allam_etal07}, and provide a geometric test of cosmology.
 
@@
 The geometric test of cosmology requires a comparison of predicted arc
-abundances and observed abundances.  In the advent of large surveys,
-such as DES and LSST, we will be limited by our ability to
-automatically process the large amounts of data and select likely
-strong lensing clusters for follow up spectroscopic measurements to
-positively identify background galaxy images.  Image identification
-has had an onslaught of new works (wc).
-
-% Serentipitous discoveries confirmed the theory (cite Einstein)
-% Cite first discoveries of different shapes of strong lensing images
-% While some serendipitous systems found recently (gladders+),
-% Describe the uptick in amount of data
-% End with need to scale with the volume of data
-Early strong lensing images were serendipitous discoveries
-(e.g. multiple quasars \citep{walsh_etal79}, arcs in clusters
-\citep{lyndsandpetrosian_86}, ...).  As the number of images with
-potential lensing systems increased, infrastructure emerged for both
-automated and visual inspection.
+abundances and observed abundances
+\citep{kochanek_96,chae_02,linder_04}.  Visual arc identification has
+been effective through the use of citizen science platforms
+(e.g. \citet{marshall_etal16,more_etal16}).  However, in the advent of
+large surveys, such as the Dark Energy Survey (DES) and the Large
+Synoptic Sky Telescope (LSST), we will be limited by our ability to
+automatically process large amounts of data and select likely strong
+lensing clusters for follow up visual and spectroscopic confirmation.
+The strong lensing sector of cluster-based cosmology requires an
+exploration of techniques in image processing and classification.
 
 % Image identification works: visual, ``robot'' identification -
-% ArcFinder, RingFinder..., and citizen science (space warps).
-% Many of these rely on some explicit aspect of the image's morphology (give example), filtering, ... ....
-% Specifics of the methodology how the instrument affects the strong lensing signal, and the objects of interest.
+% ArcFinder, RingFinder..., and citizen science (space warps).  Many
+% of these rely on some explicit aspect of the image's morphology
+% (give example), filtering, ... ....  Specifics of the methodology
+% how the instrument affects the strong lensing signal, and the
+% objects of interest.
+Over the last decade, infrastructure has emerged for both large scale
+visual and automated image classification. By nature, the human eye is
+one of the best discriminators for image classification.  {\em
+  SpaceWarps} is an example of citizen science based image
+classification of strong lensing systems in Canada France Hawaii
+Telescope Science (CFHTLS) telescope observations
+\citep{marshall_etal16,more_etal16}.  Visual classification has been
+quite successful for a dataset like CFHTLS, classifying \change{XX in
+  XX time}.  However, future datasets like Euclid and LSST will be
+\change{XX} times this size, challenging the scalability of a citizen
+science approach.  The next step is to find automated methods with
+performance comparable to or better than humans. {\em SpaceWarps} is a
+part of the Zooniverse Project (CITE???), which also includes {\em
+  Galaxy Zoo}, the citizen science based image classification of
+galaxy types (CITE???).  Galaxy classification is a successful example
+of in which machine learning algorithms successfully train models to
+classify images with comparable performance to humans (CITE???).
 
-Automated lensed image identification has fallen under the term
-``robot'' identification, where images are fed into some kind of image
-processing pipeline that enhances and extracts characteristic features
-as parameters that are fed into some kind of cutoff or pattern
-recognition piece.  ArcFinder
-... .... \citep{seidelandbartelmann_07}. For multiply imaged quasars,
-Ringfinder ... ... ...\citep{gavazzi_etal14}.  Each pipeline
+% Describe general robot identification schemes that have been
+% implemented
+General automated, or ``robot'', identification refers to a classifier
+where images are fed into an image processing pipeline that enhances
+and extracts characteristic features as parameters on which a pattern
+recognition piece is applied [wc???].  Examples of this include
+ArcFinder ... .... \citep{seidelandbartelmann_07}. For multiply imaged
+quasars, Ringfinder ... ... ...\citep{gavazzi_etal14}.  Each pipeline
 .... ... and relies on the image morphology where ... ...  Note, that
-the method best applied to ... ... and the objects of interest.  The
-human eye is one of the best discriminators of.... SpaceWarps is an
-example of citizen science... visual identification
-\citep{marshall_etal16,more_etal16}.  However, scalability, training
-....
+the method best applied to ... ... and the objects of interest.
 
-% Arc finding must optimize for completeness and purity.  Completeness
-% (no false negatives), purity (minimal false positives).  Purity can
-% be double checked in a smaller subsample of the data visually.  And,
-% spectroscopic follow up is expensive.  Also, scalability of the
-% strong lens finding method matters - example with the citizen
-% science.
+% Describe how machine learning is a step up
+With ``machine learning'' algorithms, we can train a model to separate
+a dataset according to some desired classification scheme.  However,
+we still need to reduce the dimensionality of the problem by removing
+information in the images that do not pertain to the classifier.
+Examples of automated classification will...
+
+% Previous works and our goal to make a universal pipeline 
+Machine learning to automate.  Previous works (StrongML),
+More+... Here, we focus on the improvement from preprocessing the
+images and describe the pipeline, which is publicly available.
+Depending on the image type, different preprocessing is likely
+necessary (rings, multiply lensed quasars, etc.) Our goal is to create
+an open source pipeline that is general enough for the user to select
+or add appropriate image processing techniques to augment the features
+of the lensed image, train and test data with different machine
+learning techniques, and to select the sequence of methods that
+maximizes completeness with optimal purity.
+
+% This is the first in MachLensFinder series with initial pipeline
+% results
+This is the first in a series of {\em MachLensFinder} papers.  We
+present our image processing and machine learning classifier pipeline.
+Our image processing procedure parameterizes edges in our image in a
+1-d histogram, enabling fast feature extraction that is similar to
+techniques used to identify humans in security software systems.  We
+train a model with logistic regression to identify features
+corresponding to strong lensing systems.
+
+We show results of the pipeline on mock galaxy-galaxy lens systems
+observed by HST and LSST as respective examples of classifier
+performance on optical space- and ground-based observations.
+\citet{miraldaescudeandlehar_92} first suggested that massive
+ellipticals would be likely frequent strong lensing sources in optical
+surveys.  We train and test our pipeline on subsamples from 10,000
+mock observed brightest cluster galaxy (BCG) strong lensing systems
+and 10,000 BCG non-strong lensing systems.
+
+% Arc finding must optimize for completeness and purity.  
 In general, lensed image finding must optimize for completeness and
@@
 purity is key; we must minimize false positives that would waste
-follow up telescope time.
-
-% Machine learning to automate.  Previous works (StrongML),
-% More+... Here, we focus on the improvement from preprocessing the
-% images and describe the pipeline, which is publicly available.
-% Depending on the image type, different preprocessing is likely
-% necessary (rings, multiply lensed quasars, etc.) Our goal is to
-% create an open source pipeline that is general enough for the user
-% to select or add appropriate image processing techniques to augment
-% the features of the lensed image, train and test data with different
-% machine learning techniques, and to select the sequence of methods
-% that maximizes completeness with optimal purity.
-
-% No need to explicitly extract morphological parameters to a pattern
-% finding, simply transform the image according to the appropriate
-% image preprocessing function, and directly feed this into the
-% machine learning ...
-
-% This is the first in a series of LensFinder papers where we present
-% our initial pipeline results with a test... of .... Image
-% preprocessing.... same technology to validate watermarks
+follow up telescope time.  We discuss the performance of our image
+processing and classification pipeline with respect to the
+completeness and purity rates of our trained models and illustrate the
+scalability of training our models [wc???].
 
 Our paper is organized as follows. In Section~\ref{sec:methods} we
-briefly describe ...  We present our results in
-Section~\ref{sec:results}, and our summary and discussions in
-Section~\ref{sec:conclusions}.
+briefly describe the methods to generate the mock HST and LSST data
+and our overall image processing and classification pipeline. We
+present our results in Section~\ref{sec:results}, and our summary and
+discussions in Section~\ref{sec:conclusions}.
 

### 2016-12-20 ms.tex
Added more references to the intro

@@
 gravitational lensing can manifest as visible giant arcs magnifying
-high redshift galaxies \citep{lyndsandpetrosian_86,gladders_??},
+high redshift galaxies \citep{lyndsandpetrosian_86,gladders_etal03},
 multiply imaged quasars \citep{walsh_etal79}, and arclets.  Lensing
@@
 clusters \citep{warrenanddye_03}, probe high redshift galaxy formation
-\citep{allam_etal07}, and provide a geometric test of cosmology.
+\citep{allam_etal07}, and provide a geometric test of cosmology via
+comparison of predicted arc abundances and observed abundances
+\citep{kochanek_96,chae_03,linder_04}.
 
@@
 % optical surveys DES, HSC, LSST, and Euclid (Oguri \& Marshall 2010).
-The geometric test of cosmology requires a comparison of predicted arc
-abundances and observed abundances
-\citep{kochanek_96,chae_02,linder_04}.  Visual arc identification has
-been effective through the use of citizen science platforms
-(e.g. \citet{marshall_etal16,more_etal16}).  However, in the advent of
-large surveys, such as the Dark Energy Survey (DES) and the Large
-Synoptic Sky Telescope (LSST), we will be limited by our ability to
-automatically process large amounts of data and select likely strong
-lensing clusters for follow up visual and spectroscopic confirmation.
-The strong lensing sector of cluster-based cosmology requires an
-exploration of techniques in image processing and classification.
+Visual arc identification has been effective through the use of
+citizen science platforms (e.g. \citet{marshall_etal16,more_etal16}).
+However, in the advent of large surveys, such as the Dark Energy
+Survey (DES) and the Large Synoptic Sky Telescope (LSST), we will be
+limited by our ability to automatically process large amounts of data
+and select likely strong lensing clusters for follow up visual and
+spectroscopic confirmation.  The strong lensing sector of
+cluster-based cosmology requires an exploration of techniques in image
+processing and classification.
 
@@
   Galaxy Zoo}, the citizen science based image classification of
-galaxy types (CITE???).  Galaxy classification is a successful example
-of in which machine learning algorithms successfully train models to
-classify images with comparable performance to humans (CITE???).
+galaxy types \citep{lintott_etal08}.  Galaxy classification is a
+successful example of in which machine learning algorithms
+successfully train models to classify images with comparable
+performance to humans \citep{dieleman_etal15}.
 
@@
 and extracts characteristic features as parameters on which a pattern
-recognition piece is applied [wc???].  Examples of this include
-ArcFinder ... .... \citep{seidelandbartelmann_07}. For multiply imaged
-quasars, Ringfinder ... ... ...\citep{gavazzi_etal14}.  Each pipeline
+recognition piece is applied.  Examples of this include ArcFinder for
+group or cluster scale lens \citep{seidelandbartelmann_07}, Ringfinder
+for multiply imaged quasars\citep{gavazzi_etal14}, .  Each pipeline
 .... ... and relies on the image morphology where ... ...  Note, that

### 2016-12-21 ms.tex
Modified sample lensed/unlensed images to be the same for HST, LSST, and stacked LSST

@@
 \includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
-\includegraphics[width=1\columnwidth]{figures/lsst_9_lensed_imgs_1_color.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/lsst_9_unlensed_imgs_1_color.pdf}
-\caption{Top panel: Example mock HST images, with $n_\text{pix}\times
+\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1.pdf}
+\caption{Top row: Example mock HST images, with $n_\text{pix}\times
   n_\text{pix}=300\times300$.  The left corresponds to a strong
   gravitational lensing system with a visibly obvious giant arc.  The
-  right corresponds to a non-lensing system.  Bottom panel: Example
-  mock LSST images, with $n_\text{pix}\times n_\text{pix}=45\times45$.
-  The resolution and noise of a ground based telescope is noticeably
-  worse.  The left corresponds to a strong gravitational lensing
-  system, and the right to a non-lensing system.  However, visual
-  identification of giant arcs in the LSST images is very difficult.}
+  right corresponds to a non-lensing system.  Middle row: Example mock
+  LSST images for a single epoch, with $n_\text{pix}\times
+  n_\text{pix}=45\times45$.  The resolution and noise of a ground
+  based telescope is noticeably worse.  The left and right images
+  correspond to the same systems as the top row.  However, visual
+  identification of giant arcs in the LSST images is very difficult.
+  Bottom row: Example mock LSST images for stacked data over the 10
+  year run.  Here, the arc is more visible, but not as well resolved
+  as in the HST case.}
 \end{center}

### 2016-12-21 ms.tex
Added HOG visualizations for the sample mock images

@@
 \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
+\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
 \caption{Visualized HOG feature vectors of the sample lensed HST-like

### 2016-12-21 ms.tex
added caption for HOG and first major summary point

--- 2016-12-21 ms.tex
@@
 Figure ~\ref{fig:mockimages} illustrates a sample mock lensed and
-unlensed images from each telescope.  From left to right, the top
-panel images respectively correspond to a mock HST lensing and
-non-lensing system. The mock HST images are $n_\text{pix}\times
+unlensed images from each telescope.  The top left and right panel
+images respectively correspond to a mock HST lensing and non-lensing
+system. The mock HST images are $n_\text{pix}\times
 n_\text{pix}=300\times300$ in size.  For the HST-like dataset, many
@@
 
-The bottom panel images respectively correspond to a mock LSST lensing
-and non-lensing system.  These images are $n_\text{pix}\times
+The middle row corresponds to the same simulated systems, as observed
+with a single epoch of LSST.  These images are $n_\text{pix}\times
 n_\text{pix}=45\times45$.  The ground based noise and limited
 resolution of the LSST-like dataset make visual giant arc
-identification difficult.
+identification difficult.  However, by stacking observations over the
+course of the LSST survey, we recover the arc feature, albeit at a
+much lower resolution than with the HST-like image. The bottom row
+shows the mock stacked observation, where the lensed background galaxy
+is now visible.
 
@@
 \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
-\caption{Visualized HOG feature vectors of the sample lensed HST-like
-  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
-  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
-  and (1, 1) cells per block.  Right: The HOG visualization of the
-  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
-  and (1, 1) cells per block.  The brightest lines align with
-  prominent edges.  Note, while fewer pixels per cell will better
-  resolve the arc feature, the ``edge'' corresponding to the arc is
-  less prominent.  }
+\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
+%\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
+\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
+%\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
+\caption{Top row: Visualized HOG feature vectors of the sample lensed
+  HST-like image from Figure~\ref{fig:mockimages}.  Left: The
+  corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
+  pixels per cell, and (1, 1) cells per block.  Right: The HOG
+  visualization of the same mock image with N$_\text{orient}=9$, (16,
+  16) pixels per cell, and (1, 1) cells per block.  The brightest
+  lines align with prominent edges.  Note, while fewer pixels per cell
+  will better resolve the arc feature, the ``edge'' corresponding to
+  the arc is less prominent.  Bottom row: Visualized HOG feature
+  vectors for the LSST-like single epoch and stacked images with the
+  best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
+  pixels per cell, and (3, 3) cells per block.  The single epoch image
+  (left) does not have significant enough edge features to emerge in
+  the HOG, but the stacked image (right) does.}
 \end{center}
@@
 
-\item Publicly released pipeline will be... swap out feature
-  extraction, machine learning algorithm, perform parameter searches,
-  and train a model with best parameters.
+\item We have designed our pipeline to easily select and add image
+  pre-processing and feature extraction methods, and to select a
+  machine learning algorithm for classification.  Additionally, the
+  user can easily perform parameter searches, and train a model with
+  best parameters.
 

### 2016-12-21 ms.tex
added all but final summary/discussino point on near misses

@@
   machine learning algorithm for classification.  Additionally, the
-  user can easily perform parameter searches, and train a model with
-  best parameters.
+  user can easily perform parameter searches to train a model with the
+  best parameters for a given problem.
 
-\item HOG efficiently extracts features that well-describe strong
-  lensing systems with an arc. Performance of the model... SVM doesn't
-  make a difference.
+\item We have tested HOG as an efficient and effective feature
+  extractor for galaxy-galaxy strong lensing systems in both a space
+  based (HST-like) and ground based (LSST-like) observation.
 
-\item Ground based... noise... Model out BCG.
+\item We have found almost no difference between the Logistic
+  Regression and Support Vector Machine algorithms, with Logistic
+  Regression performing at a factor of $XX$ faster.  This means that
+  features of lens and non-lens images are relatively well separated
+  by hyperplanes in feature space.
+
+\item We find AUC values of ROC curves of optimized classifier models
+  to yield $AUC=0.987$ for the HST-like data, $AUC=0.96$ for the
+  stacked LSST-like data with the lensing BCG included, and $AUC=0.86$
+  for the stacked LSST-like data with the lensing BCG perfectly
+  removed.  This suggests that we will be able to use our method to
+  detect strong galaxy-galaxy lensing systems in future space-based
+  missions (e.g. {\em Euclid}) with high purity and completeness.
+  However, for future ground-based missions like LSST, we will need to
+  perform additional image pre-processing, such as subtracting the
+  image component corresponding to the lens.
+
+\item Images that were difficult for our model to classify typically
+  fell in the ..... ....
 

### 2016-12-23 ms.tex
Added some compilation images of tp tn bp bn fn fp

@@
 %-------------------------------------------------%
-\subsection{Failed identifications}\label{sec:failedids}
+\subsection{Image classification performance}\label{sec:performance}
 %-------------------------------------------------%
 
-The best ROC curve, HST:N5ppc32cpb4C100, illustrates that we can lower
-the classification threshold and improve the true positive rate by
-$\sim10\%$ and sacrifice an increase in false positive rate by
-$\lsim5\%$.  In this section, we examine the ``borderline'' images,
-which transition from negative classification to positive calculation
-in the steepest part of the AUC curve.  Borderline images correspond
-to candidates for spectroscopic follow-up.  The model is less
-confident about this subset of images, and these would therefore be
-good candidates for follow-up human classification and/or
-spectroscopic follow-up (CITE HERE???).
+% Defining the 6 paradigms of classification
+In this section, we discuss the different image types that our model
+is most and least able to successfully classify.  We have six
+paradigms of model performance on the mock images, and include a
+larger compilation of each of the six image classification paradigms
+in the Appendix for the various models we have trained.
 
-\todo{Figure ~\ref{fig:falseids} shows a random sample of 10 borderline
-images.  Common features...????}
+% TP and TN
+Figure ~\ref{fig:HSTclassificationtile} shows a tile of representative
+HST-like images classified with the model, HST:N5ppc32cpb4C100.  The
+left column show lensing systems, and right column non-lensing
+systems.  From top to bottom, the images are ordered from highest
+scoring to lowest scoring with the classification model.  The top left
+is what we would call a ``true positive'', a lensing system that will
+always classified as positive because of its high score.  Most of the
+highest scoring lensing systems exhibit similar extended arcs
+\todo{corresponding to a large magnification.}  The bottom right is a
+``true negative'', a non-lensing system that will likely be classified
+as negative because of its low score.  Many of the lowest scoring
+non-lensing systems have \todo{fairly small BCGs, which are non likely
+  to lens a background galaxy.}
+
+% FN and FP
+The bottom left corresponds to a likely ``false negative,'' or a
+lensing system that is likely to be mis-classified as a negative.  The
+lowest scoring lensing systems tend to have images with smaller
+magnification that are minorly distorted, mimicking the shape of
+line-of-sight galaxies that the model has learned to ignore.  The top
+right corresponds to a likely ``false positive,'' or a non-lensing
+system that is likely to be mis-classified as a positive.  False
+positives tend to have ``fuzzy'' along the line of sight galaxies that
+mimic lensing arcs.
+
+% BP and BN
+The middle row are images whose classification will be most sensitive
+to the classification threshold.  We call these borderline images,
+with the left corresponding to a ``borderline positive'', and the
+right corresponding to a ``borderline negative''.  They sit around the
+knee of the ROC curve, the optimal threshold for purity and
+completeness.  Note that the ROC curve for HST:N5ppc32cpb4C100
+illustrates that we can lower the classification threshold and improve
+the true positive rate by $\sim10\%$ and sacrifice an increase in
+false positive rate by $\lsim5\%$.  However, small perturbations
+around the knee will either include or disinclude the middle row
+images.  These are the systems that would make good candidates for
+visual and/or spectroscopic follow-up.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]
+  \centering \mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
+\caption{HST-like images. The left column corresponds to typical
+  lensing systems in our sample from highest scoring (top) to lowest
+  scoring, or false negatives (bottom).  The right column corresponds
+  to typical non-lensing systems in our sample from highest scoring,
+  or false positives (top), to lowest scoring (bottom).  The middle
+  row can be considered ``borderline'' classified images, where the
+  scores of the lensing and non-lensing system are very close to one
+  another.  These are systems that will be most sensitive to the
+  classification threshold.}
+\label{fig:HSTclassificationtile}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]
+  \centering
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
+}
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
+}
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
+}
+
+\caption{LSST-like images with a BCG. These illustrate the same image
+  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
+\label{fig:LSSTBCGclassificationtile}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]
+  \centering
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
+}
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
+}
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
+    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+        clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
+}
+
+\caption{LSST-like images with no BCG. These illustrate the same image
+  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
+\label{fig:LSSTnoBCGclassificationtile}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%
+% Interpreting TP and FP rates
+Note that while our training and test set split of $50\%$ lensed and
+$50\%$ unlensed images is not realistic, our true positive and false
+positive rates in the ROC curves would stay the same for alternative
+lensed and unlensed sample splittings.
+
+On the other hand, the ROC curves show a representative rate for lens
+and source distributions that are evenly sampled.  The sampling is
+{\it not} representative of what we might expect from a an
+observational survey.
 

### 2016-12-23 ms.tex
Added a caption for the LSST-like images

@@
 is most and least able to successfully classify.  We have six
-paradigms of model performance on the mock images, and include a
+paradigms of model performance on the mock images, \todo{and include a
 larger compilation of each of the six image classification paradigms
-in the Appendix for the various models we have trained.
+in the Appendix for the various models we have trained}.
 
@@
 \caption{LSST-like images with a BCG. These illustrate the same image
-  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
+  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
+  Note, the larger PSF of LSST reduces the resolution of images,
+  making the arc-like morphology of faint images less significant and
+  increases the appearance of image-BCG blending.}
 \label{fig:LSSTBCGclassificationtile}

### 2017-01-11 ms.tex
changed focus of motivation to galaxy-galaxy lensing, mass reconstruction,  m/l ratio measurements

@@
 matter density field deflect light from background sources
-\citep[see][for a review]{kneibandnatarajan_11}.  In particular, the
-deep gravitational potential wells of galaxy clusters provide a strong
-lens, with lensed images that can be seen by eye.  Strong
-gravitational lensing can manifest as visible giant arcs magnifying
-high redshift galaxies \citep{lyndsandpetrosian_86,gladders_etal03},
-multiply imaged quasars \citep{walsh_etal79}, and arclets.  Lensing
-signatures probe the underlying dark matter distribution of galaxy
-clusters \citep{warrenanddye_03}, probe high redshift galaxy formation
+\citep[see][for a review]{kneibandnatarajan_11}.  Strong gravitational
+lensing can manifest as visible giant arcs magnifying high redshift
+galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
+quasars \citep{walsh_etal79}, and arclets.  Lensing signatures probe
+the underlying dark matter distribution of the lens
+\citep{warrenanddye_03}, high redshift galaxy formation
 \citep{allam_etal07}, and provide a geometric test of cosmology via
@@
 limited by our ability to automatically process large amounts of data
-and select likely strong lensing clusters for follow up visual and
-spectroscopic confirmation.  The strong lensing sector of
-cluster-based cosmology requires an exploration of techniques in image
-processing and classification.
+and select likely strong lensing candidates for follow up visual and
+spectroscopic confirmation.  The strong lensing sector requires an
+exploration of techniques in image processing and classification.
 
@@
 % objects of interest.
-Over the last decade, infrastructure has emerged for both large scale
-visual and automated image classification. By nature, the human eye is
+Over the last decade, infrastructure for both large scale visual and
+automated image classification emerged. By nature, the human eye is
 one of the best discriminators for image classification.  {\em
@@
 group or cluster scale lens \citep{seidelandbartelmann_07}, Ringfinder
-for multiply imaged quasars\citep{gavazzi_etal14}, .  Each pipeline
-.... ... and relies on the image morphology where ... ...  Note, that
-the method best applied to ... ... and the objects of interest.
+for multiply imaged quasars\citep{gavazzi_etal14}, and ???.  Each
+pipeline .... ... and relies on the image morphology where ... ...
+Note, that the method best applied to ... ... and the objects of
+interest.
 
@@
 
+% Summary of results
 We show results of the pipeline on mock galaxy-galaxy lens systems
@@
 
-% Arc finding must optimize for completeness and purity.  
+% Need to optimize for completeness and purity.  Arc counts and mass
+% reconstruction.
 In general, lensed image finding must optimize for completeness and
@@
 cosmological predictions, completeness is important; we must be able
-to understand the reasons and frequency of false negatives.  Since
-spectroscopic confirmation of background lensed images is expensive,
-purity is key; we must minimize false positives that would waste
-follow up telescope time.  We discuss the performance of our image
-processing and classification pipeline with respect to the
+to understand the reasons and frequency of false negatives.  In the
+application of mass reconstruction of the lensing object, completeness
+in strong lensing system identifications will allow us to constrain
+the mass-to-light ratio for a large number of objects.
+
+% Purity issues
+Since spectroscopic confirmation of background lensed images is
+expensive, purity is key; we must minimize false positives that would
+waste follow up telescope time.  We discuss the performance of our
+image processing and classification pipeline with respect to the
 completeness and purity rates of our trained models and illustrate the
@@
 %-------------------------------------------------%
+**Redshift makes sense, but only because of the redshift distribution.
+--> Zahid+15 quiescent.... this is where redshifts are from.
 
@@
 highest scoring lensing systems exhibit similar extended arcs
-\todo{corresponding to a large magnification.}  The bottom right is a
-``true negative'', a non-lensing system that will likely be classified
-as negative because of its low score.  Many of the lowest scoring
+corresponding to a large magnification (see
+Section~\ref{sec:peformance_lensmodel}).  The bottom right is a ``true
+negative'', a non-lensing system that will likely be classified as
+negative because of its low score.  Many of the lowest scoring
 non-lensing systems have \todo{fairly small BCGs, which are non likely
@@
 positives tend to have ``fuzzy'' along the line of sight galaxies that
-mimic lensing arcs.
+mimic lensing arcs.  The false positives should be from bright
+galaxies along the line of sight.  \todo{The highest scoring
+  non-lensing systems often have fairly bright disk shaped galaxies
+  along the line of sight.  Visually, these are also virtually
+  indistinguishable from a lensed image and would require
+  spectroscopic follow-up.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
-
+\subsection{BCG removed}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
@@
 %-------------------------------------------------%
+\subsubsection{Performance dependence on lens-model parameters}
+\label{sec:peformance_lensmodel}
+%-------------------------------------------------%
+
+% Summary of subsection
+Here, we examine lens-model parameters that affect how well our
+pipeline can classify the system.  The lens-model parameters we
+examined are the redshift, ellipticity, orientation angle, and
+velocity dispersion of the lensing BCG, and also the magnification of
+the lensed image compared with its original size.  The magnification
+of the lensed image is the most correlated lens-model parameter with
+our trained model performance.  The more strongly lensed an image is,
+the larger its magnification, and the easier it is for our trained
+model to classify.
+
+% Discuss figure
+In Figure~\ref{fig:scorevslensparams}, we show the classification
+score as a function of image magnification for our HST-like sample.
+The left-hand side shows the relation color-coded by the redshift of
+the lensing galaxy, and the right-hand side shows the relation
+color-coded by the velocity dispersion of the lensing galaxy.  Lensing
+systems with images that have magnification $\gsim7$ will almost
+certainly be classified as positive with threshold scores above
+$\gsim0.5$.  These systems are also those that are most easily
+classified by eye.  However, our trained model has varying performance
+for systems with lower magnifications.
+
+% Some dependence on redshift and velocity dispersion, which is folded
+% into magnitude
+Almost \todo{X\%} of lensing systems with magnifications $\lsim7$ will
+be falsely identified as non-lenses for classification threshold
+scores $\gsim0.5$.  These systems typically have lenses that are at
+higher redshifts of $z\gsim0.5$ (lighter colors in left figure) and/or
+velocity dispersions lower than $\sigma_v\lsim230.$~km/s (darker
+colors in right figure).  Note that lensing galaxies with smaller
+velocity dispersions are less massive and therefore have a smaller
+efficiency of lensing cross section.  The smaller efficiency means
+that a background galaxy is less likely to be strongly lensed with
+high magnification.  Also, due to hierarchical structure formation,
+galaxies are less massive at higher redshifts, so the trends of model
+performance with these three parameters are somewhat degenerate with
+one another.
+
+The relationship between our model performance and these lens
+parameters indicates that the magnification of lensed images is the
+most relevant, and the distribution of image magnification in a data
+set will impact trained model performance.  We did not find
+correlations in model performance with other lens parameters.  It is
+also useful to keep in mind that lensed galaxy images with
+magnification $\lsim5$ (e.g. slightly stretched spherical galaxies)
+are often visually indistinguishable from elliptical galaxies along
+the line of sight.  \todo{We will discuss how differences between the
+  lens-model parameter distributions in the training and test sets
+  affect performance in a forthcoming paper.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]
+  \centering
+
+\mbox{
+    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
+        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_z.pdf}}\hfill
+    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
+        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_velocity_dispersion.pdf}}
+} 
+\caption{Image classification score as a function of lensed image
+  magnification.  Left color-coded by redshift, right is color coded
+  by the lens velocity_dispersion.}
+\label{fig:scorevslensparams}
+\end{figure*}
+
+%-------------------------------------------------%
+\subsubsection{Performance sensitivity to line-of-sight galaxies}
+\label{sec:peformance_lensmodel}
+%-------------------------------------------------%
+
+%-------------------------------------------------%
 \subsection{Effects of BCG contamination}
@@
 %-------------------------------------------------%
+
+machine learning -> pipeline, and training set.
+
+Future work with training set tests.
 
@@
 
-\item Images that were difficult for our model to classify typically
-  fell in the ..... ....
+\item Images that were easiest for our model to classify typically
+  were lens systems that had high magnification and a BCG with large
+  velocity dispersion.
 
@@
 
-\acknowledgments CA acknowledges support from the Kavli Institute of
-Cosmological Physics, the Enrico Fermi Institute at the University of
-Chicago, and the University of Chicago Provost's Office.
+\acknowledgments CA acknowledges support from the Enrico Fermi
+Institute at the University of Chicago, and the University of Chicago
+Provost's Office. This work was also supported in part by the Kavli
+Institute for Cosmological Physics at the University of Chicago
+through grant NSF PHY-1125897 and an endowment from the Kavli
+Foundation and its founder Fred Kavli.
 \lastpagefootnotes
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\section{Sample stacked mock LSST images}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\subsection{BCG included}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \bibliography{ms}

### 2017-03-06 ms.tex
updated figures

@@
 \begin{document} 
-\shorttitle{MachLensFinder}
+\shorttitle{Automated Lensing Learner}
 \shortauthors{Avestruz, Li, Lightman}
@@
 
-\title{MachLensFinder - I: An automated Strong Lensing
+\title{Automated Lensing Learner - I: An automated Strong Lensing
   Identification Pipeline}
@@
 Euclid has prompted a need for automatic and efficient identification
-of strong lensing systems.  We present {\em MachLensFinder}, a
-strong lensing identification pipeline that will be publicly released
-as open source software.  In this first application, we employ a fast
-feature extraction method, Histogram of Oriented Gradients (HOG), to
-capture edge patterns that are characteristic of strong gravitational
-arcs in galaxy-galaxy lensing.  We use logistic regression to train a
-supervised classifier model on the HOG of \change{HST- and LSST}-like
-images.  Our best performing models reach a completeness rate of
-\change{XX\%} and purity rate of \change{XX\%} for an HST-like sample.
-However, for one orbit of LSST, our model cannot distinguish between
-strong lensing systems and non-strong lensing systems.  In absence of
-the brightest cluster galaxy in LSST-like data, our trained model
-reaches a completeness of \change{XX\%} and purity of \change{XX\%}.
-Our results show one the most efficient and effective methods for
-automated strong lensing identification in space-based surveys.  The
+of strong lensing systems.  We present {\em (ALL) Automated Lensing
+  Learner}, a strong lensing identification pipeline that will be
+publicly released as open source software.  In this first application,
+we employ a fast feature extraction method, Histogram of Oriented
+Gradients (HOG), to capture edge patterns that are characteristic of
+strong gravitational arcs in galaxy-galaxy lensing.  We use logistic
+regression to train a supervised classifier model on the HOG of HST-
+and LSST-like images.  We use an area under the curve (AUC) of a
+Receiver Operating Characteristic curve to assess model performance;
+$AUC=1.0$ is an ideal trained classifier, and $AUC=0.5$ does not
+provide any classification information.  Our best performing models
+exhibit an AUC of \change{XX} for an HST-like sample.  However, for
+one orbit of LSST, our model only reaches an AUC of \change{XX}.  In
+absence of the lens galaxy in one orbit of LSST-like data, the AUC
+improves to \change{XX}.  For 10-year mock LSST observations, the
+respective AUC with and without the lens galaxy improves to
+\change{XX} and \change{XX}.  Our results show an efficient and
+effective methods for automated strong lensing identification.  The
 results also emphasize the need for further development and testing of
@@
 comparison of predicted arc abundances and observed abundances
-\citep{kochanek_96,chae_03,linder_04}.
+\citep{kochanek_96,chae_03,linder_04} and time-delay signals from
+multiply imaged quasars ???\citep{}.
+
+% Application of constraining mass profiles - large numbers needed.
+The application of strong gravitational lensing to constrain the mass
+distribution of \todo{early-type galaxies (ETGs)} necessitates large
+samples of galaxy-galaxy lensing systems.  The strong lensing
+signature... EDITING HERE These systems exhibit a background source
+galaxy that the ETG deflects into a partial of full arc shaped
+Einstein ring.
 
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1_color.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
-\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1.pdf}\\
-\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1.pdf}
-\caption{Top row: Example mock HST images, with $n_\text{pix}\times
-  n_\text{pix}=300\times300$.  The left corresponds to a strong
-  gravitational lensing system with a visibly obvious giant arc.  The
-  right corresponds to a non-lensing system.  Middle row: Example mock
-  LSST images for a single epoch, with $n_\text{pix}\times
-  n_\text{pix}=45\times45$.  The resolution and noise of a ground
-  based telescope is noticeably worse.  The left and right images
-  correspond to the same systems as the top row.  However, visual
-  identification of giant arcs in the LSST images is very difficult.
-  Bottom row: Example mock LSST images for stacked data over the 10
-  year run.  Here, the arc is more visible, but not as well resolved
-  as in the HST case.}
+\includegraphics[width=2\columnwidth]{figures/tiles/compilations/telescope_compilation.pdf}
+\caption{Left to right show example mock HST, LSST 10 year, and LSST 1
+  year images.  The top row corresponds to a lensing system with a
+  very visible arc signature, and the bottom row to a lensing system
+  that is less obvious.  Example mock HST images have
+  $n_\text{pix}\times n_\text{pix}=300\times300$.  Example mock LSST
+  images have $n_\text{pix}\times n_\text{pix}=45\times45$.  The
+  resolution and noise of a ground based telescope is noticeably
+  worse. Visual identification of giant arcs in the LSST images in the
+  bottom row is very difficult.}
 \end{center}
@@
 train a classifier model on a subset of our images.  We have explored
-both {\em Logistic Regression} (LR) and {\em Support Vector Machine}
+both {\em Logistic Regression} (LogReg) and {\em Support Vector Machine}
 (SVM) machine learning algorithms.  We test our trained model on an
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:hogvisual}
+\begin{figure*}[t]\label{fig:mockimages}
 \begin{center}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
-\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
-%\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
-\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
-%\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
-\caption{Top row: Visualized HOG feature vectors of the sample lensed
-  HST-like image from Figure~\ref{fig:mockimages}.  Left: The
-  corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
-  pixels per cell, and (1, 1) cells per block.  Right: The HOG
-  visualization of the same mock image with N$_\text{orient}=9$, (16,
-  16) pixels per cell, and (1, 1) cells per block.  The brightest
-  lines align with prominent edges.  Note, while fewer pixels per cell
-  will better resolve the arc feature, the ``edge'' corresponding to
-  the arc is less prominent.  Bottom row: Visualized HOG feature
-  vectors for the LSST-like single epoch and stacked images with the
-  best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
-  pixels per cell, and (3, 3) cells per block.  The single epoch image
-  (left) does not have significant enough edge features to emerge in
-  the HOG, but the stacked image (right) does.}
+\includegraphics[width=2\columnwidth]{figures/tiles/compilations/hog_telescope_compilation.pdf}
+\caption{Left to right show example image transforms of mock images
+  from Figure~\ref{fig:mockimages} with a visualized histogram of
+  oriented gradients.  The image transform picks up edge features,
+  with arc features showing up as edges across radial orientations.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%% \begin{figure*}[t]\label{fig:hogvisual}
+%% \begin{center}
+%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
+%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
+%% \includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
+%% %\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
+%% \includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
+%% %\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
+%% \caption{Top row: Visualized HOG feature vectors of the sample lensed
+%%   HST-like image from Figure~\ref{fig:mockimages}.  Left: The
+%%   corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
+%%   pixels per cell, and (1, 1) cells per block.  Right: The HOG
+%%   visualization of the same mock image with N$_\text{orient}=9$, (16,
+%%   16) pixels per cell, and (1, 1) cells per block.  The brightest
+%%   lines align with prominent edges.  Note, while fewer pixels per cell
+%%   will better resolve the arc feature, the ``edge'' corresponding to
+%%   the arc is less prominent.  Bottom row: Visualized HOG feature
+%%   vectors for the LSST-like single epoch and stacked images with the
+%%   best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
+%%   pixels per cell, and (3, 3) cells per block.  The single epoch image
+%%   (left) does not have significant enough edge features to emerge in
+%%   the HOG, but the stacked image (right) does.}
+%% \end{center}
+%% \end{figure*}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   singular matrix}.  We discuss the score dependence on logistic
-regression coefficient in Section\ref{sec:unregularizedfit}.
-
-%-------------------------------------------------%
-\subsection{Receiver Operatic Characteristic}
+regression coefficient in Section\ref{sec:regularization}.
+
+%-------------------------------------------------%
+\subsection{Receiver Operating Characteristic}
 %-------------------------------------------------%
@@
 In this section, we discuss the Receiver Operating Characteristic
-(ROC) curve, which shows the true positive rate as a function of false
-positive rate for a given model and test set.  The true positive rate
-is defined as the number of true positives divided by the total number
-of positives (completeness of the positive identifications).  The
-false positive rate is defined as the number of false positives
-divided by the total number of negatives (impurity of the
-identifications).  The ROC curve illustrates the performance of our
-trained model as we vary the discrimination threshold.
+(ROC) curve, which shows the true positive rate (tpr) as a function of
+false positive rate (fpr) for a given model and test set.  The true
+positive rate is defined as the number of true positives divided by
+the total number of positives (completeness of the positive
+identifications).  The false positive rate is defined as the number of
+false positives divided by the total number of negatives (impurity of
+the identifications).  The ROC curve illustrates the performance of
+our trained model as we vary the discrimination threshold.
 
@@
 probability that the image is a strong lensing system.  To construct
-the ROC curve, the test images are ranked by probability and the
-discrimination threshold varied.
+the ROC curve, we rank the test images by probability, and calculate
+the tpr and fpr for decreasing discrimination threshold.
 
 For very high discrimination threshold, we have maximal purity, but a
-low completeness (bottom left region of the ROC).  FOr a very low
+low completeness (bottom left region of the ROC).  For a very low
 discrimination threshold, we have maximal completeness, but minimal
-purity (top right region of the ROC).  The ideal model would have a
-data point on the ROC curve that sits on the top left corner,
-i.e. $(x, y) = (0, 1)$.
+purity (top right region of the ROC).  The ideal model would have an
+ROC curve with data points that go from $(x, y) = (0, 0)$ to $(x, y) =
+(0, 1)$ to $(x, y) = (1, 1)$.
 
@@
 model will optimize the two, and we can characterize the steepness by
-the area under the curve (AUC).  A perfect model would have an AUC of
-1, with data points along $(x=0, 0\leq y\leq1)$, and $(0\leq x\leq 1,
-y=1)$.
+the area under the curve (AUC).  The ideal model would have an AUC of
+1.  We show the ROC curves of our best performing models in each
+dataset.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:ROCHST}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%% \begin{figure}[t]\label{fig:ROCHST}
+%% \begin{center}
+%% \includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
+%% \caption{Red, green, blue: ROC curves for a models trained on the
+%%   HST-like data with the Logistic Regression algorithm.  The magenta
+%%   solid (dotted) curve show the ROC curve for the LSST-like data with
+%%   (without) the BCG.  The corresponding parameters are labeled: N for
+%%   number of orientations, ppc for pixels-per-cell, cpb for
+%%   cells-per-block, and C for best regularization parameter.  The AUC
+%%   for each model is also labeled in the legend, where an AUC close to
+%%   1 is a near-ideal model, and an AUC close to 0.5 is a model that
+%%   performs as well as a coin-flip.}
+%% \end{center}
+%% \end{figure}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:ROCcompilation}
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
-\caption{Red, green, blue: ROC curves for a models trained on the
-  HST-like data with the Logistic Regression algorithm.  The magenta
-  solid (dotted) curve show the ROC curve for the LSST-like data with
-  (without) the BCG.  The corresponding parameters are labeled: N for
-  number of orientations, ppc for pixels-per-cell, cpb for
-  cells-per-block, and C for best regularization parameter.  The AUC
-  for each model is also labeled in the legend, where an AUC close to
-  1 is a near-ideal model, and an AUC close to 0.5 is a model that
-  performs as well as a coin-flip.}
+\includegraphics[width=\columnwidth]{figures/metrics/ROC/ROC_compilation.pdf}
+\caption{Red, blue, green: ROC curves for models trained on our whole
+  10,000 training set and tested on our holdout set of 1,000.  These
+  respectively correspond to the HST, LSST 1 year, and LSST 10 year
+  data.  The solid lines are for data that include the lensing central
+  galaxy, and the dashed lines for the data where there is no lensing
+  galaxy, mimicking an ideal removal of the lens.  Model performance
+  can be summarized by the area under the curve (AUC), labeled in the
+  legend. $AUC=1$ is a perfect model, and $AUC=0.5$ is a useless
+  model.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:ROCLSST}
-\begin{center}
-\includegraphics[width=\columnwidth]{figures/ROC_LSST_HOG.png}
-\caption{Red, green, blue: ROC curves for a models trained on the
-  HST-like data with the Logistic Regression algorithm.  The magenta
-  solid (dotted) curve show the ROC curve for the LSST-like data with
-  (without) the BCG.  The corresponding parameters are labeled: N for
-  number of orientations, ppc for pixels-per-cell, cpb for
-  cells-per-block, and C for best regularization parameter.  The AUC
-  for each model is also labeled in the legend, where an AUC close to
-  1 is a near-ideal model, and an AUC close to 0.5 is a model that
-  performs as well as a coin-flip.}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%-------------------------------------------------%
-\subsection{Effects of Regularization on Model Performance}\label{sec:regularizedfit}
+
+%-------------------------------------------------%
+\subsection{Effects of Regularization on Model Performance}\label{sec:regularization}
 %-------------------------------------------------%
@@
 % Logistic regression and regularization
-As described in Section~\ref{sec:logreg}, logistic regression trains a
-model with complexity determined by the regularization parameter,
+As described in Section~\ref{sec:logreg}, LogReg trains a model with
+complexity determined by the regularization parameter coefficient,
 $C_\text{LogReg}$.  Increasing model complexity (larger
@@
 increasing model complexity, the model better fits the data set it has
-been trained on.  [wc???] This is analogous to fitting a seventh order
+been trained on.  This is analogous to fitting a seventh order
 polynomial to seven data points, where the fitting function will go
@@
 with arcs.  However, past a certain $C_\text{LogReg}$, the model
-performance on the test set decreases, as it has overfit the training
-set.
+performance on the test set decreases or asymptotes, as it has overfit
+the training set.
+
+% Train time with Creg
+Lower Creg, more regularized, smaller volume to search for the
+solution (best fit coefficients), so faster on average.  But, still
+has some randomness associated with the path it takes to convergence
+(not purely monotonic).
 
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/regularized_accuracy.pdf}\hspace{-20pt}
-\includegraphics[width=1\columnwidth]{figures/regularized_AUC.pdf}
-\caption{Left: Accuracy of the model with varying regularization.
-  Each color corresponds to a model trained for features extracted
-  with a different set of HOG parameters.  The dotted (solid) lines
-  show the performance of the model on the training (test) set.
-  Right: AUC of the model with varying regularization.  Linestyles and
-  colors are similar to those in the left panel.  AUC is a better
-  characterization of model performance, since the accuracy is
-  determined for fixed classification threshold [wc?], but peak model
-  performance can occur at a different classification threshold.}
+\includegraphics[width=.66\columnwidth]{figures/Creg/HST.pdf}
+\includegraphics[width=.66\columnwidth]{figures/Creg/LSST1.pdf}
+\includegraphics[width=.66\columnwidth]{figures/Creg/LSST10.pdf}
+\caption{AUC of the model with varying LR regularization coefficient
+  parameter, $C_{reg}$, used when training the model classifier.  We
+  use a subset of the the 10,000 training images to search over the LR
+  $C_{reg}$ parameter, training on 8,000 and testing on 1,000.  Each
+  panel corresponds to a different mock observation.  From left to
+  right: HST, LSST for one year, and LSST for 10 years.  The xsolid
+  blue lines correspond to the AUC of the training set, and the dotted
+  blue lines to the AUC of the test set.  To avoid overfitting, we
+  choose the smallest parameter for which the AUC of the test set is
+  maximal: 5000, 10, and 5000, respectively.  In thin red solid lines,
+  we show the train time of the model, which roughly increases in a
+  log-log scaling with logistic regression coefficient parameter.}
 \end{center}
@@
 %-------------------------------------------------%
+\subsection{Effects of Dataset Size on Model Performance}\label{sec:datasize}
+%-------------------------------------------------% 
+%-------------------------------------------------% 
+\subsubsection{Effects of Training Set Size}
+%-------------------------------------------------% 
+In this section, we show the effects of training set size on model
+performance.  Figure~\ref{fig:trainsize} shows the AUC and the train
+time depend on the log of the size of the training set.  In solid blue
+lines, we see that the AUC improves almost linearly with the log of
+the training size set.  In dotted red, we see that the train time
+roughly scales logarithmically with the log of the train size, with an
+exception of the data point corresponding to train size of 2000.
+
+Each model was trained with the same HOG parameterization from the
+grid search and the optimal regularization parameter for that subset
+train data.  The train time of a given model generally increases for
+increasing regularization parameter.  For the subset of train size
+2000, the optimal regularization parameter happened to be
+$C_{LR}=100$, whereas it was $C_{LR}=500$ for the subset of trainsize
+1000, and $C_{LR}=1000$ for the subset of trainsize 4000.
+
+% Scores vs. regularization on larger train/test set with comparable
+% grid search in parameterization
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:trainsize}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/trainsize/LSST10.pdf}
+\caption{Solid blue line: AUC for models with varying size of the
+  training set for LSST10.  Dotted red line: Train time for that
+  model.  The improvement of AUC scales linearly with the log of the
+  training set size, but train time roughly scales logarithmically.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------% 
+\subsubsection{Effects of Rotation on AUC}
+%-------------------------------------------------% 
+To augment our training set, we rotated each image in the set by
+multiples of $90^o$.  The augmentation (factor of four) naturally
+optimizes the use of available training data, since our feature
+extraction method of HOG is not rotationally invariant.
+
+We also tested the effects of testing our model on all four rotations
+of the test set.  In Figure~\ref{fig:rotation_test}, we show the AUC
+for different orientations of the datasets.  The x-axis corresponds to
+each of our three datasets, \todo{with and without the lens galaxy}.
+The y-axis shows the AUC.  The filled blue circles correspond to the
+four AUCs calculated from test scores assigned to images at one
+rotation.  The filled red stars correspond to the AUC calculated from
+the average of all four test scores, which are systematically higher
+than any one rotation.  The average score across all rotations for
+each image is likely to be less noisy for the whole test sample,
+giving an improved AUC.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:rotation_test}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/rotated_aucs/rotated_aucs.pdf}
+\caption{The AUCs of models trained on the full 10,000 and tested on
+  the holdout 1,000.  Blue circles: AUC calculated from scores of
+  images at a given rotation (e.g. 0, 90, 180, and 270 degrees).  Red
+  stars: AUC calculated from the average score of all rotations of
+  each image.  The average score produces an improved AUC in all data
+  sets.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
 \subsection{Image classification performance}\label{sec:performance}
 %-------------------------------------------------%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]\label{fig:ROCsamplesLSST10}
+\begin{center}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tp.pdf}\hspace{5pt}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fp.pdf}\\\vspace{5pt}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bp.pdf}\hspace{5pt}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/bn.pdf}\\\vspace{5pt}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/fn.pdf}\hspace{5pt}
+\includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tn.pdf}\\
+\caption{LSST mock images over 10 years. Left two columns: Lens
+  containing images, annotated with the image score assigned by our
+  trained classifier.  Right two columns: Non-lens containing images,
+  annotated with the image score.  The top two rows show
+  characteristic images that will be accepted with a high threshold
+  for classification, contributing to the bottom left of the ROC
+  curve.  The middle two rows show characteristic images that will be
+  accepted with a moderate threshold, contributing to the knee of the
+  ROC curve.  The bottom two rows show characteristic images that will
+  only be accepted with an extremely lenient threshold, contributing
+  to the top right area of the ROC curve.}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 **Redshift makes sense, but only because of the redshift distribution.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]
-  \centering \mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
-\caption{HST-like images. The left column corresponds to typical
-  lensing systems in our sample from highest scoring (top) to lowest
-  scoring, or false negatives (bottom).  The right column corresponds
-  to typical non-lensing systems in our sample from highest scoring,
-  or false positives (top), to lowest scoring (bottom).  The middle
-  row can be considered ``borderline'' classified images, where the
-  scores of the lensing and non-lensing system are very close to one
-  another.  These are systems that will be most sensitive to the
-  classification threshold.}
-\label{fig:HSTclassificationtile}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]
-  \centering
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
-}
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
-}
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
-}
-
-\caption{LSST-like images with a BCG. These illustrate the same image
-  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
-  Note, the larger PSF of LSST reduces the resolution of images,
-  making the arc-like morphology of faint images less significant and
-  increases the appearance of image-BCG blending.}
-\label{fig:LSSTBCGclassificationtile}
-\end{figure*}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%% \begin{figure*}[t]
+%%   \centering \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
+%% \caption{HST-like images. The left column corresponds to typical
+%%   lensing systems in our sample from highest scoring (top) to lowest
+%%   scoring, or false negatives (bottom).  The right column corresponds
+%%   to typical non-lensing systems in our sample from highest scoring,
+%%   or false positives (top), to lowest scoring (bottom).  The middle
+%%   row can be considered ``borderline'' classified images, where the
+%%   scores of the lensing and non-lensing system are very close to one
+%%   another.  These are systems that will be most sensitive to the
+%%   classification threshold.}
+%% \label{fig:HSTclassificationtile}
+%% \end{figure*}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%% \begin{figure*}[t]
+%%   \centering
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
+%% }
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
+%% }
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
+%% }
+
+%% \caption{LSST-like images with a BCG. These illustrate the same image
+%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
+%%   Note, the larger PSF of LSST reduces the resolution of images,
+%%   making the arc-like morphology of faint images less significant and
+%%   increases the appearance of image-BCG blending.}
+%% \label{fig:LSSTBCGclassificationtile}
+%% \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]
-  \centering
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
-}
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
-}
-
-\mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
-    \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-        clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
-}
-
-\caption{LSST-like images with no BCG. These illustrate the same image
-  classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
-\label{fig:LSSTnoBCGclassificationtile}
-\end{figure*}
+%% \begin{figure*}[t]
+%%   \centering
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
+%% }
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
+%% }
+
+%% \mbox{
+%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
+%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
+%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
+%% }
+
+%% \caption{LSST-like images with no BCG. These illustrate the same image
+%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
+%% \label{fig:LSSTnoBCGclassificationtile}
+%% \end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-07 ms.tex
Additional figure captions added

@@
 \newcommand{\comment}[1]{{\color{red} #1}}
-\newcommand{\change}[1]{{\it\color{purple} #1}}
+\newcommand{\wording}[1]{{\it\color{purple} #1}}
 \newcommand{\todo}[1]{{\bf\color{blue} #1}}
@@
 provide any classification information.  Our best performing models
-exhibit an AUC of \change{XX} for an HST-like sample.  However, for
-one orbit of LSST, our model only reaches an AUC of \change{XX}.  In
-absence of the lens galaxy in one orbit of LSST-like data, the AUC
-improves to \change{XX}.  For 10-year mock LSST observations, the
-respective AUC with and without the lens galaxy improves to
-\change{XX} and \change{XX}.  Our results show an efficient and
-effective methods for automated strong lensing identification.  The
-results also emphasize the need for further development and testing of
-additional tools to maximize use of ground-based surveys.
+exhibit an AUC of \todo{XX} for an HST-like sample.  However, for one
+orbit of LSST, our model only reaches an AUC of \todo{XX}.  In absence
+of the lens galaxy in one orbit of LSST-like data, the AUC improves to
+\todo{XX}.  For 10-year mock LSST observations, the respective AUC
+with and without the lens galaxy improves to \todo{XX} and \todo{XX}.
+Our results show efficient and effective methods for automated strong
+lensing identification with \wording{scalable linear methods that are
+  easy to parallelize with existing open source tools.}
 \end{abstract}
@@
   Sky Telescope} (LSST) images generated with PICS (Pipeline for
-Images of Cosmological Strong lensing) \citep{li_etal16}.  These
-images include cluster-member galaxies and foreground stars.  Half of
-the images used are strong lensing systems.  Here, lensed galaxy
-images are ray-traced images of actual galaxies extracted from deep
-Hubble Space Telescope observations.  The final mock images are
-``observed'' with a realistic point spread function corresponding to
-modeled detector artifacts for bright stars.  See \cite{li_etal16} for
-more details.
+Images of Cosmological Strong lensing) \citep{li_etal16} and
+LensPop\citep{collett_etal15}.  These images include cluster-member
+galaxies and foreground stars.  Half of the images used are strong
+lensing systems.  Here, lensed galaxy images are ray-traced images of
+actual galaxies extracted from deep Hubble Space Telescope
+observations.  The final mock images are ``observed'' with a realistic
+point spread function corresponding to modeled detector artifacts for
+bright stars.  See \cite{li_etal16} for more details.
 
@@
 
-To perform our analysis, we have used a variety of tools from {\em
-  Scikit-learn} \citep{pedregosa_etal12}.  We outline the
-identification pipeline in Figure~\ref{fig:pipeline}.  The first step
-of our pipeline consists of a feature extraction stage, where our
-feature vector is a {\em histogram of oriented gradients}
-\citep{dalalandtriggs_05}.  We describe the method in
-Section~\ref{sec:hog}.  We then use a machine learning algorithm to
-train a classifier model on a subset of our images.  We have explored
-both {\em Logistic Regression} (LogReg) and {\em Support Vector Machine}
-(SVM) machine learning algorithms.  We test our trained model on an
-independent subset of the images to assess the model performance.
-
-Both the feature extrator, HOG, and the classifier contain a range of
+To perform our analysis, we have used tools from {\em Scikit-learn}
+\citep{pedregosa_etal12}.  We outline the identification pipeline in
+Figure~\ref{fig:pipeline}, which is a general description of
+supervised classification.  Supervised classification is a class of
+machine learning where the labels of classification in the training
+set are known.  In our case, the labels are lens and non-lens
+containing images.
+
+The first step of our pipeline consists of a feature extraction stage,
+where our feature vector is a {\em histogram of oriented gradients}
+\citep{dalalandtriggs_05} that quantifies edges in the image.  We
+describe the method and parameter search in Section~\ref{sec:hog}.  We
+then use {\em Logistic Regression} (LR), a machine learning algorithm
+described in Section~\ref{sec:LR}, to train a classifier model on a
+subset of our images.  LR requires a parameter search over the
+regression coefficient, $C_{LogReg}$, which we explore in
+Section~\ref{sec:regularization}.  We briefly comment that tests with
+\todo{{\em Support Vector Machine} (SVM) as an alternative machine
+  learning algorithm yielded negligible performance improvement, and
+  increased computation cost.  We do not include SVM in our final
+  analysis and comparisons.}
+
+Both the feature extrator, HOG, and the linear classifier, LR, contain
 parameters, which must be tested and optimized for peak model
 performance.  We use {\em GridSearchCV} from {\em Scikit-learn} to
-select appropriate parameters, and discuss these results in
-Section~\ref{sec:gridsearch}.
+select cross-validated parameters, and discuss this step of our
+methodology in Section~\ref{sec:gridsearch}.
+
+The second step of our analysis is to test our trained model on an
+independent subset of the images to assess the model performance.
+Here, we evaluate the model on each test image, predicting a
+likelihood (``score'') between 0 and 1 that this is a lens containing
+system.  This ``holdout set'' is not used in any of our parameter
+searches to keep our test metric independent of tuning.
 
@@
 \includegraphics[scale=0.55]{figures/supervised_classification_workflow.png}
-\caption{** Cartoon of pipeline ** Mention that median filtering generates
-visual artifacts that confuse the model. http://www.nltk.org/book/ch06.html}
+\caption{** Cartoon of pipeline ** from
+  http://www.nltk.org/book/ch06.html}
 \end{center}
@@
 %-------------------------------------------------%
-Histogram oriented gradients (HOG) is a feature extraction method that
-computes centered horizontal and vertical gradients with no smoothing.
-Originally created for human detection, .... This computes the
-gradient orientation and magnitudes in an image by first dividing the
-image into $n\times n$ blocks of X\% overlap.  The gradient
-orientation is then quantized into m bins. ``(optional) global image
-normalisation computing the gradient image in x and y computing
-gradient histograms normalising across blocks flattening into a
-feature vector''\citep{dalalandtriggs_05}.
-
-% Need to look into edge orientation histograms, scale-invariant
-% feature transform descriptors, shape contexts.
-
-% NEED TO FEED THE DESCRIPTORS TO SOMETHING WITH SUPERVISED LEARNING.
-% (e.g. SVM, Neural network).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:mockimages}
-\begin{center}
-\includegraphics[width=2\columnwidth]{figures/tiles/compilations/hog_telescope_compilation.pdf}
-\caption{Left to right show example image transforms of mock images
-  from Figure~\ref{fig:mockimages} with a visualized histogram of
-  oriented gradients.  The image transform picks up edge features,
-  with arc features showing up as edges across radial orientations.}
-\end{center}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%% \begin{figure*}[t]\label{fig:hogvisual}
-%% \begin{center}
-%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
-%% \includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
-%% %\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
-%% \includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
-%% %\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
-%% \caption{Top row: Visualized HOG feature vectors of the sample lensed
-%%   HST-like image from Figure~\ref{fig:mockimages}.  Left: The
-%%   corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
-%%   pixels per cell, and (1, 1) cells per block.  Right: The HOG
-%%   visualization of the same mock image with N$_\text{orient}=9$, (16,
-%%   16) pixels per cell, and (1, 1) cells per block.  The brightest
-%%   lines align with prominent edges.  Note, while fewer pixels per cell
-%%   will better resolve the arc feature, the ``edge'' corresponding to
-%%   the arc is less prominent.  Bottom row: Visualized HOG feature
-%%   vectors for the LSST-like single epoch and stacked images with the
-%%   best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
-%%   pixels per cell, and (3, 3) cells per block.  The single epoch image
-%%   (left) does not have significant enough edge features to emerge in
-%%   the HOG, but the stacked image (right) does.}
-%% \end{center}
-%% \end{figure*}
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%-------------------------------------------------%
-\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:logreg}
-%-------------------------------------------------%
-
-Logisitic regression is a linear classifier, which finds the optimal
-hyperplane between two classes of data points.  This hyperplane
-defines the optimal model.  We must regularize the model to prevent
-overfitting.
-
-In regularization, the goal is to minimize a cost function with
-respect to ....  Larger values of $C_\text{LogReg}$ correspond to
-increasing model complexity.  Figure~\ref{fig:regularization} shows
-the accuracy of a model for selected HOG parameters as a function of
-the regularization parameter, $C_\text{LogReg}$.  We plot the
-regularization dependency for HOG parameterization of
-$N_\text{orient}=9$, $PPC=(16, 16)$, $CPB=(1,1)$.
-
-The accuracy of a model can be defined as either the score of the
-model on a test set, or the AUC for the ROC curve.
-
-% Regularization coefficient:
-% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html
-
-%-------------------------------------------------%
-\subsection{Machine Learning Algorithm: Support Vector Machine}
-%-------------------------------------------------%
-
-%-------------------------------------------------%
-%\subsection{Deep Learning Algorithm}
-%-------------------------------------------------%
-
-%-------------------------------------------------%
-\section{Results}
-\label{sec:results}
-%-------------------------------------------------%
-%-------------------------------------------------%
-\subsection{Optimized pipeline parameters}\label{sec:gridsearch}
+% HOG intro - 
+Originally created for human detection in computer vision, histogram
+oriented gradients (HOG) is a feature extraction method that computes
+centered horizontal and vertical gradients. HOG is relatively robust
+to noise in the image, and is a fairly fast transform that describes
+edges.  Details can be found in \citet{dalalandtriggs_05}, but we
+describe the procedure here.  The end result of HOG is a one
+dimensional histogram computed as follows.
+
+% Division of the image  
+HOG first divides the image into blocks of \wording{50\% overlap}.
+Each block contains $m\times m$ cells-per-block that each contain
+$n_{pix}\times n_{pix}$ pixels-per-cell.  The computed gradient
+orientation is quantized into $N_{orient}$ bins.
+
+% Initial binning
+The orientation gradient of all pixels within each cell are binned
+into the quantized orientations, providing a net gradient description
+within that cell.  As an example, for $N_{orient}=3$, our bins are
+centered at $\theta=0, 2\pi/3, 4\pi/3$ in radians.  If a cell has no
+gradient in the vertical direction, and only a gradient across the
+horizontal direction, say in the positive x-direction with
+$\theta=\pi/2$, it will contribute 75\% of its magnitude to the
+$\theta=2\pi/3$ bin, and 25\% of its magnitude to the $\theta=0$ bin.
+The bins in all cells are then concatenated to make a larger feature
+vector that is $N_{orient}$\times$N_{cells}$.
+
+% Normalization
+The last step is a normalization procedure to control for illumination
+effects.  Here, the sub-histograms of each cell within the same block
+are normalized with respect to one another before the transformation
+returns the final feature vector.  The division of the image and the
+quantization of orientations provide a total of 3 parameters in HOG:
+$N_{orient}$, cells-per-block, and pixels-per-cell.  We discuss how we
+select parameters using cross-validation in
+Section~\ref{sec:gridsearch}
+
+%-------------------------------------------------%
+\subsubsection{Optimized Pipeline Parameters with a Grid Search}\label{sec:gridsearch}
 %-------------------------------------------------%
@@
 \tablecomments{Panel (a) shows the results of a grid search across a
-  range of HOG parameters and regression coefficient with training and
-  test sets of size 1440 with the HST-like mock dataset.  Panel (b)
-  shows the corresponding results for training and test sets of size
-  5760 with the LSST mock dataset.  We explore different HOG
-  parameters in each dataset due to resolution and image size
-  differences.}
+  range of HOG parameters and regression coefficient \wording{with
+    training and test sets of size 1440 with the HST-like mock
+    dataset.}  Panel (b) shows the corresponding results for training
+  and test sets of \wording{size 5760 with the LSST mock dataset.}  We
+  explore different HOG parameters in each dataset due to resolution
+  and image size differences.}
 \end{table}
@@
 We run a grid search across parameters that should reasonably sample
-the arc edges in either the HST- or LSST-like mock observations.
-Recall, the HST-like images are $300\times300$ pixels per image, while
-the LSST-like mock observations are $45\times45$ pixels per image.  In
-general, must run a grid search in order to best optimize the pipeline
-parameters.
-
-We must first estimate the size of a cell that will contain a coherent
-arc feature.  To first order approximation, subdivisions of cells that
-are 1/100th the area of the entire image should contain coherent arc
-edges that span an elongated shape within arc-containing cells.
-Therefore, we perturb the pixels per cell parameter about (30, 30) for
-the HST-like images, and (4, 4) for the LSST-like images.
+the arc edges in either the HST- or LSST-like mock observations, and
+illustrate the results in Table~\ref{tab:gridsearch}.  Recall, the
+HST-like images are $300\times300$ pixels per image, while the
+LSST-like mock observations are $45\times45$ pixels per image.
+
+We first estimate the size of a cell that will contain a coherent arc
+feature.  To first order approximation, subdivisions of cells that are
+1/100th the area of the entire image should contain coherent arc edges
+that span an elongated shape within arc-containing cells.  Therefore,
+\wording{we perturb the pixels per cell parameter about (30, 30) for
+  the HST-like images, and (4, 4) for the LSST-like images.}
 
@@
 downweight arc-like edges in cells that neighbor very bright cells,
-such as cells that cover the BCG.  We therefore vary the cells per
-block parameter between (1, 1) and (3, 3).
+such as cells that cover the central lens galaxy.  \wording{We therefore
+  vary the cells per block parameter between (1, 1) and (3, 3).}
 
@@
 edges.  For example, if we only have two orientations, an arc-like
-feature in a cell will appear as .... However, contributions from a
-cluster or line-of-sight galaxy in the same cell will ... the
-normalizations in the histogram.  The resolution of the overall image
-will also limit the additional information that an increase in
-$N_\text{orient}$ will provide.  For the LSST-like data,
-$N_\text{orient}=9$ compared with $N_\text{orient}=5$ only
-results in a $???\%$ improvement.  In the case of the HST-like data,
-$N_\text{orient}=9$ compared with $N_\text{orient}=5$
-results in a $???\%$ improvement.
-
-Note, we also include the size of the extracted features, e.g. the
-length of the HOG feature vector.  A longer feature vector will
-increase the amount of time required to train the model.
-Additionally, for fixed memory restrictions, there is a tradeoff
-between the length of the feature vector and the size of the training
-set.  The logistic regression coefficient will also increase the
-training time, \todo{since larger coefficients correspond to a more
-  singular matrix}.  We discuss the score dependence on logistic
-regression coefficient in Section\ref{sec:regularization}.
-
-%-------------------------------------------------%
-\subsection{Receiver Operating Characteristic}
+feature in a cell directly north of the lensing galaxy will appear in
+our HOG visualization as a strong horizontal line (e.g. see top left
+in Figure~\ref{fig:hogimages}), and an arc-like feature north-east of
+the lensing galaxy will appear as an L-shape.  However, contributions
+from a cluster or line-of-sight galaxy in the same cell will tend to
+contribute edges in all orientations of the histogram (e.g. bottom
+right in Figure~\ref{fig:hogimages}).
+
+Finally, the resolution of the overall image will also limit the
+additional information that an increase in $N_\text{orient}$ will
+provide.  \wording{For the LSST-like data, the optimal orientation is
+  $N_\text{orient}=?$ compared with $N_\text{orient}=?$ only results
+  in a $???\%$ improvement.}
+
+% Impact on image performance
+The image size affects the length of the HOG feature vector, which has
+a monotonically increasing relationship with the time required to
+train the model.  Additionally, for fixed memory restrictions, there
+is a tradeoff between the length of the feature vector and the size of
+the training set.  We will discuss how the training set size affects
+the train time for each data set in Section~\ref{sec:trainsetsize}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]\label{fig:hogimages}
+\begin{center}
+\includegraphics[width=2\columnwidth]{figures/tiles/compilations/hog_telescope_compilation.pdf}
+\caption{Left to right show example image transforms of mock images
+  from Figure~\ref{fig:mockimages} with a visualized histogram of
+  oriented gradients.  The image transform picks up edge features,
+  with arc features showing up as edges across radial orientations.}
+\end{center}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%% \begin{figure*}[t]\label{fig:hogvisual}
+%% \begin{center}
+%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
+%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
+%% \includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
+%% %\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
+%% \includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
+%% %\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
+%% \caption{Top row: Visualized HOG feature vectors of the sample lensed
+%%   HST-like image from Figure~\ref{fig:mockimages}.  Left: The
+%%   corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
+%%   pixels per cell, and (1, 1) cells per block.  Right: The HOG
+%%   visualization of the same mock image with N$_\text{orient}=9$, (16,
+%%   16) pixels per cell, and (1, 1) cells per block.  The brightest
+%%   lines align with prominent edges.  Note, while fewer pixels per cell
+%%   will better resolve the arc feature, the ``edge'' corresponding to
+%%   the arc is less prominent.  Bottom row: Visualized HOG feature
+%%   vectors for the LSST-like single epoch and stacked images with the
+%%   best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
+%%   pixels per cell, and (3, 3) cells per block.  The single epoch image
+%%   (left) does not have significant enough edge features to emerge in
+%%   the HOG, but the stacked image (right) does.}
+%% \end{center}
+%% \end{figure*}
+%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%-------------------------------------------------%
+\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
+%-------------------------------------------------%
+\todo{ Logisitic regression (LR) is a linear classifier, which finds
+  the optimal hyperplane between two classes of data points.  In our
+  case, the two classes are lens and non-lens containing images.  The
+  data points are the HOG feature vectors transformed from the
+  training set data.  Each point occupies an N-dimensional space,
+  where N is the length of the HOG vector.  In fitting for the best
+  hyperplane, we must regularize the model to prevent overfitting,
+  adding an additional parameter in our parameter search,
+  regularization parameter $C_\text{LogReg}$.
+
+Regularization minimizes the a cost function with respect to ....
+Larger values of $C_\text{LogReg}$ correspond to increasing model
+complexity.  Figure~\ref{fig:regularization} shows the accuracy of a
+model for selected HOG parameters as a function of the regularization
+parameter, $C_\text{LogReg}$.
+
+The performance of a model can be measured as either the score of the
+model on a test set, or some other metric, such as the area under the
+Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).
+
+The $C_{LogReg}$ will also increase the training time, \todo{since
+  larger coefficients correspond to a more singular matrix}.  We
+discuss the score and train time dependence on logistic regression
+coefficient in Section\ref{sec:regularization}.
+}
+% Regularization coefficient:
+% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html
+
+%-------------------------------------------------%
+\section{Results}
+\label{sec:results}
+%-------------------------------------------------%
+
+%-------------------------------------------------%
+\subsection{Receiver Operating Characteristic}\label{sec:ROC}
 %-------------------------------------------------%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:PRcompilation}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/metrics/PR/PR_compilation.pdf}
+\caption{Red, blue, green: Precision-recall (PR) curves for models
+  trained on our whole 10,000 training set and tested on our holdout
+  set of 1,000.  These respectively correspond to the same models and
+  data shown in Figure~\ref{fig:ROCcompilation}.  An ideal model would
+  reach both a precision (purity) and recall (completeness) that equal
+  1.  Note, that this performance describes a data set with a 50-50
+  split between lens and non-lens containing images.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 % Logistic regression and regularization
-As described in Section~\ref{sec:logreg}, LogReg trains a model with
+As described in Section~\ref{sec:LR}, LR trains a model with
 complexity determined by the regularization parameter coefficient,
@@
 %-------------------------------------------------% 
-\subsubsection{Effects of Training Set Size}
+\subsubsection{Effects of Training Set Size}\label{sec:trainsetsize}
 %-------------------------------------------------% 
@@
 %% \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
-\subsection{BCG removed}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+
 %% \begin{figure*}[t]
@@
 
-%-------------------------------------------------%
-\subsubsection{Performance dependence on lens-model parameters}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+\subsection{Performance dependence on lens-model parameters}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%-------------------------------------------------%
+\subsubsection{Effects of Image Magnification on Scoring}
 \label{sec:peformance_lensmodel}

### 2017-03-07 ms.tex
Added nLSST10 figure and caption to compare

@@
 that span an elongated shape within arc-containing cells.  Therefore,
-\wording{we perturb the pixels per cell parameter about (30, 30) for
-  the HST-like images, and (4, 4) for the LSST-like images.}
+we sample the pixels per cell parameter from (8, 8) to (32, 32) for
+the HST-like images, and (3, 3) to (5, 5) for the LSST-like images in
+our grid search.
 
@@
 downweight arc-like edges in cells that neighbor very bright cells,
-such as cells that cover the central lens galaxy.  \wording{We therefore
-  vary the cells per block parameter between (1, 1) and (3, 3).}
+such as cells that cover the central lens galaxy.  We therefore vary
+the cells per block parameter between (2, 2) and (4, 4) for the
+LSST-like images and between (1, 1) and (4, 4) for the HST-like
+images.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:trainsize}
+\begin{figure}[t]\label{fig:trainsizeLSST10}
 \begin{center}
@@
   training set size, but train time roughly scales logarithmically.}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]\label{fig:trainsizenLSST10}
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/trainsize/nLSST10.pdf}
+\caption{Same as Figure~\ref{fig:trainsizeLSST10} for nLSST10.  For
+  small trainsize, the nLSST10 performs better than LSST10. }
 \end{center}

### 2017-03-09 ms.tex
update results to Creg

@@
 \includegraphics[scale=0.55]{figures/supervised_classification_workflow.png}
-\caption{** Cartoon of pipeline ** from
-  http://www.nltk.org/book/ch06.html}
+\caption{Cartoon of pipeline \footnote{from
+    http://www.nltk.org/book/ch06.html} for supervised classification.
+  In our case, the labels are either lens or non-lens containing
+  images.  Our input is the set of mock HST- or LSST-like
+  observations.  The feature extractor is the histogram of oriented
+  gradients, producing an N-dimensional feature vector that quantify
+  edges in our images.  Our machine learning algorithm is logistic
+  regression.}
 \end{center}
@@
 In this section, we discuss the Receiver Operating Characteristic
-(ROC) curve, which shows the true positive rate (tpr) as a function of
-false positive rate (fpr) for a given model and test set.  The true
-positive rate is defined as the number of true positives divided by
-the total number of positives (completeness of the positive
-identifications).  The false positive rate is defined as the number of
-false positives divided by the total number of negatives (impurity of
-the identifications).  The ROC curve illustrates the performance of
-our trained model as we vary the discrimination threshold.
+(ROC) curve (see Figure~\ref{fig:ROCcompilation}), which shows the
+true positive rate (tpr) as a function of false positive rate (fpr)
+for a given model and test set.  The true positive rate is defined as
+the number of true positives divided by the total number of positives
+(completeness of the positive identifications).  The false positive
+rate is defined as the number of false positives divided by the total
+number of negatives (impurity of the identifications).  The ROC curve
+illustrates the performance of our trained model as we vary the
+discrimination threshold.
 
@@
 
-% HST model performance
-Figure~\ref{fig:ROC} shows the ROC curves for three different HOG
-parameterizations for the HST-like dataset in red, green, and blue.
-The parameters and corresponding AUC for each curve are labeled in the
-legend.  The models for the HST-like dataset perform well, and have
-AUCs very close to 1.
-
-% LSST model performance
-On the other hand, the model for our LSST-like dataset (solid magenta)
-does not perform well.  The dashed diagonal like corresponds to a
-model that is as good as a random classifier, e.g. a coin-flip, for
-each test image.  The LSST-like ROC curve does marginally better, and
-the $AUC=0.527$ is within the statistical noise of the sample.
-
-% No BCG LSST
-One possible method of improving the detection of strong lensing
-systems is to model out the BCG.  The dotted magenta ROC curve
-corresponds to a model trained and tested on LSST-like data where the
-BCG has not been added to the mock image.  This model results in an
-AUC of 0.64, performing better than random.  In other words, if we
-were to perfectly model out the BCG contribution in LSST-like data, we
-could improve the performance by $\sim10\%$.
-
-% Choosing C
-The ROCs correspond to models that have been trained with logistic
-regression regularization parameter, $C_\text{LogReg}$, that best
-describes the training dataset without overfitting.  We discuss the
-choice of regularization parameter in
-Section~\ref{sec:regularizedfit}.
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%% \begin{figure}[t]\label{fig:ROCHST}
-%% \begin{center}
-%% \includegraphics[width=\columnwidth]{figures/ROC_HST_HOG.png}
-%% \caption{Red, green, blue: ROC curves for a models trained on the
-%%   HST-like data with the Logistic Regression algorithm.  The magenta
-%%   solid (dotted) curve show the ROC curve for the LSST-like data with
-%%   (without) the BCG.  The corresponding parameters are labeled: N for
-%%   number of orientations, ppc for pixels-per-cell, cpb for
-%%   cells-per-block, and C for best regularization parameter.  The AUC
-%%   for each model is also labeled in the legend, where an AUC close to
-%%   1 is a near-ideal model, and an AUC close to 0.5 is a model that
-%%   performs as well as a coin-flip.}
-%% \end{center}
-%% \end{figure}
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+% Precision-recall
+For comparison, we also show a Precision-Recall curve (see
+Figure~\ref{fig:PRcompilation}), where precision is the number of true
+positives identified as positive divided by the total number of
+positively identified images (purity) and recall is the number of true
+positives identified as positive divided by the total number of true
+positives (completeness).  Each point in the figure is calculated with
+a varying threshold for identification.  Since our sample has a class
+balance of 50-50 between positives (lens) and negatives (non-lens),
+the most lenient threshold for identification would yield a precision
+of 0.5 at a recall of 1.0.  It is important to note that this figure
+changes as the class balance changes; if we had 90\% non-lenses and
+10\% lenses, the most lenient threshold would yield a precision of 1/9
+at a recall of 1.  The ROC curve is a more typical metric for
+supervised classification.
+
+% Summary of ROC curves
+Figure~\ref{fig:ROCcompilation} shows the ROC curves for models
+trained using the entire 10,000 training sample, with best-case HOG
+and regularization parameters.  The models have been evaluated on a
+hold-out test set of 1,000 images that were not used in the parameter
+search.  We show the mock HST, LSST1, and LSST10 results respectively
+in red, blue, and green.  Solid lines correspond to a model trained
+and tested on images with the lensing galaxy.  Dashed lines correspond
+to a model trained and tested on images where the lensing galaxy is
+excluded from the mock observation, simulating an ideal modeling and
+subtraction of the lensing galaxy, which has been one proposed method
+to improve the identification of strong lensing systems.  The
+corresponding AUC is listed in the legend.
+
+% Model performance summary
+The model performance for the mock HST data is AUC=0.975 for images
+with the lens galaxy, and AUC=0.98 for images without the lens galaxy
+(red solid and dashed).  On the other hand, the model for our
+LSST-like dataset for one year has an AUC=0.625 with the lens galaxy
+and AUC=0.579 without the lens galaxy (blue solid and dashed), and the
+model for our LSST-like dataset for 10 years has an AUC=0.809 with the
+lens galaxy and AUC=0.792 without the lens galaxy (green solid and
+dashed).  Removal of the lens galaxy does not systematically perform
+better, and is actually dependent on the size of the training set.  We
+discuss relative model performance and complexity for images with and
+without the lens galaxy in Section~\ref{sec:trainsetsize}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
@@
 $C_\text{LogReg}$.  Increasing model complexity (larger
-$C_\text{LogReg}$), will better describe features in the training
-set[wc?].  However, an overly complex model will overfit the training
-set at the expense of its performance on any independent test set.
-The regularization parameter ultimately defines the model performance,
-and we must perform a parameter search to identify the optimal value
-for $C_\text{LogReg}$.
+$C_\text{LogReg}$), will better describe features in the training set.
+However, an overly complex model will overfit the training set at the
+expense of its performance on any independent test set.  The
+regularization parameter ultimately defines the model performance, and
+we must perform a parameter search to identify the optimal value for
+$C_\text{LogReg}$.
 
@@
 Figure~\ref{fig:regularization} shows the model performance as a
-function of regularization parameter.  The left panel shows the
-accuracy, or score, of the model as a function of regularization
-parameter.  The accuracy is simply the percentage of correct
-predictions, true positives and true negatives, out of a given set.
-The right panel shows the AUC of the model as a function of
-regularization parameter.  The solid and dotted lines respectively
-correspond to the model performance on the test and training set.
+function of regularization parameter for each data set HST, LSST, and
+LSST10.  The solid and dotted lines respectively correspond to the
+model performance on the test and training set.
 
@@
 % Train time with Creg
+In red, we show the train time as a function of $C_\text{LogReg}$.
 Lower Creg, more regularized, smaller volume to search for the
@@
   panel corresponds to a different mock observation.  From left to
-  right: HST, LSST for one year, and LSST for 10 years.  The xsolid
-  blue lines correspond to the AUC of the training set, and the dotted
-  blue lines to the AUC of the test set.  To avoid overfitting, we
+  right: HST, LSST for one year, and LSST for 10 years.  The solid
+  blue lines correspond to the AUC of the test set, and the dotted
+  blue lines to the AUC of the training set.  To avoid overfitting, we
   choose the smallest parameter for which the AUC of the test set is
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/trainsize/LSST10.pdf}
-\caption{Solid blue line: AUC for models with varying size of the
-  training set for LSST10.  Dotted red line: Train time for that
-  model.  The improvement of AUC scales linearly with the log of the
-  training set size, but train time roughly scales logarithmically.}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:trainsizenLSST10}
-\begin{center}
-\includegraphics[width=\columnwidth]{figures/trainsize/nLSST10.pdf}
-\caption{Same as Figure~\ref{fig:trainsizeLSST10} for nLSST10.  For
-  small trainsize, the nLSST10 performs better than LSST10. }
+\includegraphics[width=\columnwidth]{figures/trainsize/LSST10_with_nLSST10.pdf}
+\caption{Solid (dotted) blue line: AUC for models with varying size of
+  the training set for LSST10 (nLSST10).  Solid (dotted) red line:
+  Optimal regularization parameter for training on the train size for
+  LSST10 (nLSST10). The improvement of AUC scales linearly with the
+  log of the training set size, but train time roughly scales
+  logarithmically.  Note, LSST10 requires more model complexity to
+  exceed the performance of nLSST10.}
 \end{center}

### 2017-03-09 ms.tex
Finished section on logistic regression.  Citation on effect regularization parameter on training time is needed.

@@
 %-------------------------------------------------%
-\todo{ Logisitic regression (LR) is a linear classifier, which finds
-  the optimal hyperplane between two classes of data points.  In our
-  case, the two classes are lens and non-lens containing images.  The
-  data points are the HOG feature vectors transformed from the
-  training set data.  Each point occupies an N-dimensional space,
-  where N is the length of the HOG vector.  In fitting for the best
-  hyperplane, we must regularize the model to prevent overfitting,
-  adding an additional parameter in our parameter search,
-  regularization parameter $C_\text{LogReg}$.
-
-Regularization minimizes the a cost function with respect to ....
-Larger values of $C_\text{LogReg}$ correspond to increasing model
-complexity.  Figure~\ref{fig:regularization} shows the accuracy of a
+The problem of detecting gravitational lenses in images falls
+under the general category of \em{classification} in machine
+learning. In general the task is to find a function that
+assigns data points $x$ to one of two or more classes, denoted
+by the class label $y$.  This is
+equivalent to specifying a decision boundary, or decision
+boundaries between the classes in the space of the data points.
+(Compare this to
+\em{regression} in which the task is to find a function 
+$y=f(x)$, where $y$ is a continuous, rather than discrete,
+variable.) In our case, we have two classes: lens and
+non-lens containing images, and the data points $x$ are the
+HOG feature vectors transformed from the training set data.
+In this paper we use the Logisitic Regression (LR)
+algorithm, for which the decision boundary is a hyperplane .
+(The equivalent in the regression setting would be linear
+regression.) In LR we determine the optimal hyperplane by
+minimizing the objective function
+\begin{equation}
+\label{log_reg_objective}
+L(A,b) = \sum_i \log \left[1 + \exp \left(-y_i (A \cdot x_i + b) \right) \right]
+\end{equation}
+where $x_i$ is a data point (HOG feature vector), $y_i$ is the
+known label for that data point ($1$ for a lens containing
+image, $-1$ for a non-lens containing), and $A$ and $b$ are
+the parameters of the hyperplane. Eq. \ref{log_reg_objective}
+is to be minimized with respect to $A$ and $b$.
+Other more complicated machine learning algorithms exist which
+do not necessarily produce a linear decision boundary, such as
+Support Vector Machines (SVM), Random Forests, and Neural Networks.
+training set data \citep{hastie_09}.
+
+The HOG feature vectors in this paper can be very high-dimensional.
+When dealing with high-dimensional data, where the number of
+dimensions becomes comparable to the number of data points,
+overfitting can become an issue. (An example of an extreme case
+of overfitting would be if you fit a degree $n$ polynomial to $n$
+points.  The polynomial would simply wiggle so that it goes
+through every point, and would have no predictive power if you
+tried to interpolate or extrapolate.) In machine learning,
+overfitting is avoided using different \em{regularization}
+techniques. A common choice for logistic regression is to
+add a penalty term to Eq. \ref{log_reg_objective}
+\begin{equation}\ref{log_reg_regularized}
+L_\text{Reg}(A,b,C_\text{LogReg}) = L(A,b) + \frac{1}{2C_\text{LogReg}} \|A\|
+\end{equation}
+where the norm $\|A\|$ is typically taken as either the
+sum of squares of the coefficients ($L_2$ norm) or the sum
+of absolute values of the coefficients ($L_1$ norm).  In this
+paper we use the former.
+
+The amount of regularization is
+controlled by the parameter $C_\text{LogReg}$:
+larger values of $C_\text{LogReg}$ correspond to increasing model
+complexity.  If $C_\text{LogReg}$ is too large then the model will
+overfit, and if it is too small the model will underfit.
+To determine whether a model is overfit or underfit, the model is
+trained, (i.e. Eq. \ref{log_reg_regularized} is minimized), on a
+subset of the data called the \em{training set} and its performance
+(goodness of fit) is evaluated both on the the training set and
+a set of hold-out data called the \em{test set} that was not used
+in constructing the model.
+Figure~\ref{fig:regularization} shows the performance of a
 model for selected HOG parameters as a function of the regularization
-parameter, $C_\text{LogReg}$.
-
-The performance of a model can be measured as either the score of the
-model on a test set, or some other metric, such as the area under the
-Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).
-
-The $C_{LogReg}$ will also increase the training time, \todo{since
-  larger coefficients correspond to a more singular matrix}.  We
-discuss the score and train time dependence on logistic regression
-coefficient in Section\ref{sec:regularization}.
-}
-% Regularization coefficient:
-% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html
+parameter, $C_\text{LogReg}$, for both the training and the test set.
+(The performance can be measured by the accuracy, i.e. percent of
+images correctly classified, or by some other metric,
+such as the area under the
+Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).)
+
+When $C_\text{LogReg}$ is small, the performance of the model improves
+with increasing $C_\text{LogReg}$ on both the training and test set,
+meaning that $C_\text{LogReg}$ is
+still in the underfitting regime. Eventually the performance on the
+test set reaches a maximum and starts to decrease, even while the
+performance on the training set continues to increase.  This means
+that the model is no longer generalizing well and is starting to
+overfit. The optimal $C_\text{LogReg}$ occurs when the performance
+of the test set is at its maximum; this is the value of $C_\text{LogReg}$
+that should be used in the final model.
+
+In practice, there is something of a trade-off between accuracy and
+computational resources because a larger value of $C_\text{LogReg}$
+will also increase the training time, since a larger $C_\text{LogReg}$
+corresponds to a less constrained parameter space being searched
+\todo{(citation needed)}.
+We discuss the performance and training time dependence on $C_\text{LogReg}$
+in Section\ref{sec:regularization}.
 

### 2017-03-09 ms.tex
Finished subsection on regularization and model performance

@@
 %-------------------------------------------------%
-The problem of detecting gravitational lenses in images falls
-under the general category of \em{classification} in machine
-learning. In general the task is to find a function that
-assigns data points $x$ to one of two or more classes, denoted
-by the class label $y$.  This is
-equivalent to specifying a decision boundary, or decision
-boundaries between the classes in the space of the data points.
-(Compare this to
-\em{regression} in which the task is to find a function 
-$y=f(x)$, where $y$ is a continuous, rather than discrete,
-variable.) In our case, we have two classes: lens and
-non-lens containing images, and the data points $x$ are the
-HOG feature vectors transformed from the training set data.
-In this paper we use the Logisitic Regression (LR)
-algorithm, for which the decision boundary is a hyperplane .
-(The equivalent in the regression setting would be linear
-regression.) In LR we determine the optimal hyperplane by
-minimizing the objective function
+The problem of detecting gravitational lenses in images falls under
+the general category of {\em{classification}} in machine learning. In
+general the task is to find a function that assigns data points $x$ to
+one of two or more classes, denoted by the class label $y$.  This is
+equivalent to specifying a decision boundary, or decision boundaries
+between the classes in the space of the data points.  (Compare this to
+{\em{regression}} in which the task is to find a function $y=f(x)$,
+where $y$ is a continuous, rather than discrete, variable.) In our
+case, we have two classes: lens and non-lens containing images, and
+the data points $x$ are the HOG feature vectors transformed from the
+training set data.  In this paper we use the Logisitic Regression (LR)
+algorithm, for which the decision boundary is a hyperplane .  (The
+equivalent in the regression setting would be linear regression.) In
+LR we determine the optimal hyperplane by minimizing the objective
+function
 \begin{equation}
-\label{log_reg_objective}
+\label{eqn:log_reg_objective}
 L(A,b) = \sum_i \log \left[1 + \exp \left(-y_i (A \cdot x_i + b) \right) \right]
@@
 image, $-1$ for a non-lens containing), and $A$ and $b$ are
-the parameters of the hyperplane. Eq. \ref{log_reg_objective}
+the parameters of the hyperplane. Eq. \ref{eqn:log_reg_objective}
 is to be minimized with respect to $A$ and $b$.
@@
 tried to interpolate or extrapolate.) In machine learning,
-overfitting is avoided using different \em{regularization}
+overfitting is avoided using different {\em{regularization}}
 techniques. A common choice for logistic regression is to
-add a penalty term to Eq. \ref{log_reg_objective}
-\begin{equation}\ref{log_reg_regularized}
+add a penalty term to Equation~\ref{eqn:log_reg_objective}
+\begin{equation}\label{eqn:log_reg_regularized}
 L_\text{Reg}(A,b,C_\text{LogReg}) = L(A,b) + \frac{1}{2C_\text{LogReg}} \|A\|
@@
 
-The amount of regularization is
-controlled by the parameter $C_\text{LogReg}$:
-larger values of $C_\text{LogReg}$ correspond to increasing model
-complexity.  If $C_\text{LogReg}$ is too large then the model will
-overfit, and if it is too small the model will underfit.
-To determine whether a model is overfit or underfit, the model is
-trained, (i.e. Eq. \ref{log_reg_regularized} is minimized), on a
-subset of the data called the \em{training set} and its performance
-(goodness of fit) is evaluated both on the the training set and
-a set of hold-out data called the \em{test set} that was not used
-in constructing the model.
-Figure~\ref{fig:regularization} shows the performance of a
-model for selected HOG parameters as a function of the regularization
-parameter, $C_\text{LogReg}$, for both the training and the test set.
-(The performance can be measured by the accuracy, i.e. percent of
-images correctly classified, or by some other metric,
-such as the area under the
-Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).)
+The amount of regularization is controlled by the parameter
+$C_\text{LogReg}$: larger values of $C_\text{LogReg}$ correspond to
+increasing model complexity.  If $C_\text{LogReg}$ is too large then
+the model will overfit, and if it is too small the model will
+underfit.  To determine whether a model is overfit or underfit, the
+model is trained, (i.e. Eq. \ref{eqn:log_reg_regularized} is
+minimized), on a subset of the data called the {\em{training set}} and
+its performance (goodness of fit) is evaluated both on the the
+training set and a set of hold-out data called the {\em{test set}}
+that was not used in constructing the model.
+Figure~\ref{fig:regularization} shows the performance of a model for
+selected HOG parameters as a function of the regularization parameter,
+$C_\text{LogReg}$, for both the training and the test set.  (The
+performance can be measured by the accuracy, i.e. percent of images
+correctly classified, or by some other metric, such as the area under
+the Receiver Operating Characteristic curve (see
+Section~\ref{sec:ROC}).)
 
@@
 complexity determined by the regularization parameter coefficient,
-$C_\text{LogReg}$.  Increasing model complexity (larger
-$C_\text{LogReg}$), will better describe features in the training set.
-However, an overly complex model will overfit the training set at the
-expense of its performance on any independent test set.  The
-regularization parameter ultimately defines the model performance, and
-we must perform a parameter search to identify the optimal value for
-$C_\text{LogReg}$.
+$C_\text{LogReg}$.  Larger values of $C_\text{LogReg}$ are less
+regularized and allow for increased model complexity.  The highest
+values of $C_\text{LogReg}$ will better describe features in the
+training set.  However, an overly complex model will overfit the
+training set at the expense of its performance on any independent test
+set.  The regularization parameter ultimately defines the model
+performance, and we must perform a parameter search to identify the
+optimal value for $C_\text{LogReg}$.
 
@@
 function of regularization parameter for each data set HST, LSST, and
-LSST10.  The solid and dotted lines respectively correspond to the
-model performance on the test and training set.
+LSST10.  The solid and dotted blue lines respectively correspond to
+the model performance on the test and training set, with the AUC as a
+metric for performance.  In red, we show the train time as a function
+of $C_{LogReg}$.
 
 % Training behavior with C
-For either characterization of the model, the model performance on the
-training set increases and asymptotes with $C_\text{LogReg}$.  With
-increasing model complexity, the model better fits the data set it has
-been trained on.  This is analogous to fitting a seventh order
-polynomial to seven data points, where the fitting function will go
-through every point but will not likely predict additional points.
-
-% Test behavior with C
-We use the model performance on a test set to determine the best value
-for $C_\text{LogReg}$ that will not overfit the training data.  With
-increasing model complexity, we are able to better able to capture
-features that are generally characteristic of strong lensing systems
-with arcs.  However, past a certain $C_\text{LogReg}$, the model
-performance on the test set decreases or asymptotes, as it has overfit
-the training set.
+As expected, the training set increases and asymptotes with
+$C_\text{LogReg}$.  With increasing model complexity, the model better
+fits the training data set.  This is analogous to fitting a seventh
+order polynomial to seven data points, where the fitting function will
+go through every point but will not likely predict additional points.
+With increasing model complexity, we are able to better able to
+capture features that are generally characteristic of strong lensing
+systems with arcs. However, past a certain $C_\text{LogReg}$, the
+model performance on the test set decreases or asymptotes, as it has
+overfit the training set.  We use the scaling of AUC with
+$C_\text{LogReg}$ when training 8,000 out of our full 10,000 training
+data set to determine the best value for $C_\text{LogReg}$.  However,
+the optimal parameter is also dependent on the size of the training
+set (see Section~\ref{sec:trainsetsize}), so this choice is not
+generalizable.
 
 % Train time with Creg
-In red, we show the train time as a function of $C_\text{LogReg}$.
-Lower Creg, more regularized, smaller volume to search for the
-solution (best fit coefficients), so faster on average.  But, still
-has some randomness associated with the path it takes to convergence
-(not purely monotonic).
+For fixed train size, the log of the train time roughly scales
+linearly with the log of $C_\text{LogReg}$.  Since lower values of
+$C_\text{LogReg}$ correspond to a more regularized model, there is a
+smaller volume in hyperparameter space to search for the best fit
+coefficients.  The solution, on average, will converge more quickly,
+for more regularized models.  The scaling is not purely monotonic
+because the fitting still has some randomness associated with the path
+it takes to convergence.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:regularization}
+\begin{figure*}[t]
 \begin{center}
@@
   we show the train time of the model, which roughly increases in a
-  log-log scaling with logistic regression coefficient parameter.}
+  log-log scaling with logistic regression coefficient
+  parameter.}\label{fig:regularization}
 \end{center}
@@
 In this section, we show the effects of training set size on model
-performance.  Figure~\ref{fig:trainsize} shows the AUC and the train
-time depend on the log of the size of the training set.  In solid blue
-lines, we see that the AUC improves almost linearly with the log of
-the training size set.  In dotted red, we see that the train time
-roughly scales logarithmically with the log of the train size, with an
-exception of the data point corresponding to train size of 2000.
+performance.  Figure~\ref{fig:trainsizeLSST10} shows how the AUC and
+the logistic regression coefficient depend on the log of the size of
+the training set.  In solid blue lines, we see that the AUC improves
+almost linearly with the log of the training size set.  In dotted red,
+we see that the train time roughly scales logarithmically with the log
+of the train size, with an exception of the data point corresponding
+to train size of 2000.
 
@@
 2000, the optimal regularization parameter happened to be
-$C_{LR}=100$, whereas it was $C_{LR}=500$ for the subset of trainsize
-1000, and $C_{LR}=1000$ for the subset of trainsize 4000.
+$C_{LogReg}=100$, whereas it was $C_{LogReg}=500$ for the subset of trainsize
+1000, and $C_{LogReg}=1000$ for the subset of trainsize 4000.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:trainsizeLSST10}
+\begin{figure}[t]
 \begin{center}
@@
   logarithmically.  Note, LSST10 requires more model complexity to
-  exceed the performance of nLSST10.}
+  exceed the performance of nLSST10.}\label{fig:trainsizeLSST10}
 \end{center}

### 2017-03-09 ms.tex
Finished subsection on training set size and model performance/model train time

@@
 $AUC=1.0$ is an ideal trained classifier, and $AUC=0.5$ does not
-provide any classification information.  Our best performing models
-exhibit an AUC of \todo{XX} for an HST-like sample.  However, for one
-orbit of LSST, our model only reaches an AUC of \todo{XX}.  In absence
-of the lens galaxy in one orbit of LSST-like data, the AUC improves to
-\todo{XX}.  For 10-year mock LSST observations, the respective AUC
-with and without the lens galaxy improves to \todo{XX} and \todo{XX}.
-Our results show efficient and effective methods for automated strong
-lensing identification with \wording{scalable linear methods that are
-  easy to parallelize with existing open source tools.}
+provide any classification information.  Our best performing models on
+a training set of 10,000 lens containing images and 10,000 non-lens
+containing images exhibit an AUC of 0.975 for an HST-like sample.
+However, for one orbit of LSST, our model only reaches an AUC of
+0.625.  For 10-year mock LSST observations, the AUC improves to 0.809.
+Model performance appears to continually improve with the size of the
+training set.  Models trained on fewer images perform better in
+absence of the lens galaxy, which can decrease the false positive rate
+by blending with light from a lensed galaxy image near the central
+lensing galaxy.  However, with larger training data sets, information
+from the lensing galaxy improves model performance.  \wordchoice{Our
+  results show efficient and effective methods for automated strong
+  lensing identification with scalable linear methods that are easy to
+  parallelize with existing open source tools and are reproducible on
+  personal laptop computers.}
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:ROCcompilation}
+\begin{figure}[t]
 \begin{center}
@@
   legend. $AUC=1$ is a perfect model, and $AUC=0.5$ is a useless
-  model.}
+  model.}\label{fig:ROCcompilation}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:PRcompilation}
+\begin{figure}[t]
 \begin{center}
@@
   1.  Note, that this performance describes a data set with a 50-50
-  split between lens and non-lens containing images.}
+  split between lens and non-lens containing
+  images.}\label{fig:PRcompilation}
 \end{center}
@@
 %-------------------------------------------------%
+
 In this section, we show the effects of training set size on model
-performance.  Figure~\ref{fig:trainsizeLSST10} shows how the AUC and
-the logistic regression coefficient depend on the log of the size of
-the training set.  In solid blue lines, we see that the AUC improves
-almost linearly with the log of the training size set.  In dotted red,
-we see that the train time roughly scales logarithmically with the log
-of the train size, with an exception of the data point corresponding
-to train size of 2000.
-
-Each model was trained with the same HOG parameterization from the
+performance on the holdout test set of 1,000 images.  We also compare
+the improvement between images that include the lens galaxy and images
+with no lens galaxy.
+
+Figure~\ref{fig:trainsizeLSST10} shows how the AUC and the optimal
+logistic regression coefficient depend on the log of the size of the
+training set for both the LSST10 data in solid blue lines, and the
+nLSST10 data in dashed blue lines.  The AUC for models trained on the
+LSST10 data improves almost linearly with the log of the training set
+size, increasing from AUC=0.705 to AUC=0.788 when the train size is
+increased from 500 lens/non-lens images to 8000 lens/non-lens images.
+However, for the nLSST10 data, where the lens galaxy has been removed
+from the images, the improvement is less dramatic.  With the same
+increase in training size, the AUC for nLSST10 changes from just below
+0.77 to just below 0.78.
+
+In solid red, we see that the optimal value for $C_\text{LogReg}$ for
+LSST10 roughly scales logarithmically with the log of the train size,
+with an exception of the data point corresponding to train size of
+2000.  Generally, a larger training set will require an increase in
+model complexity to capture additional information.  This is also true
+for the optimal $C_\text{LogReg}$ dependence on the number of training
+images in the nLSST10 data.  But, the required complexity is
+systematically less than for the LSST10 images.
+
+% Comparison of the two LSST10 vs. nLSST10
+In the LSST10 case, the trained model can incorporate the additional
+information of the edges from the lens galaxy, which is correlated
+with the lensing cross-section and likelihood of the image being a
+lensing system.  The nLSST10 images do not contain this information,
+but provide cleaner signals of the lensed image for lensed images that
+occur close to the lens galaxy.  The cleaner signal in nLSST10 allows
+for better model performance for smaller training data set sizes
+($N_\text{train}\sim5,000$).  However, models trained on LSST10
+improve more rapidly with train size, since the additional information
+from the lens galaxy better describes the lens containing images.  For
+$N_\text{train}\gsim 5,000$, the models trained on LSST10 outperform
+  those trained on nLSST10.
+
+%M Model complexity, train time, and performance
+Since the models that contain information from the lens galaxy edges
+in LSST10 are more complex, the models require a larger training set
+size for a better fit.  While model performance for LSST10 appears to
+steadily increase, this comes at the cost of increased train time,
+which is two-fold.  The train time will increase due to both an
+increase in data to fit, and also an increase in optimal
+$C_\text{LogReg}$ where the volume of hyperparameter space for allowed
+solutions is larger (see red lines in
+Figure~\ref{fig:regularization}).
+
+% Train time
+Figure~\ref{fig:traintimeLSST10} shows the train time for LSST10 and
+nLSST10 as a function of the size of the training set for the optimal
+regularization parameter for that subset training data.  Each model
+uses features extracted with the same HOG parameterization from the
 grid search and the optimal regularization parameter for that subset
@@
 increasing regularization parameter.  For the subset of train size
-2000, the optimal regularization parameter happened to be
-$C_{LogReg}=100$, whereas it was $C_{LogReg}=500$ for the subset of trainsize
-1000, and $C_{LogReg}=1000$ for the subset of trainsize 4000.
-
-% Scores vs. regularization on larger train/test set with comparable
+$N_\text{train}=2000$ in LSST10, the optimal regularization parameter
+happened to be $C_{LogReg}=100$, whereas it was $C_{LogReg}=500$ for
+the subset of trainsize 1000, and $C_{LogReg}=1000$ for the subset of
+trainsize 4000.  This makes the train time increase at train size
+$N_\text{train}=2000$ for LSST10 less dramatic than the average
+log-log slope of approximately 2.
+
+% Train time behavior for nLSST10
+Since nLSST10 does not contain the lens galaxies, fewer of the
+extracted features describe the lensing system, requiring decreased
+model complexity.  The increase in train time for nLSST10 as a
+function of train size is mostly due to only having more data to fit
+in the regression, leading to a steady and slow increase of train time
+with number of training images with log-log slope of approximately 1.
+
+% AUC vs. regularization on larger train/test set with comparable
 % grid search in parameterization
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=\columnwidth]{figures/traintime/LSST10.pdf}
+\caption{Solid (dotted) blue line: Train time for models with varying
+  size of the training set for LSST10 (nLSST10).  Train time roughly
+  scales logarithmically.  Note, LSST10 requires more model complexity
+  to exceed the performance of nLSST10, and therefore requires more
+  training time for continual increase in
+  performance.}\label{fig:traintimeLSST10}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %-------------------------------------------------% 
@@
 To augment our training set, we rotated each image in the set by
-multiples of $90^o$.  The augmentation (factor of four) naturally
-optimizes the use of available training data, since our feature
-extraction method of HOG is not rotationally invariant.
+multiples of $90^o$.  Augmenting our data by a factor of four
+naturally optimizes the use of available training data, since our
+feature extraction method of HOG is not rotationally invariant.
 
@@
 \includegraphics[width=\columnwidth]{figures/rotated_aucs/rotated_aucs.pdf}
-\caption{The AUCs of models trained on the full 10,000 and tested on
-  the holdout 1,000.  Blue circles: AUC calculated from scores of
-  images at a given rotation (e.g. 0, 90, 180, and 270 degrees).  Red
-  stars: AUC calculated from the average score of all rotations of
-  each image.  The average score produces an improved AUC in all data
-  sets.}
+\caption{Our summary figure: The AUCs of models trained on the full
+  10,000 and tested on the holdout 1,000.  Blue circles: AUC
+  calculated from scores of images at a given rotation (e.g. 0, 90,
+  180, and 270 degrees).  Red stars: AUC calculated from the average
+  score of all rotations of each image.  The average score produces an
+  improved AUC in all data sets.}
 \end{center}
@@
 \includegraphics[width=.8\columnwidth]{figures/tiles/compilations/LSST10/tn.pdf}\\
-\caption{LSST mock images over 10 years. Left two columns: Lens
-  containing images, annotated with the image score assigned by our
-  trained classifier.  Right two columns: Non-lens containing images,
+\caption{LSST 10 year mock images. Left two columns: Lens containing
+  images, annotated with the image score assigned by our trained
+  classifier.  Right two columns: Non-lens containing images,
   annotated with the image score.  The top two rows show
   characteristic images that will be accepted with a high threshold
-  for classification, contributing to the bottom left of the ROC
-  curve.  The middle two rows show characteristic images that will be
-  accepted with a moderate threshold, contributing to the knee of the
-  ROC curve.  The bottom two rows show characteristic images that will
-  only be accepted with an extremely lenient threshold, contributing
-  to the top right area of the ROC curve.}
+  for classification, contributing to the bottom left of the ROC curve
+  in Figure~\ref{fig:ROCcompilation}.  The middle two rows show
+  characteristic images that will be accepted with a moderate
+  threshold, contributing to the knee of the ROC curve, with true
+  positive rates and false positive rates of $tpr\approx0.8$ and
+  $fpr\approx0.2$, respectively.  The bottom two rows show
+  characteristic images that will only be accepted with an extremely
+  lenient threshold, contributing to the top right area of the ROC
+  curve.}
 \end{center}

### 2017-03-09 ms.tex
Finished subsection on rotations - short one

@@
 lensing galaxy.  However, with larger training data sets, information
-from the lensing galaxy improves model performance.  \wordchoice{Our
+from the lensing galaxy improves model performance.  \wording{Our
   results show efficient and effective methods for automated strong
@@
   oriented gradients.  The image transform picks up edge features,
-  with arc features showing up as edges across radial orientations.}
+  with arc features showing up as edges across radial orientations.
+  \wording{Each of the oriented gradients within a cell is
+    color-coded by magnitude, and represented as a line in the
+    direction perpendicular to that gradient.}  The actual extracted
+  features fill a one-dimensional feature vector comprised of the
+  magnitudes of each of the oriented edges within the visualized
+  cells.}
 \end{center}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%% \begin{figure*}[t]\label{fig:hogvisual}
-%% \begin{center}
-%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
-%% \includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
-%% \includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
-%% %\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
-%% \includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
-%% %\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
-%% \caption{Top row: Visualized HOG feature vectors of the sample lensed
-%%   HST-like image from Figure~\ref{fig:mockimages}.  Left: The
-%%   corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
-%%   pixels per cell, and (1, 1) cells per block.  Right: The HOG
-%%   visualization of the same mock image with N$_\text{orient}=9$, (16,
-%%   16) pixels per cell, and (1, 1) cells per block.  The brightest
-%%   lines align with prominent edges.  Note, while fewer pixels per cell
-%%   will better resolve the arc feature, the ``edge'' corresponding to
-%%   the arc is less prominent.  Bottom row: Visualized HOG feature
-%%   vectors for the LSST-like single epoch and stacked images with the
-%%   best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
-%%   pixels per cell, and (3, 3) cells per block.  The single epoch image
-%%   (left) does not have significant enough edge features to emerge in
-%%   the HOG, but the stacked image (right) does.}
-%% \end{center}
-%% \end{figure*}
+%% \caption{Top row: Visualized HOG feature vectors of the sample
+%%   lensed HST-like image from Figure~\ref{fig:mockimages}.  Left:
+%%   The corresponding HOG visualization with N$_\text{orient}=5$,
+%%   (32, 32) pixels per cell, and (1, 1) cells per block.  Right: The
+%%   HOG visualization of the same mock image with
+%%   N$_\text{orient}=9$, (16, 16) pixels per cell, and (1, 1) cells
+%%   per block.  The brightest lines align with prominent edges.
+%%   Note, while fewer pixels per cell will better resolve the arc
+%%   feature, the ``edge'' corresponding to the arc is less prominent.
+%%   Bottom row: Visualized HOG feature vectors for the LSST-like
+%%   single epoch and stacked images with the best scoring HOG
+%%   parameterization of N$_\text{orient}=4$, (3, 3) pixels per cell,
+%%   and (3, 3) cells per block.  The single epoch image (left) does
+%%   not have significant enough edge features to emerge in the HOG,
+%%   but the stacked image (right) does.}  \end{center} \end{figure*}
 %%   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %-------------------------------------------------%
-\subsection{Effects of Dataset Size on Model Performance}\label{sec:datasize}
-%-------------------------------------------------% 
-%-------------------------------------------------% 
-\subsubsection{Effects of Training Set Size}\label{sec:trainsetsize}
+\subsection{Dataset Size Dependence}\label{sec:datasize}
+%-------------------------------------------------% 
+%-------------------------------------------------% 
+\subsubsection{Effects of Training Set Size on Performance and Train Time}\label{sec:trainsetsize}
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
+
+% Augmenting dataset
 To augment our training set, we rotated each image in the set by
@@
 naturally optimizes the use of available training data, since our
-feature extraction method of HOG is not rotationally invariant.
-
-We also tested the effects of testing our model on all four rotations
-of the test set.  In Figure~\ref{fig:rotation_test}, we show the AUC
-for different orientations of the datasets.  The x-axis corresponds to
-each of our three datasets, \todo{with and without the lens galaxy}.
-The y-axis shows the AUC.  The filled blue circles correspond to the
-four AUCs calculated from test scores assigned to images at one
-rotation.  The filled red stars correspond to the AUC calculated from
-the average of all four test scores, which are systematically higher
-than any one rotation.  The average score across all rotations for
-each image is likely to be less noisy for the whole test sample,
-giving an improved AUC.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure}[t]\label{fig:rotation_test}
+feature extraction method of HOG is not rotationally invariant.  This
+has an equivalent improvement to the study illustrated in
+Figure~\ref{fig:trainsizeLSST10}.
+
+% Rotations of the test set
+We also tested the effects of evaluating our model on all four
+rotations of the test set, and using the average score of each test
+image to calculate the AUC.  In Figure~\ref{fig:rotation_test}, we
+show the AUC for different orientations of the datasets.  The x-axis
+corresponds to each of our three datasets, with and without the lens
+galaxy.  The y-axis shows the AUC.  The filled blue circles correspond
+to the four AUCs calculated when the model evaluated images at each of
+the four rotations.  The filled red stars correspond to the AUC
+calculated from the average of all four test scores, which are
+systematically higher than any one rotation.  The average score across
+all rotations for each image is likely to be less noisy for the whole
+test sample, giving an improved AUC.
+
+% Summary figure
+Figure~\ref{fig:rotation_test} also summarizes the best-case results
+of our models trained on our entire 10,000 training sets, and tested
+on our holdout 1,000 test set.  Recall, however, that we expect model
+performance on images containing the lens galaxy to improve further
+with larger training sets (see Figure~\ref{fig:trainsizeLSST10}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]
 \begin{center}
@@
   score of all rotations of each image.  The average score produces an
-  improved AUC in all data sets.}
+  improved AUC in all data sets.  We expect the AUC to further improve
+  with increased train size.}\label{fig:rotation_test}
 \end{center}

### 2017-03-09 ms.tex
Added first two paragraphs to discussion

@@
 regression coefficient, $C_{LogReg}$, which we explore in
-Section~\ref{sec:regularization}.  We briefly comment that tests with
-\todo{{\em Support Vector Machine} (SVM) as an alternative machine
-  learning algorithm yielded negligible performance improvement, and
-  increased computation cost.  We do not include SVM in our final
-  analysis and comparisons.}
+Section~\ref{sec:regularization}.  We briefly comment that our initial
+tests with {\em Support Vector Machine} (SVM) as an alternative
+machine learning algorithm yielded negligible performance improvement,
+and significantly increased computation cost.  This indicated that the
+features of lens and non-lens images are relatively well separated by
+hyperplanes in feature space.  For these reasons, we do not include
+SVM in our final analysis and comparisons and continue all discussions
+with a linear classifier.
 
@@
 additional information that an increase in $N_\text{orient}$ will
-provide.  \wording{For the LSST-like data, the optimal orientation is
-  $N_\text{orient}=?$ compared with $N_\text{orient}=?$ only results
-  in a $???\%$ improvement.}
+provide.  The best case number of orientations for each dataset is
+$N_\text{orient,HST}=9$, $N_\text{orient,LSST10}=3$, \todo{and
+  $N_\text{orient,LSST1}=$.}
 
 % Impact on image performance
-The image size affects the length of the HOG feature vector, which has
-a monotonically increasing relationship with the time required to
-train the model.  Additionally, for fixed memory restrictions, there
-is a tradeoff between the length of the feature vector and the size of
-the training set.  We will discuss how the training set size affects
-the train time for each data set in Section~\ref{sec:trainsetsize}.
+The image resolution affects the length of the HOG feature vector,
+which has a monotonically increasing relationship with the time
+required to train the model.  Additionally, for fixed memory
+restrictions, there is a tradeoff between the length of the feature
+vector and the size of the training set.  We will discuss how the
+training set size affects the train time for each data set in
+Section~\ref{sec:trainsetsize}.
 
@@
 Since nLSST10 does not contain the lens galaxies, fewer of the
-extracted features describe the lensing system, requiring decreased
-model complexity.  The increase in train time for nLSST10 as a
-function of train size is mostly due to only having more data to fit
-in the regression, leading to a steady and slow increase of train time
-with number of training images with log-log slope of approximately 1.
+extracted features describe the lens system, requiring decreased model
+complexity.  The increase in train time for nLSST10 as a function of
+train size is mostly due to only having more data to fit in the
+regression, leading to a steady and slow increase of train time with
+number of training images with log-log slope of approximately 1.
 
@@
 %-------------------------------------------------%
-\subsection{Image classification performance}\label{sec:performance}
-%-------------------------------------------------%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:ROCsamplesLSST10}
+\subsection{Image Classification Performance}\label{sec:performance}
+%-------------------------------------------------%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure*}[t]
 \begin{center}
@@
   lenient threshold, contributing to the top right area of the ROC
-  curve.}
+  curve.}\label{fig:ROCsamplesLSST10}
 \end{center}
@@
 
-**Redshift makes sense, but only because of the redshift distribution.
---> Zahid+15 quiescent.... this is where redshifts are from.
-
+\subsubsection{Populating the ROC Curve}
 % Defining the 6 paradigms of classification
@@
 is most and least able to successfully classify.  We have six
-paradigms of model performance on the mock images, \todo{and include a
-larger compilation of each of the six image classification paradigms
-in the Appendix for the various models we have trained}.
-
-% TP and TN
-Figure ~\ref{fig:HSTclassificationtile} shows a tile of representative
-HST-like images classified with the model, HST:N5ppc32cpb4C100.  The
-left column show lensing systems, and right column non-lensing
-systems.  From top to bottom, the images are ordered from highest
-scoring to lowest scoring with the classification model.  The top left
-is what we would call a ``true positive'', a lensing system that will
-always classified as positive because of its high score.  Most of the
-highest scoring lensing systems exhibit similar extended arcs
-corresponding to a large magnification (see
-Section~\ref{sec:peformance_lensmodel}).  The bottom right is a ``true
-negative'', a non-lensing system that will likely be classified as
-negative because of its low score.  Many of the lowest scoring
-non-lensing systems have \todo{fairly small BCGs, which are non likely
-  to lens a background galaxy.}
-
-% FN and FP
-The bottom left corresponds to a likely ``false negative,'' or a
-lensing system that is likely to be mis-classified as a negative.  The
-lowest scoring lensing systems tend to have images with smaller
-magnification that are minorly distorted, mimicking the shape of
-line-of-sight galaxies that the model has learned to ignore.  The top
-right corresponds to a likely ``false positive,'' or a non-lensing
-system that is likely to be mis-classified as a positive.  False
-positives tend to have ``fuzzy'' along the line of sight galaxies that
-mimic lensing arcs.  The false positives should be from bright
-galaxies along the line of sight.  \todo{The highest scoring
-  non-lensing systems often have fairly bright disk shaped galaxies
-  along the line of sight.  Visually, these are also virtually
-  indistinguishable from a lensed image and would require
-  spectroscopic follow-up.}
-
-% BP and BN
-The middle row are images whose classification will be most sensitive
-to the classification threshold.  We call these borderline images,
-with the left corresponding to a ``borderline positive'', and the
-right corresponding to a ``borderline negative''.  They sit around the
-knee of the ROC curve, the optimal threshold for purity and
-completeness.  Note that the ROC curve for HST:N5ppc32cpb4C100
-illustrates that we can lower the classification threshold and improve
-the true positive rate by $\sim10\%$ and sacrifice an increase in
-false positive rate by $\lsim5\%$.  However, small perturbations
-around the knee will either include or disinclude the middle row
-images.  These are the systems that would make good candidates for
-visual and/or spectroscopic follow-up.
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%% \begin{figure*}[t]
-%%   \centering \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1787_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1354_unlensed_imgs_1.pdf}} } \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1052_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1994_unlensed_imgs_1.pdf}} } \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1862_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/HST/1723_unlensed_imgs_1.pdf}} }
-%% \caption{HST-like images. The left column corresponds to typical
-%%   lensing systems in our sample from highest scoring (top) to lowest
-%%   scoring, or false negatives (bottom).  The right column corresponds
-%%   to typical non-lensing systems in our sample from highest scoring,
-%%   or false positives (top), to lowest scoring (bottom).  The middle
-%%   row can be considered ``borderline'' classified images, where the
-%%   scores of the lensing and non-lensing system are very close to one
-%%   another.  These are systems that will be most sensitive to the
-%%   classification threshold.}
-%% \label{fig:HSTclassificationtile}
-%% \end{figure*}
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%% \begin{figure*}[t]
-%%   \centering
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1204_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1534_unlensed_imgs_1.pdf}}
-%% }
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1384_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1703_unlensed_imgs_1.pdf}} 
-%% }
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1641_lensed_imgs_1.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/BCG/lsst_stack_1518_unlensed_imgs_1.pdf}} 
-%% }
-
-%% \caption{LSST-like images with a BCG. These illustrate the same image
-%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.
-%%   Note, the larger PSF of LSST reduces the resolution of images,
-%%   making the arc-like morphology of faint images less significant and
-%%   increases the appearance of image-BCG blending.}
-%% \label{fig:LSSTBCGclassificationtile}
-%% \end{figure*}
-
-%% \begin{figure*}[t]
-%%   \centering
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_1957_lensed_imgs_0.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1098.pdf}}
-%% }
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_1634_lensed_imgs_0.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1664.pdf}} 
-%% }
-
-%% \mbox{
-%%     \subfigure{\includegraphics[width=\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_1629_lensed_imgs_0.pdf}}\hfill
-%%     \subfigure{\includegraphics[width=1\columnwidth,trim=120 50 0 0,
-%%         clip]{figures/LSST/noBCG/lsst_stack_stamps_1399.pdf}} 
-%% }
-
-%% \caption{LSST-like images with no BCG. These illustrate the same image
-%%   classification paradigms as Figure~\ref{fig:HSTclassificationtile}.}
-%% \label{fig:LSSTnoBCGclassificationtile}
-%% \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
-\subsection{Performance dependence on lens-model parameters}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-%-------------------------------------------------%
-\subsubsection{Effects of Image Magnification on Scoring}
-\label{sec:peformance_lensmodel}
-%-------------------------------------------------%
+paradigms of model performance on the mock images based on the score
+an image receives when evaluated by the trained model, and its true
+label.  From highest scoring to lowest scoring: True Positives (tp),
+False Positives (fp), Borderline Positives (bp), Borderline Negatives
+(bn), False Negatives (fn), and True Negatives (tn).
+
+Figure~\ref{fig:ROCsamplesLSST10} illustrates four images from each
+paradigm for the holdout test set of LSST10.  The trained model used
+the entire 10,000 training set.  The left two columns show lens
+systems, and the right two columns show non-lens systems.  The
+annotation in the top left corner of each images shows the score,
+\todo{and the letters in the bottom right label the paradigm of
+  performance.}
+
+% tp, tn description
+In general, the true positives (the highest scoring lens systems) have
+lensed images with large magnification.  The the true negatives (the
+lowest scoring non-lens systems) have small lens galaxies with
+galaxies along the line of sight that are rounded.  The successful
+classification of these two paradigms are least sensitive to the
+threshold.  On the other hand the failed classification of the false
+negatives (the highest scoring non-lens systems) and the false
+positives (the lowest scoring lens systems) are also least sensitive
+to the threshold.  False negatives are typically lens systems with
+lensed images of smaller magnification and minor distortions that
+mimic along the line of sight galaxies that the model has learned to
+ignore.  False positives are often non-lens systems with elongated,
+elliptical, or ``fuzzy'', galaxies along the line of sight whose signal
+blends with the lens galaxy contributing to the false positive rate
+even for conservative thresholds.  Visually, these false positives are
+virtually indistinguishable from true arcs, and would require
+spectroscopic follow-up.
+
+% Borderlines
+The middle two rows of Figure~\ref{fig:ROCsamplesLSST10} illustrate
+the borderline positives and borderline negatives. The successful
+classification of the borderline positives and negatives are most
+sensitive to the threshold, and would be the first candidates for
+alternative classification methods, such as visual follow-up.
+Thresholds set around these scores yield a true positive rate and
+false positive rate of $tpr\approx0.8$ and $fpr\approx0.2$,
+respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+\subsubsection{Dependence on Lens-Model Parameters}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 examined are the redshift, ellipticity, orientation angle, and
-velocity dispersion of the lensing BCG, and also the magnification of
-the lensed image compared with its original size.  The magnification
-of the lensed image is the most correlated lens-model parameter with
-our trained model performance.  The more strongly lensed an image is,
-the larger its magnification, and the easier it is for our trained
-model to classify.
+velocity dispersion of the lensing galaxy, and also the magnification
+of the lensed image compared with its original size.  We found that
+the magnification of the lensed image is the most correlated
+lens-model parameter with our trained model performance, with a
+secondary and related correlation with lens galaxy velocity
+dispersion.  The more strongly lensed an image is, the larger its
+magnification, and the easier it is for our trained model to classify.
 
@@
 In Figure~\ref{fig:scorevslensparams}, we show the classification
-score as a function of image magnification for our HST-like sample.
-The left-hand side shows the relation color-coded by the redshift of
-the lensing galaxy, and the right-hand side shows the relation
-color-coded by the velocity dispersion of the lensing galaxy.  Lensing
-systems with images that have magnification $\gsim7$ will almost
-certainly be classified as positive with threshold scores above
+score as a function of image magnification for lens images in our
+HST-like sample.  The left-hand side shows the relation color-coded by
+the redshift of the lensing galaxy, and the right-hand side shows the
+relation color-coded by the velocity dispersion of the lensing galaxy.
+Lensing systems with images that have magnification $\gsim7$ will
+almost certainly be classified as positive with threshold scores above
 $\gsim0.5$.  These systems are also those that are most easily
@@
 are often visually indistinguishable from elliptical galaxies along
-the line of sight.  \todo{We will discuss how differences between the
-  lens-model parameter distributions in the training and test sets
-  affect performance in a forthcoming paper.}
-
+the line of sight.
+
+In a forthcoming paper, we will discuss how class imbalance, or
+differences between the lens-model parameter distributions in the
+training and test sets affect model performance and will explore a
+method to correct for this.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
@@
   \centering 
-
   \mbox{
@@
   } 
-\caption{Image classification score as a function of lensed image
-  magnification.  Left color-coded by redshift, right is color coded
-  by the lens velocity_dispersion.}
+\caption{Image classification score on HST mock data as a function of
+  lensed image magnification.  Left color-coded by redshift, right is
+  color coded by the lens velocity dispersion.}
 \label{fig:scorevslensparams}
 \end{figure*}
-
-%-------------------------------------------------%
-\subsubsection{Performance sensitivity to line-of-sight galaxies}
-\label{sec:peformance_lensmodel}
-%-------------------------------------------------%
-
-%-------------------------------------------------%
-\subsection{Effects of BCG contamination}
-%-------------------------------------------------%
-
-Previous works to identify strong lensing systems have often modeled
-out the BCG from images to better identify lensed images (???CITE
-HERE???).  Here, we test the effects of the BCG by training and
-testing models on mock data where the BCG has not been included.  By
-construction, these results show the maximal improvement that can be
-obtained from BCG subtraction.
-
-Figure~\ref{fig:ROCnobcg} shows the \todo{ROC curve for models of HOG
-  feature vectors of mock data with no BCG.  The feature vectors are
-  the same HOG parameters as in Figure~\ref{fig:ROC} }.  \todo{The
-  grid search over parameter space was similar to that for data with
-  the BCG.}
-
-???????
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-machine learning -> pipeline, and training set.
-
-Future work with training set tests.
+% Summarize paper
+We have presented a supervised classification pipeline to
+automatically identify galaxy-galaxy strong lensing systems using a
+histogram of oriented gradients as a feature extractor, and logistic
+regression as a machine learning algorithm.  Our pipeline can easily
+be extended to identify other strong lensing features, such as
+multiply imaged quasars, and to test alternative features and/or
+machine learning algorithms.
+
+% Training set
+We have also made use of a new sophisticated set of mock observations,
+which will also be made publicly available.  The lensing systems have
+lens galaxies generated with a realistic redshift distribution and
+along the line of sight galaxies drawn from ultra-deep Hubble
+observations.  We have explored results from mock HST, one year LSST,
+and ten year LSST observations.
 
@@
   Regression and Support Vector Machine algorithms, with Logistic
-  Regression performing at a factor of $XX$ faster.  This means that
-  features of lens and non-lens images are relatively well separated
-  by hyperplanes in feature space.
+  Regression performing at a factor of $XX$ faster.
 
@@
 
+% Benefits of our method
+We emphasize that classical linear classifiers, such as logistic
+regression, is scalable and relatively easy to parallelize with open
+source tools such as {\em Spark}.  Initial checks indicated that HOG
+features are well separated enough for a linear classifier algorithm.
+Reproducible results do not require supercomputing resources.
+
+% Impact of work
 These results indicate that...
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\section{Sample stacked mock LSST images}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\subsection{BCG included}
+%\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%\section{Sample stacked mock LSST images}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+%\subsection{BCG included}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-09 ms.tex
Finished text for discussion/summary.  Need to follow-up on what data set I had used where the AUC for nLSST10 was .96, and .86 for LSST10.  Was likely the one with constant zlens????

@@
 automatically identify galaxy-galaxy strong lensing systems using a
-histogram of oriented gradients as a feature extractor, and logistic
-regression as a machine learning algorithm.  Our pipeline can easily
-be extended to identify other strong lensing features, such as
-multiply imaged quasars, and to test alternative features and/or
-machine learning algorithms.
+histogram of oriented gradients (HOG) as a feature extractor, and
+logistic regression (LR) as a machine learning algorithm.  Our
+pipeline can easily be extended to identify other strong lensing
+features, such as multiply imaged quasars, and to test alternative
+features and/or machine learning algorithms.
 
@@
 lens galaxies generated with a realistic redshift distribution and
-along the line of sight galaxies drawn from ultra-deep Hubble
+along the line of sight galaxies drawn from Hubble Ultra-Deep field
 observations.  We have explored results from mock HST, one year LSST,
@@
 
-\item We have tested HOG as an efficient and effective feature
-  extractor for galaxy-galaxy strong lensing systems in both a space
-  based (HST-like) and ground based (LSST-like) observation.
-
-\item We have found almost no difference between the Logistic
-  Regression and Support Vector Machine algorithms, with Logistic
-  Regression performing at a factor of $XX$ faster.
+\item We have tested and run parameter tests for a histogram of
+  oriented gradients as an efficient and effective feature extractor
+  for galaxy-galaxy strong lensing systems in both a space based
+  (HST-like) and ground based (LSST-like) observation.  We have also
+  tested and run parameter tests for logistic regression as a
+  scalable, cheap, and effective machine learning algorithm.
 
 \item We find AUC values of ROC curves of optimized classifier models
-  to yield $AUC=0.987$ for the HST-like data, $AUC=0.96$ for the
-  stacked LSST-like data with the lensing BCG included, and $AUC=0.86$
-  for the stacked LSST-like data with the lensing BCG perfectly
-  removed.  This suggests that we will be able to use our method to
-  detect strong galaxy-galaxy lensing systems in future space-based
-  missions (e.g. {\em Euclid}) with high purity and completeness.
-  However, for future ground-based missions like LSST, we will need to
-  perform additional image pre-processing, such as subtracting the
-  image component corresponding to the lens.
+  to yield $AUC=0.975$ for the HST-like data, $AUC=0.809$ for the
+  stacked LSST-like data.  Model performance exhibits continual
+  increase with the training size.
+
+\item While removal of the lens galaxy improves model performance for
+  smaller size training samples, features from the lens galaxy improve
+  model performance for larger training data sets.
 
 \item Images that were easiest for our model to classify typically
-  were lens systems that had high magnification and a BCG with large
-  velocity dispersion.
-
+  were lens systems that had high lensed image magnification and a
+  lens galaxy with large velocity dispersion or non-lens systems with
+  lens galaxies with smaller velocity dispersion and non-elongated
+  along the line of sight galaxies.
 \end{itemize}
@@
 % Impact of work
-These results indicate that...
+These results indicate that effective image classification of
+galaxy-galaxy strong lensing systems do not require large scale
+computing resources.
 
 % Caveat of the mock data set
-One major caveat ... training and test mock images... LOS galaxies all
-from Hubble Ultra Deep field.  Success measured by performance on the
-small sample of systems observed with HST.
+One major caveat of our resuls is the fact that our mock data likely
+does not describe the full range of lens and non-lens images that will
+be observed.  For example, the along the line of sight galaxies in our
+training and test images all come from the Hubble Ultra Deep field,
+sampling a smaller range of potential systems that are not associated
+with a lensed image.  We will address these shortcomings in subsequent
+work.
 
 % Interpreting TP and FP rates
-Note that while our training and test set split of $50\%$ lensed and
-$50\%$ unlensed images is not realistic, our true positive and false
-positive rates in the ROC curves would stay the same for alternative
-lensed and unlensed sample splittings.
-
-On the other hand, the ROC curves show a representative rate for lens
-and source distributions that are evenly sampled.  The sampling is
-{\it not} representative of what we might expect from a an
-observational survey.
+Finally, we must take the class balance, or relative number of lens to
+non-lens systems, into account when assessing a metric.  The
+Purity-Recall (purity-completeness) metric is sensitive to the ratio
+of lens and non-lens systems in the data.  Both of our training and
+test data sets have $50\%$ lensed and $50\%$ unlensed images, which is
+not expected in observations.  The ROC curve metric is insensitive to
+the ratio, but is sensitive to the sampling.  Given alternative lens
+and non-lens sample splittings, our true positive and false positive
+rates in the ROC curves would stay the same, making the ROC curve a
+more standard metric in the literature.  On the other hand, the ROC
+curves show a representative rate for lens and source distributions
+that are evenly sampled.  We do {\it not} expect this sampling to be
+representative of what we might expect from a an observational survey.
 

### 2017-03-09 ms.tex
Added relevance of paper to tail end of intro

@@
 The application of strong gravitational lensing to constrain the mass
-distribution of \todo{early-type galaxies (ETGs)} necessitates large
-samples of galaxy-galaxy lensing systems.  The strong lensing
-signature... EDITING HERE These systems exhibit a background source
-galaxy that the ETG deflects into a partial of full arc shaped
-Einstein ring.
+distribution of strong lenses, such as early-type galaxies (ETGs),
+necessitates large samples of galaxy-galaxy lensing systems.  The
+strong lensing signature directly probes the underlying matter. These
+systems exhibit a background source galaxy that the lens galaxy
+deflects into a partial of full arc shaped Einstein ring.
 
@@
 scalability of training our models [wc???].
+
+%  Relevance of our work
+While there has been a recent surge in the use of neural networks
+applied to image classification problems, these implementations are
+not easily scalable, nor easily accessible to the entire scientific
+community.  We present a supervised classification pipeline built with
+open source tools, tested on mock HST and LSST data.  Results are
+reproducible on personal computers, as both the pipeline and the data
+will be publicly distributed.
 

### 2017-03-12 ms.tex
Removed todo: don't need citation for training time of logistic regression as a function of C_{LogReg}.

@@
 will also increase the training time, since a larger $C_\text{LogReg}$
-corresponds to a less constrained parameter space being searched
-\todo{(citation needed)}.
+corresponds to a less constrained parameter space being searched.
 We discuss the performance and training time dependence on $C_\text{LogReg}$

### 2017-03-13 ms.tex
Polished general intro and shortened previous works, also added recent neural network papers to .bib.  Still need to incorporate these in intro

--- 2017-03-09 ms.tex
@@
 \shorttitle{Automated Lensing Learner}
-\shortauthors{Avestruz, Li, Lightman}
+\shortauthors{Avestruz, et al.}
 \submitted{The Astrophysical Journal} 
@@
 \author{Camille Avestruz\altaffilmark{1-3,$\dagger$}\thanks{E-mail:
-    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, and Matthew Lightman\altaffilmark{5} }
+    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, Matthew Lightman\altaffilmark{5}, Thomas E.~Collett\altaffilmark{6}}
 
@@
 $^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
+$^6${Institute of Cosmology and Gravitation, University of Portsmouth, Burnaby Rd, Portsmouth, PO1 3FX, UK};\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 
-% Gravitational lensing as a geometric (?) test of cosmology.  Also
+% Gravitational lensing as a geometric test of cosmology.  Also
 % probes underlying matter distribution in galaxy clusters, sensitive
@@
 galaxies \citep{lyndsandpetrosian_86,gladders_etal03}, multiply imaged
-quasars \citep{walsh_etal79}, and arclets.  Lensing signatures probe
-the underlying dark matter distribution of the lens
+quasars \citep{walsh_etal79}, multiply imaged galaxies
+\citep{sharon_etal05}, and arclets \citep{bezecourt_etal98}.  Lensing
+signatures probe the underlying dark matter distribution of the lens
 \citep{warrenanddye_03}, high redshift galaxy formation
@@
 \citep{kochanek_96,chae_03,linder_04} and time-delay signals from
-multiply imaged quasars ???\citep{}.
+multiply imaged quasars\citep{xli_etal12,suyu_etal14,suyu_etal16}.
 
@@
 deflects into a partial of full arc shaped Einstein ring.
-
-% Arc identification can be done visually (e.g. that zooniverse
-% thing).  But, in the advent of optical surveys, DES and LSST, we
-% will be limited by our ability to automatically process the large
-% amounts of data.  Wide field surveys - SPT in millimeter, Herschel
-% in submillimeter; high resolution spectroscopic imaging with ALMA;
-% optical surveys DES, HSC, LSST, and Euclid (Oguri \& Marshall 2010).
-Visual arc identification has been effective through the use of
-citizen science platforms (e.g. \citet{marshall_etal16,more_etal16}).
-However, in the advent of large surveys, such as the Dark Energy
-Survey (DES) and the Large Synoptic Sky Telescope (LSST), we will be
-limited by our ability to automatically process large amounts of data
-and select likely strong lensing candidates for follow up visual and
-spectroscopic confirmation.  The strong lensing sector requires an
-exploration of techniques in image processing and classification.
 
@@
 automated image classification emerged. By nature, the human eye is
-one of the best discriminators for image classification.  {\em
-  SpaceWarps} is an example of citizen science based image
-classification of strong lensing systems in Canada France Hawaii
+one of the best discriminators for image classification.  Visual arc
+identification has been effective through the use of citizen science
+platforms.  {\em SpaceWarps} is an example of citizen science based
+image classification of strong lensing systems in Canada France Hawaii
 Telescope Science (CFHTLS) telescope observations
-\citep{marshall_etal16,more_etal16}.  Visual classification has been
-quite successful for a dataset like CFHTLS, classifying \change{XX in
-  XX time}.  However, future datasets like Euclid and LSST will be
-\change{XX} times this size, challenging the scalability of a citizen
-science approach.  The next step is to find automated methods with
-performance comparable to or better than humans. {\em SpaceWarps} is a
-part of the Zooniverse Project (CITE???), which also includes {\em
-  Galaxy Zoo}, the citizen science based image classification of
-galaxy types \citep{lintott_etal08}.  Galaxy classification is a
-successful example of in which machine learning algorithms
-successfully train models to classify images with comparable
-performance to humans \citep{dieleman_etal15}.
-
-% Describe general robot identification schemes that have been
-% implemented
-General automated, or ``robot'', identification refers to a classifier
-where images are fed into an image processing pipeline that enhances
-and extracts characteristic features as parameters on which a pattern
-recognition piece is applied.  Examples of this include ArcFinder for
-group or cluster scale lens \citep{seidelandbartelmann_07}, Ringfinder
-for multiply imaged quasars\citep{gavazzi_etal14}, and ???.  Each
-pipeline .... ... and relies on the image morphology where ... ...
-Note, that the method best applied to ... ... and the objects of
-interest.
+\citep{marshall_etal16,more_etal16}.  These platforms are quite
+successful for a dataset like CFHTLS, classifying \todo{XX in XX
+  time}\citep{}.  However, future datasets like Euclid
+\citep{oguriandmarshall_10} and LSST \cite{} will be \todo{XX} times
+this size, challenging the scalability of a citizen science approach.
+
+% Transition to automated identification
+Recent efforts have focused on the development of automated methods
+with performance comparable to or better than humans. {\em SpaceWarps}
+is a part of the Zooniverse Project \citep{marshall_etal16}, which
+also includes {\em Galaxy Zoo}, the citizen science based image
+classification of galaxy types \citep{lintott_etal08}.  Galaxy
+classification is an early successful example of in which machine
+learning algorithms successfully train models to classify astronomical
+images with comparable performance to humans \citep{dieleman_etal15}.
+
+% Early efforts
+Earlier efforts on automated, or ``robot'', identification of strong
+lensing systems have two distinct steps.  The first enhances and
+extracts characteristic features, and the second uses some form of
+pattern recognition to classify lens and non-lens containing systems.
+{\em ArcFinder} is one such code that finds arcs in groups or cluster
+scale lens \citep{seidelandbartelmann_07}, and {\em RingFinder} an
+analogous tool in searching for multiply imaged quasars
+\citep{gavazzi_etal14}.
+
+% Recent works, deep learning
+Much more recent works have made use of neural networks to
 
@@
 % Previous works and our goal to make a universal pipeline 
-Machine learning to automate.  Previous works (StrongML),
-More+... Here, we focus on the improvement from preprocessing the
-images and describe the pipeline, which is publicly available.
-Depending on the image type, different preprocessing is likely
-necessary (rings, multiply lensed quasars, etc.) Our goal is to create
-an open source pipeline that is general enough for the user to select
-or add appropriate image processing techniques to augment the features
-of the lensed image, train and test data with different machine
-learning techniques, and to select the sequence of methods that
-maximizes completeness with optimal purity.
+Machine learning to automate.  Previous works \citep{lenzen_etal04},
+(StrongML), More+... Here, we focus on the improvement from
+preprocessing the images and describe the pipeline, which is publicly
+available.  Depending on the image type, different preprocessing is
+likely necessary (rings, multiply lensed quasars, etc.) Our goal is to
+create an open source pipeline that is general enough for the user to
+select or add appropriate image processing techniques to augment the
+features of the lensed image, train and test data with different
+machine learning techniques, and to select the sequence of methods
+that maximizes completeness with optimal purity.
 
@@
 While there has been a recent surge in the use of neural networks
-applied to image classification problems, these implementations are
-not easily scalable, nor easily accessible to the entire scientific
-community.  We present a supervised classification pipeline built with
-open source tools, tested on mock HST and LSST data.  Results are
-reproducible on personal computers, as both the pipeline and the data
-will be publicly distributed.
+applied to image classification problems, \wording{these
+  implementations are not readily scalable, nor are the necessary
+  computational resources and expertise easily accessible to the
+  entire scientific community.}  We present a supervised
+classification pipeline built with open source tools, tested on mock
+HST and LSST data.  Results are reproducible on personal computers, as
+both the pipeline and the data will be publicly distributed.  This
+first paper serves as a case study for one feature extraction and
+classical machine learning method, respectively, the {\em histogram of
+  oriented gradients} and {\em logistic regression}.  This framework
+is easily extendable to other feature methods and machine learning
+algorithms for supervised classification.
 
@@
 Telescope (LSST) images generated with PICS (Pipeline for Images of
-Cosmological Strong lensing) (Li et al. 2016) and LensPOP (Thomas
-Colletti 2013) as training set and testing set. In these images, the
-lensed images include the images of lens galaxies, lensed images, and
-galaxies on the line of sight; the unlensed images include the images
-of lens galaxies and the galaxies on the line of sight.
+Cosmological Strong lensing) \citep{li_etal16} and LensPOP
+\citep{collett_15} as training set and testing set. In these images,
+the lensed images include the images of lens galaxies, lensed images,
+and galaxies on the line of sight; the unlensed images include the
+images of lens galaxies and the galaxies on the line of sight.
 
@@
 Images of Cosmological Strong lensing) \citep{li_etal16} and
-LensPop\citep{collett_etal15}.  These images include cluster-member
+LensPop\citep{collett_15}.  These images include cluster-member
 galaxies and foreground stars.  Half of the images used are strong
@@
   positive rates and false positive rates of $tpr\approx0.8$ and
-  $fpr\approx0.2$, respectively.  The bottom two rows show
+  $fpr\approx0.25$, respectively.  The bottom two rows show
   characteristic images that will only be accepted with an extremely
@@
 Thresholds set around these scores yield a true positive rate and
-false positive rate of $tpr\approx0.8$ and $fpr\approx0.2$,
+false positive rate of $tpr\approx0.8$ and $fpr\approx0.25$,
 respectively.

### 2017-03-13 ms.tex
Added more references to previous classification papers

@@
 distribution of strong lenses, such as early-type galaxies (ETGs),
-necessitates large samples of galaxy-galaxy lensing systems.  The
-strong lensing signature directly probes the underlying matter. These
-systems exhibit a background source galaxy that the lens galaxy
-deflects into a partial of full arc shaped Einstein ring.
+necessitates large samples of galaxy-galaxy lensing systems.
+\citet{miraldaescudeandlehar_92} first suggested that massive
+ellipticals would be likely frequent strong lensing sources in optical
+surveys.  These systems exhibit a background source galaxy that the
+lens galaxy deflects into a partial of full arc shaped Einstein ring.
+The strong lensing signature directly probes the underlying matter.
+The identification of such systems in upcoming surveys is the first
+step in constraining the mass-to-light ratio for a large number of
+objects in this mass range.
 
@@
 Earlier efforts on automated, or ``robot'', identification of strong
-lensing systems have two distinct steps.  The first enhances and
-extracts characteristic features, and the second uses some form of
-pattern recognition to classify lens and non-lens containing systems.
-{\em ArcFinder} is one such code that finds arcs in groups or cluster
-scale lens \citep{seidelandbartelmann_07}, and {\em RingFinder} an
-analogous tool in searching for multiply imaged quasars
-\citep{gavazzi_etal14}.
+lensing systems have two distinct generalized steps.  The first
+enhances and extracts characteristic features, and the second uses
+some form of pattern recognition in the features to classify lens and
+non-lens containing systems.  Among others, selected features might
+include shape parameterization
+\citep[see][e.g.]{,alard_06,kuboanddellantonio_08,xu_etal16,lee_17},
+colors in multi-band imaging \citep{maturi_etal14,gavazzi_etal14},
+light profiles \citep{braultandgavazzi_15}, and characteristics of
+potential lens galaxies \citep{marshall_etal09}.  Pattern recognition
+often incorporate cutoffs in selected parameter space distributions
+\citep{lenzen_etal04,joseph_etal14,paraficz_etal16}.  A number of
+these have been publicly distributed, with specific end applications.
+For example, {\em ArcFinder} is one such code that finds arcs in
+groups or cluster scale lens \citep{seidelandbartelmann_07}, and {\em
+  RingFinder} an analogous tool in searching for multiply imaged
+quasars \citep{gavazzi_etal14}.  Codes like these have been
+complementary to human identification \citep{more_etal16}.
+
+% Classical machine learning methods
+More recently, these methods have transitioned to using ``machine
+learning'' algorithms.  In classical machine learning, we can train a
+model to separate a dataset according to some desired classification
+scheme.  However, we still need to reduce the dimensionality of the
+problem by removing information in the images that do not pertain to
+the classifier.
+
+Examples of automated classification will...
+% Previous works and our goal to make a universal pipeline 
+Machine learning to automate.  Here, we focus on the improvement from
+preprocessing the images and describe the pipeline, which is publicly
+available.  Depending on the image type, different preprocessing is
+likely necessary (rings, multiply lensed quasars, etc.)
 
@@
 
-% Describe how machine learning is a step up
-With ``machine learning'' algorithms, we can train a model to separate
-a dataset according to some desired classification scheme.  However,
-we still need to reduce the dimensionality of the problem by removing
-information in the images that do not pertain to the classifier.
-Examples of automated classification will...
-
-% Previous works and our goal to make a universal pipeline 
-Machine learning to automate.  Previous works \citep{lenzen_etal04},
-(StrongML), More+... Here, we focus on the improvement from
-preprocessing the images and describe the pipeline, which is publicly
-available.  Depending on the image type, different preprocessing is
-likely necessary (rings, multiply lensed quasars, etc.) Our goal is to
-create an open source pipeline that is general enough for the user to
-select or add appropriate image processing techniques to augment the
-features of the lensed image, train and test data with different
-machine learning techniques, and to select the sequence of methods
-that maximizes completeness with optimal purity.
-
-% This is the first in MachLensFinder series with initial pipeline
-% results
-This is the first in a series of {\em MachLensFinder} papers.  We
-present our image processing and machine learning classifier pipeline.
-Our image processing procedure parameterizes edges in our image in a
-1-d histogram, enabling fast feature extraction that is similar to
-techniques used to identify humans in security software systems.  We
-train a model with logistic regression to identify features
-corresponding to strong lensing systems.
-
-% Summary of results
-We show results of the pipeline on mock galaxy-galaxy lens systems
-observed by HST and LSST as respective examples of classifier
-performance on optical space- and ground-based observations.
-\citet{miraldaescudeandlehar_92} first suggested that massive
-ellipticals would be likely frequent strong lensing sources in optical
-surveys.  We train and test our pipeline on subsamples from 10,000
-mock observed brightest cluster galaxy (BCG) strong lensing systems
-and 10,000 BCG non-strong lensing systems.
+\citep{petrillo_etal17} convolutional neural networks with the Kilo
+Degree Survey. \citet{bom_etal16} ... \citet{lanusse_etal17} using
+state-of-the-art residual networks to....  directly in the image space
+with minimal image pre-processing.
 
@@
 application of mass reconstruction of the lensing object, completeness
-in strong lensing system identifications will allow us to constrain
-the mass-to-light ratio for a large number of objects.
+in strong lensing system identifications will allow us
 
@@
 classification pipeline built with open source tools, tested on mock
-HST and LSST data.  Results are reproducible on personal computers, as
-both the pipeline and the data will be publicly distributed.  This
-first paper serves as a case study for one feature extraction and
-classical machine learning method, respectively, the {\em histogram of
-  oriented gradients} and {\em logistic regression}.  This framework
-is easily extendable to other feature methods and machine learning
-algorithms for supervised classification.
+HST and LSST data, which will also be made publicly available.  Our
+goal is to centralize an open source pipeline that is general enough
+for the user to select or add appropriate image processing techniques
+to augment the features of the lensed image, train and test data with
+different machine learning techniques, and to select the sequence of
+methods that provides optimal model performance.  Results are
+reproducible on personal computers, as both the pipeline and the data
+will be publicly distributed.
+
+% Summary of paper 
+This first paper serves as a case study for our pipeline with one
+feature extraction and classical machine learning method,
+respectively, the {\em histogram of oriented gradients} (HOG) and {\em
+  logistic regression} (LR).  HOG is a fast feature extraction
+procedure that quantifies edges in images, commonly used to identify
+humans in security software.  LR is a linear classifier, making its
+scalability relatively straightforward with existing open source
+tools.  This framework is easily extendable to other feature methods
+and machine learning algorithms for supervised classification.
+
+% Summary of results
+We show results of the pipeline on mock galaxy-galaxy lens systems
+observed by HST and LSST as respective examples of classifier
+performance on optical space- and ground-based observations.  We train
+and test our pipeline on subsamples from 10,000 mock observed strong
+lensing systems and 10,000 non-strong lensing systems, each centered
+on a potential lens galaxy.
 

### 2017-03-14 ms.tex
Final paragraph summarizing neural network use in strong lensing systems

@@
 \citep{oguriandmarshall_10} and LSST \cite{} will be \todo{XX} times
-this size, challenging the scalability of a citizen science approach.
+this size, and {\em Euclid} is estimated to find tens of thousands
+galaxy-scale strong lenses \citep{pawase_etal12}.  The volume of
+upcoming data challenges the scalability of a citizen science
+approach.
 
@@
 % Classical machine learning methods
-More recently, these methods have transitioned to using ``machine
-learning'' algorithms.  In classical machine learning, we can train a
-model to separate a dataset according to some desired classification
-scheme.  However, we still need to reduce the dimensionality of the
-problem by removing information in the images that do not pertain to
-the classifier.
-
-Examples of automated classification will...
-% Previous works and our goal to make a universal pipeline 
-Machine learning to automate.  Here, we focus on the improvement from
-preprocessing the images and describe the pipeline, which is publicly
-available.  Depending on the image type, different preprocessing is
-likely necessary (rings, multiply lensed quasars, etc.)
-
-% Recent works, deep learning
-Much more recent works have made use of neural networks to
-
-\citep{petrillo_etal17} convolutional neural networks with the Kilo
-Degree Survey. \citet{bom_etal16} ... \citet{lanusse_etal17} using
+The latter of these methods have transitioned to using ``machine
+learning'' algorithms for the pattern recognition step.  In classical
+machine learning, we can train a model to separate a dataset according
+to some desired classification scheme.  However, we still need to
+reduce the dimensionality of the problem with a feature extraction
+method.  The dominant ``features'' of that determine image
+classification are not a priori known, but determined by the
+algorithm.
+
+% Recent works, neural nets, and deep learning
+Much more recent works have made use of a subset tool in machine
+learning, neural networks, to classify images either from input image
+parameters or directly in image space.  In \citet{estrada_etal07},
+authors used input shape parameters to train neural nets to identify
+arc candidates.  \citet{agnello_etal15} used neural networks trained
+on data from multiband magnitudes, and \citet{bom_etal16} used
+extracted morphological parameters.
+
+% Convolutional and residual
+In image space, \citep{petrillo_etal17} used data from the Kilo Degree
+survey to train convolutional neural networks with the Kilo Degree
+Survey. \citet{bom_etal16}. \citet{lanusse_etal17} using
 state-of-the-art residual networks to....  directly in the image space
 with minimal image pre-processing.
-
-% Need to optimize for completeness and purity.  Arc counts and mass
-% reconstruction.
-In general, lensed image finding must optimize for completeness and
-purity.  In the application of arc abundance comparisons with
-cosmological predictions, completeness is important; we must be able
-to understand the reasons and frequency of false negatives.  In the
-application of mass reconstruction of the lensing object, completeness
-in strong lensing system identifications will allow us
-
-% Purity issues
-Since spectroscopic confirmation of background lensed images is
-expensive, purity is key; we must minimize false positives that would
-waste follow up telescope time.  We discuss the performance of our
-image processing and classification pipeline with respect to the
-completeness and purity rates of our trained models and illustrate the
-scalability of training our models [wc???].
 

### 2017-03-14 ms.tex
Marked the to-do for final intro paragraph to resolve
Streamlined the mock observations description in Sect 2.1, also broke it into subsubsections for readability

@@
 survey to train convolutional neural networks with the Kilo Degree
-Survey. \citet{bom_etal16}. \citet{lanusse_etal17} using
-state-of-the-art residual networks to....  directly in the image space
-with minimal image pre-processing.
+Survey. \citet{lanusse_etal17} using state-of-the-art residual
+networks to work directly in the image space with minimal image
+pre-processing.  A major strength of the \citet{lanusse_etal17}
+implementation is that residual networks ..... , which regular
+convolutional networks do not.
+
+EDITING HERE: Double check that petrillo paper
+operates in image space.
 
@@
 While there has been a recent surge in the use of neural networks
-applied to image classification problems, \wording{these
+applied to astronomy image classification problems, \wording{these
   implementations are not readily scalable, nor are the necessary
@@
 %-------------------------------------------------%
-\subsection{Creating Simulated Images for Training Set and Testing Set}
-
-We use mock Hubble Space Telescope (HST) and Large Synoptic Sky
-Telescope (LSST) images generated with PICS (Pipeline for Images of
-Cosmological Strong lensing) \citep{li_etal16} and LensPOP
-\citep{collett_15} as training set and testing set. In these images,
-the lensed images include the images of lens galaxies, lensed images,
-and galaxies on the line of sight; the unlensed images include the
-images of lens galaxies and the galaxies on the line of sight.
-
-To produce simulated lensed galaxies, we first set mass models of the
-lenses to be the Singular Isothermal Ellipsoid (SIE):
-
-\begin{equation}
-\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}}.
+\subsection{Mock Observations}
+%-------------------------------------------------%
+\subsection{Mock Images}
+%-------------------------------------------------%
+% Summary of HST and LSST images
+We use mock {\em Hubble Space Telescope}\footnote{\todo{hst...org}}
+(HST) and {\em Large Synoptic Sky
+  Telescope}\footnote{\todo{lsst....org}} (LSST) images generated with
+PICS (Pipeline for Images of Cosmological Strong lensing)
+\citep{li_etal16} and LensPOP \citep{collett_15} to train and test our
+model.  Along the line of sight galaxies and foreground stars.  Half
+of the images used are strong lensing systems.  Lensed galaxy images
+are ray-traced images of actual galaxies extracted from deep Hubble
+Space Telescope observations.  The final mock images are ``observed''
+with a realistic point spread function corresponding to modeled
+detector artifacts for bright stars.  We refer to \cite{li_etal16} for
+further details, but outline the process here.
+
+We generate 10,000 lens containing mock observations and 10,000
+non-lens containing mock observations to run our parameter search, and
+keep a hold-out test set of 1,000 lens containing mock observations
+and 1,000 non-lens containing mock observations on which we evaluate
+the final trained model.
+
+Lens containing mock observations include the lens galaxy, lensed
+images of the source galaxy, and galaxies along the line of sight.
+Non-lens containing mock observations include all but a lensed source
+image.  We convolve each of the $2\times 10,000$ train/test images and
+$2\times 1,000$ hold-out images to produce three separate sets of mock
+``observations'' with equal numbers of lens and non-lens containing
+systems: (1) HST-like observations, (2) LSST-like observations over
+the span of one year, and (3) LSST-like observations over the span of
+ten years.  We respectively label these observations as HST, LSST1,
+and LSST10.
+%-------------------------------------------------%
+\subsubsection{Modeling Images of the Source Galaxies}
+%-------------------------------------------------%
+To produce images of the simulated lensed source galaxies, we first
+set mass models of the lens galaxy to be the Singular Isothermal
+Ellipsoid (SIE):
+%-------------------------------------------------%
+\begin{equation}\label{eqn:sie}
+\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}},
 \end{equation}
-
-Where, $\theta_{\rm E}$ is the Einstein Radius, $q$ is axis
-ratio. Einstein radius can be calculated according to the redshift of
+%-------------------------------------------------%
+where $\theta_{\rm E}$ is the Einstein radius and $q$ is the axis
+\wording{ratio between semi-major and semi-minor axes $x_1$ and
+  $x_2$}. We can calculate the Einstein radius from the redshift of
 the lens, the redshift of the source, and the velocity dispersion of
 the lens galaxy.
-\begin{equation}
-\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
+%-------------------------------------------------%
+\begin{equation}\label{eqn:einsteinradius}
+\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}. 
 \end{equation}
-where, $c$ is the speed of light, $\sigma_v$ is the velocity
-dispersion of the lens galaxy, $D_{ls}$ and $D_{s}$ are the angular
-diameter distance from the source plane to the lens plane and from the
-source plane to the observer separately.
+%-------------------------------------------------%
+Here, $c$ is the speed of light, $\sigma_v$ is the velocity dispersion
+of the lens galaxy, and $D_{ls}$ and $D_{s}$ are the respective
+angular diameter distance from the source plane to the lens plane and
+from the source plane to the observer.
 
 To rotate the lenses with a random orientation angles, we adopt the
-transformation below:
-
+transformation below for orientation angle, $\phi$:
+%-------------------------------------------------%
 \begin{eqnarray}
-\label{eq:rotation}
+\label{eqn:rotation}
 \begin{bmatrix}
@@
 \end{eqnarray}
-
-$\phi$ is the orientation angle.  According to above equations, we
-need $\sigma_v$, $q$, $\phi$, redshift of the lens $z_l$, and redshift
-of the source $z_s$ to derivative the lensing maps completely.
-Velocity dispersion, ellipticity, and orientation are randomly chosen
-from typical ranges of a galaxy, where $\sigma_v = [200, 320] km/s$,
-$q = [0.5, 1.0]$, and $\phi = [0, 360]$. The redshift of the lens is
-fixed at $z_l = 0.2$, and the redshift of the source is fixed at $z_s
-= 1.0$. The images of source galaxies are extracted from the CANDELS
-survey. We selected 33 bright galaxies, and relocated them to
-projected positions, which are close to the caustic of the lensing
-system, and the projected position of the lens is fixed in the center
-of the field of view of each image. Once we have the lens, source, and
-the parameters of the image simulation, i.e., $300 \times 300 {\rm
-  pixels}^2$ and 0.03 arcsec per pixel per side, settled, the lensed
-images can be produced by performing ray-tracing simulations.
-
-The light distributions of the lens galaxies  are modeled as the elliptical Sersic profile,
-
-\begin{equation}
+%-------------------------------------------------%
+From Equations~\ref{eqn:sie}~-~\ref{eqn:rotation}, there are five
+independent parameters that uniquely define the lensing system:
+$\sigma_v$, ellipticity $q$, orientation angle $\phi$, redshift of the
+lens $z_l$, and redshift of the source $z_s$.
+
+% Parameters of lensing system
+We choose $\sigma_v$, $q$, and $\phi$ randomly from typical ranges of
+a galaxy, where $\sigma_v = [200, 320] km/s$, $q = [0.5, 1.0]$, and
+$\phi = [0, 360]$.  The redshift of the lens galaxy is drawn from the
+distribution \todo{found in \citet{???}}.  We fix the redshift of the
+source to $z_s = 1.0$. We then extract images of 33 bright galaxies
+from the CANDELS survey as source galaxies.  We place the source
+galaxy images in projected positions close to the caustic of the
+lensing system and fix the projected position of the lens galaxy to
+the center of the field of view of each image.  Once we have
+determined all parameters of the lensing system, we perform
+ray-tracing simulations to produce the final lensed image.
+
+%-------------------------------------------------%
+\subsubsection{Modeling Lens Galaxies}
+%-------------------------------------------------%
+We model the light distributions of the lens galaxies with an
+elliptical Sersic profile,
+%-------------------------------------------------%
+\begin{equation}\label{eqn:sersic}
 I(R) = I_{\rm eff}~{\rm exp} \left\lbrace -b_{n} \left[ \left(
-  \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ] \right\rbrace
+  \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ] \right\rbrace,
 \end{equation}
-
-Where, $R = \sqrt[]{x_1^2 /q+x_2^2 q }$, $R_{\rm eff}$ is the
-effective radius in units of arcsecond, $I_{\rm eff}$ is the intensity
-at the effective radius, $n$ is the index of the Sersic profile, $q$
-is the ellipticity, and We perform the similar transformation as
-Eq. \ref{eq:rotation} to orient the sources.  We assume that the
-distribution of light is following that of mass, so ellipticity and
-orientation are the same as the SIE model. Matching the velocity
-dispersion with the COSMOS morphological
-catalog \footnote{\url{https://arxiv.org/pdf/1501.04977v2.pdf}}, we
-assign effective radius, effective luminosity, and index to the light
-profile.  We also assume the light center is on top of the mass
-center, the noiseless images of lenses can be drawn. The galaxies on
-the line of sight are constructed by cutting light-cones from the
-Hubble Ultra Deep Field.  Stacking all these images together and
-collaborating the magnitude of each component, we create primarily
-simulated lensed images.
-
-The final part is mock observing. To produce HST-like images, we do
-not need to do anything further than stacking and magnitude
-calibrating, because noise and PSF are involved when we are extracting
-galaxies on the line of sight. To produce LSST-like images, we perform
-re-binning, convolving with PSF, and adding noise serially; this
-process is implemented in LensPop. We created single-epoch-LSST-like
-images and stacked -LSST-like images for investigating the performance
-and usability of our pipeline in LSST data. Figure 2.1 illustrates a
-sample mock lensed and unlensed images from each telescope. From left
-to right, the top panel images respectively correspond to a mock HST
-lensing and non-lensing system. The mock HST images are 300 × 300 in
-size, and the pixel size is 0.03 arcsecond. For the HST-like data-set,
-many giant arcs are visually obvious. The middle panel images
-respectively correspond to a mock single-epoch LSST lensing and
-non-lensing systems. The bottom panel images respectively correspond
-to a mock stacked LSST lensing and non-lensing systems. These images
-are 45 × 45; the pixel size is 0.2 arcsecond. The ground based noise,
-PSF, and limited resolution of the LSST-like data-set make visual
-giant arc identification difficult. But when in the stacked LSST
-images, the quality is better, because more data improves the signal
-to noise ratio better.
-
-In the training sets, we also generate unlensed images, the procedure
-is similar to mock lensed images but getting rid of the part of
-ray-tracing. 10000 lensed images and 10000 unlensed images are merged
-to construct one training set. Furthermore, for investigating the
-influence of BCG galaxies on the performance of our lens
-identification pipeline in LSST data, we build another training sets
-of the images without BCG galaxies.
-
-%-------------------------------------------------%
-\subsection{Mock Images}
-%-------------------------------------------------%
-
-% Summary of HST and LSST images
-We use mock {\em Hubble Space Telescope} (HST) and {\em Large Synoptic
-  Sky Telescope} (LSST) images generated with PICS (Pipeline for
-Images of Cosmological Strong lensing) \citep{li_etal16} and
-LensPop\citep{collett_15}.  These images include cluster-member
-galaxies and foreground stars.  Half of the images used are strong
-lensing systems.  Here, lensed galaxy images are ray-traced images of
-actual galaxies extracted from deep Hubble Space Telescope
-observations.  The final mock images are ``observed'' with a realistic
-point spread function corresponding to modeled detector artifacts for
-bright stars.  See \cite{li_etal16} for more details.
-
-Figure ~\ref{fig:mockimages} illustrates a sample mock lensed and
-unlensed images from each telescope.  The top left and right panel
-images respectively correspond to a mock HST lensing and non-lensing
-system. The mock HST images are $n_\text{pix}\times
-n_\text{pix}=300\times300$ in size.  For the HST-like dataset, many
-giant arcs are visually obvious.
-
-The middle row corresponds to the same simulated systems, as observed
-with a single epoch of LSST.  These images are $n_\text{pix}\times
-n_\text{pix}=45\times45$.  The ground based noise and limited
-resolution of the LSST-like dataset make visual giant arc
-identification difficult.  However, by stacking observations over the
-course of the LSST survey, we recover the arc feature, albeit at a
-much lower resolution than with the HST-like image. The bottom row
-shows the mock stacked observation, where the lensed background galaxy
-is now visible.
+%-------------------------------------------------%
+where, $R = \sqrt[]{x_1^2 /q+x_2^2 q }$, $R_{\rm eff}$ is the
+effective radius in units of arcseconds, $I_{\rm eff}$ is the
+intensity at the effective radius, $n$ is the index of the Sersic
+profile, and $q$ is the ellipticity of the lens galaxy.  We perform a
+similar transformation as Equation~\ref{eqn:rotation} to orient the
+sources.  We assume that the distribution of light is following that
+of mass, so ellipticity and orientation are the same as the SIE model.
+
+We use the COSMOS morphological
+catalog \footnote{\url{https://arxiv.org/pdf/1501.04977v2.pdf}} to
+match the velocity dispersion with an assigned effective radius,
+effective luminosity, and index to the light profile.  We also assume
+the light center is on top of the mass center, creating noiseless
+images of lens galaxies.
+
+We construct galaxies along the line of sight by cutting light-cones
+from the \todo{Hubble Ultra Deep Field\footnote{udf...org}}.  We stack
+these images with the lens galaxy image and the lensed source galaxy,
+calibrating the magnitude of all three components.
+
+%-------------------------------------------------%
+\subsubsection{Producing Mock Images}
+%-------------------------------------------------%
+
+The final step is to perform a mock observations.  For HST-like
+observations, galaxies along the line of sight already include noise
+and a point spread function (PSF).  We therefore stack and magnitude
+calibrate all components to produce the final HST-like images, which
+are $300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.
+
+To produce LSST-like images, we use {\em LensPop} to serially perform
+re-binning, convolve with the corresponding PSF, and add
+noise\citep{collett_15}.  We created one year LSST-like (LSST1) images
+and stacked ten-year LSST-like images (LSST10) to investigate the
+performance and usability of our pipeline in future LSST
+data. LSST-like images are $45\times45~{\rm pix}^2$ with $0.2$~arcsec
+per pixel.
+
+Figure~\ref{fig:mockimages} illustrates sample mock observations with
+a strong lensing signature from each telescope.  The left-most column
+respectively correspond to a mock HST lensing system with a highly
+magnified source galaxy (top) and a less visible image of the source
+galaxy (bottom). For the HST-like dataset, many arcs are visually
+obvious due to the exquisite spatial resolution.
+
+The middle column corresponds to the same simulated systems, as
+observed with over ten years of LSST, LSST10.  The right-most column
+corresponds to the simulated systems observed over just one year of
+LSST1.  LSST10 images visually exhibit an improved signal to noise
+ratio, recovering the arc feature, albeit at a much lower resolution
+than with the HST-like image.  The top images of LSST10 and LSST1 show
+a visible lensed source galaxy image.  The bottom images are washed
+out in the bottom row, where the magnification of the source galaxy is
+not as large.  The ground based noise, PSF, and limited resolution of
+the LSST1 make visual giant arc identification difficult, except in
+systems with the most magnified source galaxies.
 
@@
 
+Our mock observations also include non-lens containing images.  The
+procedure is similar to mock lensed images but we do not perform
+ray-tracing, so these images do not have lensed source galaxies.
+
+Furthermore, we investigate the influence of light from the lens
+galaxies on the performance of our lens identification pipeline.  We
+generate another set of each HST, LSST1, and LSST10 images without the
+lens galaxy.  We label these nHST, nLSST1, and nLSST10.
+
+The final data is then comprised of $6\times10,000$ lens containing
+images, and $6\times 10,000$ non-lens containing images.  We also keep
+a hold-out set of $6\times 1,000$ lens containing images, and $6\times
+1,000$ non-lens containing images.
 %-------------------------------------------------%

### 2017-03-15 ms.tex
added ms

@@
 
-EDITING HERE: Double check that petrillo paper
-operates in image space.
+\todo{EDITING HERE: Double check that petrillo paper operates in image
+  space, edit previous paragraph.}
 
@@
 To augment our training set, we rotated each image in the set by
-multiples of $90^o$.  Augmenting our data by a factor of four
-naturally optimizes the use of available training data, since our
-feature extraction method of HOG is not rotationally invariant.  This
-has an equivalent improvement to the study illustrated in
+multiples of $90^o$.  Since our feature extraction method of HOG is
+not rotationally invariant, augmenting our data by a factor of four
+naturally optimizes the use of available training data.  This has an
+equivalent improvement to the study illustrated in
 Figure~\ref{fig:trainsizeLSST10}.
@@
 regression, is scalable and relatively easy to parallelize with open
-source tools such as {\em Spark}.  Initial checks indicated that HOG
-features are well separated enough for a linear classifier algorithm.
-Reproducible results do not require supercomputing resources.
+source tools such as \todo{\em Spark}\footnote{...spark...org}}.
+  Initial checks indicated that HOG features are well separated enough
+  for a linear classifier algorithm.  Reproducible results do not
+  require supercomputing resources.
 

### 2017-03-20 ms.tex
Committed tweak to final unfinished intro paragraph

@@
 % Convolutional and residual
-In image space, \citep{petrillo_etal17} used data from the Kilo Degree
-survey to train convolutional neural networks with the Kilo Degree
-Survey. \citet{lanusse_etal17} using state-of-the-art residual
-networks to work directly in the image space with minimal image
+The most advanced use of neural networks for strong lensing
+classification operate directly in image space.
+\citep{petrillo_etal17} used mock Kilo Degree Survey data to train
+convolutional neural networks, with a training set size of six million
+images. \citet{lanusse_etal17} used state-of-the-art residual learning
+to also work directly in the image space with minimal image
 pre-processing.  A major strength of the \citet{lanusse_etal17}
-implementation is that residual networks ..... , which regular
-convolutional networks do not.
-
-\todo{EDITING HERE: Double check that petrillo paper operates in image
-  space, edit previous paragraph.}
+implementation is that residual learning has been found to be easier
+to train in deep neural networks, and can outperform implementations
+of convolutional neural networks.
 

### 2017-03-21 ms.tex
add nan's text for the simulation section

@@
 \label{sec:methods}
-%-------------------------------------------------%
-\subsection{Mock Observations}
-%-------------------------------------------------%
-\subsection{Mock Images}
-%-------------------------------------------------%
-% Summary of HST and LSST images
-We use mock {\em Hubble Space Telescope}\footnote{\todo{hst...org}}
-(HST) and {\em Large Synoptic Sky
-  Telescope}\footnote{\todo{lsst....org}} (LSST) images generated with
-PICS (Pipeline for Images of Cosmological Strong lensing)
-\citep{li_etal16} and LensPOP \citep{collett_15} to train and test our
-model.  Along the line of sight galaxies and foreground stars.  Half
-of the images used are strong lensing systems.  Lensed galaxy images
-are ray-traced images of actual galaxies extracted from deep Hubble
-Space Telescope observations.  The final mock images are ``observed''
-with a realistic point spread function corresponding to modeled
-detector artifacts for bright stars.  We refer to \cite{li_etal16} for
-further details, but outline the process here.
-
-We generate 10,000 lens containing mock observations and 10,000
-non-lens containing mock observations to run our parameter search, and
-keep a hold-out test set of 1,000 lens containing mock observations
+We use mock {\em Hubble Space Telescope}\footnote{\todo{hst.org}} (HST) and {\em Large
+Synoptic Sky Telescope}\footnote{\todo{lsst.org}}
+(LSST) images generated with PICS (Pipeline for Images of Cosmological Strong
+lensing) \citep{li_etal16} and LensPop\citep{collett_etal15} for training and testing.
+
+There are 10,000 lens containing mock observations and 10,000
+non-lens containing mock observations for running our parameter search. 
+We keep a hold-out test set of 1,000 lens containing mock observations
 and 1,000 non-lens containing mock observations on which we evaluate
@@
 
-Lens containing mock observations include the lens galaxy, lensed
+Mock lensing systems contain mock observations include the lens galaxy, lensed
 images of the source galaxy, and galaxies along the line of sight.
-Non-lens containing mock observations include all but a lensed source
+Mock Non-lensing systems contain mock observations include all but a lensed source
 image.  We convolve each of the $2\times 10,000$ train/test images and
@@
 %-------------------------------------------------%
-\subsubsection{Modeling Images of the Source Galaxies}
-%-------------------------------------------------%
-To produce images of the simulated lensed source galaxies, we first
-set mass models of the lens galaxy to be the Singular Isothermal
-Ellipsoid (SIE):
-%-------------------------------------------------%
-\begin{equation}\label{eqn:sie}
-\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}},
+\subsubsection{Modeling the Mass Distribution of Lens Galaxies}
+To produce simulated lensed galaxies, we first set mass models of the lenses to
+be the Singular Isothermal Ellipsoid (SIE). This model is not only analytically
+tractable, it has also been found to be consistent with models of individual
+lenses and lens statistics on the length scales relevant for strong lensing
+(e.g. Koopmans et al. 2006\footnote{Koopmans L. V. E., Treu T., Bolton A. S.,
+Burles S., Moustakas L. A., 2006, The Astrophysical Journal, 649, 599}; Gavazzi
+et al. 2007\footnote{Gavazzi R., Treu T., Rhodes J. D., Koopmans L. V. E.,
+Bolton A. S., Burles S., Massey R. J., Moustakas L. A., 2007, The Astrophysical
+Journal, 667, 176}; Dye et al. 2008\footnote{Dye S., Evans N. W., Belokurov V.,
+Warren S. J., Hewett P., 2008, Monthly Notices of the Royal Astronomical
+Society, 388, 384}; Li et al.
+2009\footnote{http://iopscience.iop.org/article/10.1088/1674-4527/9/11/001/meta}).
+The normalized convergence map of SIE model is defined as :
+
+\begin{equation}
+\kappa = \frac{\theta_{\rm E}}{2}\frac{1}{\sqrt{x_1^2/q+x_2^2 q}}.
 \end{equation}
-%-------------------------------------------------%
-where $\theta_{\rm E}$ is the Einstein radius and $q$ is the axis
-\wording{ratio between semi-major and semi-minor axes $x_1$ and
-  $x_2$}. We can calculate the Einstein radius from the redshift of
+
+Where, $\theta_{\rm E}$ is the Einstein Radius, $q$ is axis
+ratio. Einstein radius can be calculated according to the redshift of
 the lens, the redshift of the source, and the velocity dispersion of
 the lens galaxy.
-%-------------------------------------------------%
-\begin{equation}\label{eqn:einsteinradius}
-\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}. 
+\begin{equation}
+\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
 \end{equation}
-%-------------------------------------------------%
-Here, $c$ is the speed of light, $\sigma_v$ is the velocity dispersion
-of the lens galaxy, and $D_{ls}$ and $D_{s}$ are the respective
-angular diameter distance from the source plane to the lens plane and
-from the source plane to the observer.
+where, $c$ is the speed of light, $\sigma_v$ is the velocity
+dispersion of the lens galaxy, $D_{ls}$ and $D_{s}$ are the angular
+diameter distance from the source plane to the lens plane and from the
+source plane to the observer separately.
 
 To rotate the lenses with a random orientation angles, we adopt the
-transformation below for orientation angle, $\phi$:
-%-------------------------------------------------%
+transformation below:
 \begin{eqnarray}
-\label{eqn:rotation}
+\label{eq:rotation}
 \begin{bmatrix}
-
     x_{1}\prime      \\
@@
     x_2      
-\end{bmatrix} .
+\end{bmatrix}.
 \end{eqnarray}
-%-------------------------------------------------%
-From Equations~\ref{eqn:sie}~-~\ref{eqn:rotation}, there are five
-independent parameters that uniquely define the lensing system:
-$\sigma_v$, ellipticity $q$, orientation angle $\phi$, redshift of the
-lens $z_l$, and redshift of the source $z_s$.
-
-% Parameters of lensing system
-We choose $\sigma_v$, $q$, and $\phi$ randomly from typical ranges of
-a galaxy, where $\sigma_v = [200, 320] km/s$, $q = [0.5, 1.0]$, and
-$\phi = [0, 360]$.  The redshift of the lens galaxy is drawn from the
-distribution \todo{found in \citet{???}}.  We fix the redshift of the
-source to $z_s = 1.0$. We then extract images of 33 bright galaxies
-from the CANDELS survey as source galaxies.  We place the source
-galaxy images in projected positions close to the caustic of the
-lensing system and fix the projected position of the lens galaxy to
-the center of the field of view of each image.  Once we have
-determined all parameters of the lensing system, we perform
-ray-tracing simulations to produce the final lensed image.
-
-%-------------------------------------------------%
-\subsubsection{Modeling Lens Galaxies}
+$\phi$ is the orientation angle.  According to above equations, we need
+$\sigma_v$, $q$, $\phi$, redshift of the lens $z_l$, and redshift of the source
+$z_s$ to derivative the lensing maps completely. Velocity dispersion,
+ellipticity, and orientation are randomly chosen from typical ranges of a
+galaxy, where $\sigma_v = [150, 350] km/s$, $q = [0.5, 1.0]$, and $\phi = [0,
+360]$ degrees. The lens redshifts are obtained by matching the velocity
+dispersion in our simulations to the catalog of elliptical galaxies in the
+COSMOS survey from Zahid et al. (2015)\footnote{Zahid H. J., Damjanov I.,
+Geller M. J., Chilingarian I., 2015, The Astrophysical Journal, 806, 122}. The
+resulting redshift range of our lenses is zl ∈ [0.2, 0.7].
+
+%-------------------------------------------------%
+\subsubsection{Modeling Images of the Lens Galaxies}
 %-------------------------------------------------%
@@
 
-%-------------------------------------------------%
-\subsubsection{Producing Mock Images}
-%-------------------------------------------------%
-
-The final step is to perform a mock observations.  For HST-like
+The light distributions of the lens galaxies  are modeled as the elliptical
+Sersic profile, \begin{equation} I(R) = I_{\rm eff}~{\rm exp} \left\lbrace
+-b_{n} \left[ \left( \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ]
+\right\rbrace \end{equation} where $R = \sqrt[]{x_1^2 /q+x_2^2 q }$, $R_{\rm
+eff}$ is the effective radius in units of arcsecond, $I_{\rm eff}$ is the
+intensity at the effective radius, $n$ is the index of the Sersic profile, $q$
+is the ellipticity, and We perform the similar transformation as Eq.
+\ref{eq:rotation} to orient the sources.  We assume that the distribution of
+light is following that of mass, so ellipticity and orientation are the same as
+the SIE model. Matching the velocity dispersion with the COSMOS morphological
+catalog \footnote{\url{https://arxiv.org/pdf/1501.04977v2.pdf}}, we assign
+effective radius, effective luminosity, and index to the light profile.  We
+also assume the light center is on top of the mass center, the noiseless images
+of lenses can be drawn. The galaxies on the line of sight are constructed by
+cutting light-cones from the Hubble Ultra Deep Field.  Stacking all these
+images together and collaborating the magnitude of each component, we create
+primarily simulated lensed images.
+
+\subsubsection{Modeling Images of the Source Galaxies}
+
+The background sources are a set of detailed images of low-redshift bright
+galaxies (z ∼ 0.45) extracted from the mosaics produced by the CANDELS team
+(Grogin et al. 2011\footnote{Grogin N. A., et al., 2011, The Astrophysical
+Journal Supplement Series December The Astrophysical Journal Supplement Series,
+197, 3535}; Koekemoer et al. 2011\footnote{Koekemoer A. M., et al., 2011, The
+Astrophysical Journal Supplement Series December The Astrophysical Journal
+Supplement Series, 197}) and selected from the CANDELS UDS catalog Galametz et
+al. (2013)\footnote{Galametz A., et al., 2013, The Astrophysical Journal
+Supplement Series, 206, 10}. These galaxies are rescaled and placed at a fixed
+redshift $z_s = 2.0$, near the caustics of the lensing system, and the
+projected position of the lens is fixed in the center of the field of view of
+each image. Therefore, once we have the lens, source, and the parameters of the
+image simulation, i.e., $300 \times 300 {\rm pixels}^2$ and 0.03 arcsec per
+pixel per side, settled, the lensed images can be produced by performing
+ray-tracing simulations.
+
+%-------------------------------------------------%
+\subsubsection{Mock Observing}
+%-------------------------------------------------%
+
+The final part is mock observing. For HST-like
 observations, galaxies along the line of sight already include noise
@@
 
-To produce LSST-like images, we use {\em LensPop} to serially perform
-re-binning, convolve with the corresponding PSF, and add
-noise\citep{collett_15}.  We created one year LSST-like (LSST1) images
-and stacked ten-year LSST-like images (LSST10) to investigate the
-performance and usability of our pipeline in future LSST
-data. LSST-like images are $45\times45~{\rm pix}^2$ with $0.2$~arcsec
-per pixel.
+To produce LSST-like images from the ideal images produced in the previous steps,
+we use the LensPop software Collett (2015)\footnote{Collett T. E., 2015, The
+Astrophysical Journal, 811, 20} to perform mock observing. Images are resampled
+to match the detector pixel scale and convolved with a circularly symmetric
+Gaussian Point Spread Function discretised at the same pixel scale. A noisy
+realisation of this image is generated assuming a Poisson model based on the
+sky plus signal, and an additional Gaussian read-out noise. Parameters for
+these simulations follow Collett (2015)\footnote{Collett T. E., 2015, The
+Astrophysical Journal, 811, 20} and are based on the LSST observation simulator
+(Connolly et al. 2010)\footnote{Connolly A. J., et al., 2010, SPIE Astronomical
+Telescopes + Instrumentation, pp 77381O–77381O–10}. To account for seeing and
+sky-brightness variations over the course of the survey, each simulated
+exposure is drawn from a stochastic distribution of these parameters. We then
+consider two different strategies to use these exposures. For each field, we
+build one single-epoch image by keeping only the best seeing exposure and
+another ``worst-case''' stack image by co-adding all individual exposures after
+degrading them all in resolution to match the one with the worst seeing. These
+two sets of images will allow us to investigate the trade-off between
+signal-to-noise and resolution for our automated lens search. Figure 2.1
+illustrates a sample mock lensed and unlensed images from each telescope. From
+left to right, the top panel images respectively correspond to a mock HST
+lensing and non-lensing system. The mock HST images are 300 × 300 in size, and
+the pixel size is 0.03 arcsecond. For the HST-like data-set, many giant arcs
+are visually obvious. The middle panel images respectively correspond to a mock
+single-epoch LSST lensing and non-lensing systems. The bottom panel images
+respectively correspond to a mock stacked LSST lensing and non-lensing systems.
+These images are 45 × 45; the pixel size is 0.18 arcsecond. The ground based
+noise, PSF, and limited resolution of the LSST-like data-set make visual giant
+arc identification difficult. But when in the stacked LSST images, the quality
+is better, because more data improves the signal to noise ratio better.
 
@@
 systems with the most magnified source galaxies.
+
+In the training sets, we also generate unlensed images, the procedure is
+similar to mock lensed images but getting rid of the part of ray-tracing. 10000
+lensed images and 10000 unlensed images are merged to construct one training
+set. Furthermore, for investigating the influence of BCG galaxies on the
+performance of our lens identification pipeline in LSST data, we build another
+training sets of the images without BCG galaxies.
 

### 2017-03-21 ms.tex
Went through methodology additions and highlighted in purple re-wording that Matt needs to look at

--- 2017-03-21 ms.tex
@@
 \citep{marshall_etal16,more_etal16}.  These platforms are quite
-successful for a dataset like CFHTLS, classifying \todo{XX in XX
-  time}\citep{}.  However, future datasets like Euclid
-\citep{oguriandmarshall_10} and LSST \cite{} will be \todo{XX} times
-this size, and {\em Euclid} is estimated to find tens of thousands
-galaxy-scale strong lenses \citep{pawase_etal12}.  The volume of
-upcoming data challenges the scalability of a citizen science
-approach.
+successful for a dataset like CFHTLS; here, 3,000 candidate images
+were identified in eight months, resulting in 89 final candidates.
+However, future datasets like Euclid \citep{oguriandmarshall_10} and
+LSST expect to find tens of thousands galaxy-scale strong lenses
+\citep{pawase_etal12}.  The volume of upcoming data challenges the
+scalability of a pure citizen science approach.
 
@@
 % Convolutional and residual
-The most advanced use of neural networks for strong lensing
+\wording{The most advanced use of neural networks for strong lensing
   classification operate directly in image space.
   \citep{petrillo_etal17} used mock Kilo Degree Survey data to train
-convolutional neural networks, with a training set size of six million
-images. \citet{lanusse_etal17} used state-of-the-art residual learning
-to also work directly in the image space with minimal image
-pre-processing.  A major strength of the \citet{lanusse_etal17}
-implementation is that residual learning has been found to be easier
-to train in deep neural networks, and can outperform implementations
-of convolutional neural networks.
+  convolutional neural networks, with a training set size of six
+  million images. \citet{lanusse_etal17} used state-of-the-art
+  residual learning to also work directly in the image space with
+  minimal image pre-processing.  A major strength of the
+  \citet{lanusse_etal17} implementation is that residual learning has
+  been found to be easier to train in deep neural networks, and can
+  outperform implementations of convolutional neural networks.}
 
 %  Relevance of our work
-While there has been a recent surge in the use of neural networks
-applied to astronomy image classification problems, \wording{these
+\wording{While there has been a recent surge in the use of neural
+  networks applied to astronomy image classification problems, these
   implementations are not readily scalable, nor are the necessary
   computational resources and expertise easily accessible to the
-  entire scientific community.}  We present a supervised
-classification pipeline built with open source tools, tested on mock
-HST and LSST data, which will also be made publicly available.  Our
-goal is to centralize an open source pipeline that is general enough
-for the user to select or add appropriate image processing techniques
-to augment the features of the lensed image, train and test data with
+  entire scientific community.  We present a supervised classification
+  pipeline built with open source tools, tested on mock HST and LSST
+  data, which will also be made publicly available.  Our goal is to
+  centralize an open source pipeline that is general enough for the
+  user to select or add appropriate image processing techniques to
+  augment the features of the lensed image, train and test data with
   different machine learning techniques, and to select the sequence of
   methods that provides optimal model performance.  Results are
-reproducible on personal computers, as both the pipeline and the data
-will be publicly distributed.
+  reproducible on personal computers, as both the pipeline and the
+  data will be publicly distributed.}
 
 % Summary of paper 
-This first paper serves as a case study for our pipeline with one
-feature extraction and classical machine learning method,
-respectively, the {\em histogram of oriented gradients} (HOG) and {\em
-  logistic regression} (LR).  HOG is a fast feature extraction
-procedure that quantifies edges in images, commonly used to identify
-humans in security software.  LR is a linear classifier, making its
-scalability relatively straightforward with existing open source
-tools.  This framework is easily extendable to other feature methods
-and machine learning algorithms for supervised classification.
+This first paper serves as both a presentation of the mock data set
+and as a thorough case study for our pipeline with one feature
+extraction and classical machine learning method, respectively, the
+{\em histogram of oriented gradients} (HOG) and {\em logistic
+  regression} (LR).  HOG is a fast feature extraction procedure that
+quantifies edges in images, commonly used to identify humans in
+security software.  LR is a linear classifier, making its scalability
+relatively straightforward with existing open source tools.  This
+framework is easily extendable to other feature methods and machine
+learning algorithms for supervised classification.
 
@@
 %-------------------------------------------------%
-\subsection{Mock Observations}
-%-------------------------------------------------%
 \subsection{Mock Images}
 %-------------------------------------------------%
-% Summary of HST and LSST images
-We use mock {\em Hubble Space Telescope}\footnote{\todo{hst...org}}
-(HST) and {\em Large Synoptic Sky
-  Telescope}\footnote{\todo{lsst....org}} (LSST) images generated with
-PICS (Pipeline for Images of Cosmological Strong lensing)
-\citep{li_etal16} and LensPOP \citep{collett_15} to train and test our
-model.  Along the line of sight galaxies and foreground stars.  Half
-of the images used are strong lensing systems.  Lensed galaxy images
-are ray-traced images of actual galaxies extracted from deep Hubble
-Space Telescope observations.  The final mock images are ``observed''
-with a realistic point spread function corresponding to modeled
-detector artifacts for bright stars.  We refer to \cite{li_etal16} for
-further details, but outline the process here.
-
-We generate 10,000 lens containing mock observations and 10,000
-non-lens containing mock observations to run our parameter search, and
-keep a hold-out test set of 1,000 lens containing mock observations
+We use mock {\em Hubble Space
+  Telescope}\footnote{https://www.spacetelescope.org/} (HST) and {\em
+  Large Synoptic Sky Telescope}\footnote{https://www.lsst.org} (LSST)
+images generated with {\em PICS} (Pipeline for Images of Cosmological
+Strong lensing) \citep{li_etal16} and {\em LensPop} \citep{collett_15}
+for training and testing.
+
+There are 10,000 lens containing mock observations and 10,000
+non-lens containing mock observations for running our parameter search. 
+We keep a hold-out test set of 1,000 lens containing mock observations
 and 1,000 non-lens containing mock observations on which we evaluate
@@
 
-Lens containing mock observations include the lens galaxy, lensed
+Mock observations of lensing systems include the lens galaxy, lensed
 images of the source galaxy, and galaxies along the line of sight.
-Non-lens containing mock observations include all but a lensed source
-image.  We convolve each of the $2\times 10,000$ train/test images and
-$2\times 1,000$ hold-out images to produce three separate sets of mock
-``observations'' with equal numbers of lens and non-lens containing
-systems: (1) HST-like observations, (2) LSST-like observations over
-the span of one year, and (3) LSST-like observations over the span of
-ten years.  We respectively label these observations as HST, LSST1,
-and LSST10.
-%-------------------------------------------------%
-\subsubsection{Modeling Images of the Source Galaxies}
-%-------------------------------------------------%
-To produce images of the simulated lensed source galaxies, we first
-set mass models of the lens galaxy to be the Singular Isothermal
-Ellipsoid (SIE):
+Mock observations of non-lensing systems include all but the images of
+a lensed source galaxy.  We convolve each of the $2\times 10,000$
+train/test images and $2\times 1,000$ hold-out images to produce three
+separate sets of mock ``observations''.  These each have equal numbers
+of lens and non-lens containing systems: (1) HST-like observations,
+(2) LSST-like observations over the span of one year, and (3)
+LSST-like observations over the span of ten years.  We respectively
+label these observations as HST, LSST1, and LSST10.
+
+%-------------------------------------------------%
+\subsubsection{Modeling the Mass Distribution of Lens Galaxies}
+%-------------------------------------------------%
+
+To produce simulated lensed galaxies, we first model the mass of lens
+galaxies as the Singular Isothermal Ellipsoid (SIE). This model is
+both analytically tractable and is consistent with models of
+individual lenses and lens statistics on the length scales relevant
+for strong lensing
+\citep[e.g.]{koopmans_etal06,gavazzi_etal07,dye_etal08,liandchen_09}.
+
+The normalized convergence map of SIE model is defined as:
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-where $\theta_{\rm E}$ is the Einstein radius and $q$ is the axis
-\wording{ratio between semi-major and semi-minor axes $x_1$ and
-  $x_2$}. We can calculate the Einstein radius from the redshift of
-the lens, the redshift of the source, and the velocity dispersion of
-the lens galaxy.
-%-------------------------------------------------%
-\begin{equation}\label{eqn:einsteinradius}
-\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}. 
+where $\theta_{\rm E}$ is the Einstein Radius and $q$ is axis ratio.
+The Einstein radius can be calculated from the redshift of the
+lens, the redshift of the source, and the velocity dispersion of the
+lens galaxy as follows,
+%-------------------------------------------------%
+\begin{equation}
+\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
 \end{equation}
@@
 Here, $c$ is the speed of light, $\sigma_v$ is the velocity dispersion
-of the lens galaxy, and $D_{ls}$ and $D_{s}$ are the respective
-angular diameter distance from the source plane to the lens plane and
-from the source plane to the observer.
-
-To rotate the lenses with a random orientation angles, we adopt the
-transformation below for orientation angle, $\phi$:
-%-------------------------------------------------%
+of the lens galaxy, $D_{ls}$ and $D_{s}$ are respectively the angular
+diameter distances from the source plane to the lens plane and from
+the source plane to the observer.
+
+To rotate the lenses with random orientation angle $\phi$, we adopt
+the transformation below:
 \begin{eqnarray}
@@
 \begin{bmatrix}
-
     x_{1}\prime      \\
@@
     x_2      
-\end{bmatrix} .
+\end{bmatrix}.
 \end{eqnarray}
-%-------------------------------------------------%
+
 From Equations~\ref{eqn:sie}~-~\ref{eqn:rotation}, there are five
-independent parameters that uniquely define the lensing system:
-$\sigma_v$, ellipticity $q$, orientation angle $\phi$, redshift of the
-lens $z_l$, and redshift of the source $z_s$.
-
-% Parameters of lensing system
+independent parameters from which we can derive the lensing map:
+velocity dispersion $\sigma_v$, axis ratio or ellipticity $q$,
+orientation angle $\phi$, redshift of the lens $z_l$, and redshift of
+the source $z_s$.
+
 We choose $\sigma_v$, $q$, and $\phi$ randomly from typical ranges of
-a galaxy, where $\sigma_v = [200, 320] km/s$, $q = [0.5, 1.0]$, and
-$\phi = [0, 360]$.  The redshift of the lens galaxy is drawn from the
-distribution \todo{found in \citet{???}}.  We fix the redshift of the
-source to $z_s = 1.0$. We then extract images of 33 bright galaxies
-from the CANDELS survey as source galaxies.  We place the source
-galaxy images in projected positions close to the caustic of the
-lensing system and fix the projected position of the lens galaxy to
-the center of the field of view of each image.  Once we have
-determined all parameters of the lensing system, we perform
-ray-tracing simulations to produce the final lensed image.
-
-%-------------------------------------------------%
-\subsubsection{Modeling Lens Galaxies}
+observed galaxies: $\sigma_v \in [200, 320]~km/s$, $q \in [0.5, 1.0]$,
+and $\phi \in [0, 360]$.  We obtain the redshift of the lens galaxy by
+matching the velocity dispersion from our simulations to the catalog
+of elliptical galaxies in the COSMOS survey from \citet{zahid_etal15},
+resulting in lens galaxy redshifts in the range, $z_l \in [0.2,0.7]$.
+
+%-------------------------------------------------%
+\subsubsection{Modeling Images of the Lens Galaxies}
 %-------------------------------------------------%
@@
 I(R) = I_{\rm eff}~{\rm exp} \left\lbrace -b_{n} \left[ \left(
-  \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ] \right\rbrace,
+  \frac{R}{R_{\rm eff}}\right)^{1/n} - 1 \right ]
+\right\rbrace 
 \end{equation}
@@
 similar transformation as Equation~\ref{eqn:rotation} to orient the
-sources.  We assume that the distribution of light is following that
-of mass, so ellipticity and orientation are the same as the SIE model.
-
-We use the COSMOS morphological
-catalog \footnote{\url{https://arxiv.org/pdf/1501.04977v2.pdf}} to
-match the velocity dispersion with an assigned effective radius,
-effective luminosity, and index to the light profile.  We also assume
-the light center is on top of the mass center, creating noiseless
-images of lens galaxies.
+source galaxies and assume that the distribution of light follows that
+of mass.  The ellipticity and orientation are therefore the same as in
+the SIE model.
+
+We use the COSMOS morphological catalog \citep{zahid_etal15} to match
+the velocity dispersion with an assigned effective radius, effective
+luminosity, and index to the light profile.  We also assume the light
+center is on top of the mass center, creating noiseless images of lens
+galaxies.
 
 We construct galaxies along the line of sight by cutting light-cones
-from the \todo{Hubble Ultra Deep Field\footnote{udf...org}}.  We stack
-these images with the lens galaxy image and the lensed source galaxy,
-calibrating the magnitude of all three components.
-
-%-------------------------------------------------%
-\subsubsection{Producing Mock Images}
-%-------------------------------------------------%
-
-The final step is to perform a mock observations.  For HST-like
-observations, galaxies along the line of sight already include noise
-and a point spread function (PSF).  We therefore stack and magnitude
-calibrate all components to produce the final HST-like images, which
-are $300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.
-
-To produce LSST-like images, we use {\em LensPop} to serially perform
-re-binning, convolve with the corresponding PSF, and add
-noise\citep{collett_15}.  We created one year LSST-like (LSST1) images
-and stacked ten-year LSST-like images (LSST10) to investigate the
-performance and usability of our pipeline in future LSST
-data. LSST-like images are $45\times45~{\rm pix}^2$ with $0.2$~arcsec
-per pixel.
+from the Hubble Ultra Deep
+Field\footnote{http://www.spacetelescope.org/science/deep\_fields/}.
+We stack these images with the lens galaxy image and the lensed source
+galaxy, calibrating the magnitude of all three components.
+
+%-------------------------------------------------%
+\subsubsection{Modeling Images of the Source Galaxies}
+%-------------------------------------------------%
+The background source galaxies come from a set of detailed images of
+low-redshift bright galaxies ($z\sim0.45$) that have been extracted
+from mosaics produced by the CANDELS team
+\citep{grogin_etal11,koekemoer_etal11} and selected from the CANDELS
+UDS catalog \citep{galametz_etal13}.  We rescale these background
+source galaxies, set the source redshift to $z_s=0.2$, and select
+source positions near caustics of the lensing system.  We then fix the
+projected position of the lens galaxy at the center of the field of
+view for each image.
+
+We perform ray-tracing simulations using the modeled galaxy images and
+parameters.  The lens galaxy, source galaxy, and parameters of the
+image simulations (i.e., $300 \times 300~{\rm pixels}^2$ with
+0.03~arcsec/pixel for an HST-like image) are inputs to the simulation
+that produce ideal lensed images with the appropriate resolution.
+
+%-------------------------------------------------%
+\subsubsection{Mock Observing}
+%-------------------------------------------------%
+
+The final part is to perform the mock observation from the ideal
+images produced in the previous step. For HST-like observations,
+galaxies along the line of sight already include noise and a point
+spread function (PSF).  We therefore stack and magnitude calibrate all
+components to produce the final HST-like images, which are
+$300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.
+
+For LSST-like observations, we use the {\em LensPop} software
+\citep{collett_15}.  We resample images to match the detector pixel
+scale and convolve the resampled image with a circularly symmetric
+Gaussian Point Spread Function discretised at the same pixel scale. To
+generate a noisy realization of the image, we assume a Poisson model
+based on the sky plus signal, and an additional Gaussian read-out
+noise. Parameters for these simulations follow \citet{collett_15} and
+are based on the LSST observation simulator \citep{connolly_etal10}.
+
+To account for variations in seeing and sky-brightness over the course
+of the survey, we draw each simulated exposure from a stochastic
+distribution of these parameters. We then consider two different
+strategies to use the simulated exposures. First, we build one
+single-epoch image for each field (hereafter labeled as LSST1) by
+keeping only the best seeing exposure.  Second, we build another
+``worst-case'' stacked image by degrading all individual exposures to
+match the one with the worst seeing and co-add all exposures to a
+single image (hereafter labeled as LSST10).  These two sets of images
+will allow us to investigate the trade-off between resolution and
+signal-to-noise for our automated lens search.
 
@@
 a strong lensing signature from each telescope.  The left-most column
-respectively correspond to a mock HST lensing system with a highly
-magnified source galaxy (top) and a less visible image of the source
-galaxy (bottom). For the HST-like dataset, many arcs are visually
-obvious due to the exquisite spatial resolution.
-
-The middle column corresponds to the same simulated systems, as
-observed with over ten years of LSST, LSST10.  The right-most column
-corresponds to the simulated systems observed over just one year of
-LSST1.  LSST10 images visually exhibit an improved signal to noise
-ratio, recovering the arc feature, albeit at a much lower resolution
-than with the HST-like image.  The top images of LSST10 and LSST1 show
-a visible lensed source galaxy image.  The bottom images are washed
-out in the bottom row, where the magnification of the source galaxy is
-not as large.  The ground based noise, PSF, and limited resolution of
-the LSST1 make visual giant arc identification difficult, except in
-systems with the most magnified source galaxies.
+corresponds to a mock HST lensing system with a highly magnified
+source galaxy (top) and a less visible image of the source galaxy
+(bottom). For the HST-like dataset, many arcs are visually obvious due
+to the exquisite spatial resolution and quality of space based
+imaging.
+
+The middle column corresponds to the same simulated systems for
+LSST10.  The right-most column corresponds to the simulated systems of
+LSST1.  These images have resolution $45\times45~{\rm pixels}^2$ with
+$0.18$~arcsec/pixel.  LSST10 images visually exhibit the improved
+signal to noise ratio, recovering the arc feature, albeit at a much
+lower resolution than with the HST-like image or the LSST1 image.  The
+top images of LSST10 and LSST1 show a visible lensed source galaxy
+image.  The bottom images are washed out in the bottom row, where the
+magnification of the source galaxy is not as large.  The ground based
+noise, PSF, and limited resolution of the LSST1 make visual giant arc
+identification difficult, except in systems with the most magnified
+source galaxies.
 
@@
 generate another set of each HST, LSST1, and LSST10 images without the
-lens galaxy.  We label these nHST, nLSST1, and nLSST10.
-
-The final data is then comprised of $6\times10,000$ lens containing
-images, and $6\times 10,000$ non-lens containing images.  We also keep
-a hold-out set of $6\times 1,000$ lens containing images, and $6\times
-1,000$ non-lens containing images.
+lens galaxy.  We respectively label these nHST, nLSST1, and nLSST10.
+
+The final data set is then comprised of $6\times10,000$ lens
+containing images, and $6\times 10,000$ non-lens containing images.
+We also keep a hold-out set of $6\times 1,000$ lens containing images,
+and $6\times 1,000$ non-lens containing images.
+
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-\subsection{Feature Extractor: Histogram Oriented Gradients}\label{sec:hog}
+\subsubsection{Feature Extractor: Histogram Oriented Gradients}\label{sec:hog}
 %-------------------------------------------------%
@@
 % Division of the image  
-HOG first divides the image into blocks of \wording{50\% overlap}.
-Each block contains $m\times m$ cells-per-block that each contain
-$n_{pix}\times n_{pix}$ pixels-per-cell.  The computed gradient
-orientation is quantized into $N_{orient}$ bins.
+HOG first divides the image into blocks of 50\% overlap.  Each block
+contains $m\times m$ cells-per-block that each contain $n_{pix}\times
+n_{pix}$ pixels-per-cell.  The computed gradient orientation is
+quantized into $N_{orient}$ bins.
 
@@
 %-------------------------------------------------%
-\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
+\subsubsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
 %-------------------------------------------------%
@@
 % Benefits of our method
-We emphasize that classical linear classifiers, such as logistic
-regression, is scalable and relatively easy to parallelize with open
-source tools such as \todo{\em Spark}\footnote{...spark...org}}.
-  Initial checks indicated that HOG features are well separated enough
-  for a linear classifier algorithm.  Reproducible results do not
-  require supercomputing resources.
+\wording{We emphasize that classical linear classifiers, such as
+  logistic regression, is scalable and relatively easy to parallelize
+  with open source tools such as {\em
+    Spark}\footnote{http://spark.apache.org/}.  Initial checks
+  indicated that HOG features are well separated enough for a linear
+  classifier algorithm.  Finally, our methods enable reproducible
+  results that do not require supercomputing resources.
 
@@
 galaxy-galaxy strong lensing systems do not require large scale
-computing resources.
+computing resources or expertise.}
 
@@
 training and test images all come from the Hubble Ultra Deep field,
-sampling a smaller range of potential systems that are not associated
-with a lensed image.  We will address these shortcomings in subsequent
-work.
+sampling a smaller range of potential contaminants that are not
+associated with a lensed image.  Also, the redshift of the source
+galaxies have been fixed to $z_s=.2$.  We will address these
+shortcomings in subsequent work.
 

### 2017-03-22 ms.tex
Added score vs. magnification for all three datasets

@@
 In Figure~\ref{fig:scorevslensparams}, we show the classification
-score as a function of image magnification for lens images in our
-HST-like sample.  The left-hand side shows the relation color-coded by
-the redshift of the lensing galaxy, and the right-hand side shows the
-relation color-coded by the velocity dispersion of the lensing galaxy.
-Lensing systems with images that have magnification $\gsim7$ will
-almost certainly be classified as positive with threshold scores above
-$\gsim0.5$.  These systems are also those that are most easily
-classified by eye.  However, our trained model has varying performance
-for systems with lower magnifications.
+score as a function of image magnification of the source galaxy in
+each of our samples.  In the top panel, each data point is color-coded
+by the velocity dispersion of the lensing galaxy.  In the bottom
+panel, the color-coding is by the redshift of the lens galaxy.  In
+either an HST-like or LSST-like observation, lensing systems with
+images that have magnification $\gsim7$ will almost certainly be
+classified as positive with threshold scores above $\gsim0.5$.  These
+systems are also those that are most easily classified by eye.
+However, our trained model has varying performance for systems with
+lower magnifications.
 
@@
 % into magnitude
-Almost \todo{X\%} of lensing systems with magnifications $\lsim7$ will
-be falsely identified as non-lenses for classification threshold
-scores $\gsim0.5$.  These systems typically have lenses that are at
-higher redshifts of $z\gsim0.5$ (lighter colors in left figure) and/or
-velocity dispersions lower than $\sigma_v\lsim230.$~km/s (darker
+In our mock HST sample, all but one of our lensing systems with
+magnifications $\lsim7$ will be successfully identified for
+classification threshold scores $\gsim0.5$.  These highly magnified
+systems typically have lenses that are at higher redshifts of
+$z\gsim0.5$ (lighter colors in bottom row) and/or lens galaxies with
+velocity dispersions higher than $\sigma_v\lsim230.$~km/s (darker
 colors in right figure).  Note that lensing galaxies with smaller
@@
   \mbox{
-    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
-        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_z.pdf}}\hfill
-    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
-        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_velocity_dispersion.pdf}}
-  } 
-\caption{Image classification score on HST mock data as a function of
-  lensed image magnification.  Left color-coded by redshift, right is
-  color coded by the lens velocity dispersion.}
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/HST_Magnification_Velocity_Dispersion.pdf}}\hfill
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/LSST10_Magnification_Velocity_Dispersion.pdf}}\hfill
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/LSST1_Magnification_Velocity_Dispersion.pdf}\hfill}
+  }\\ 
+  \mbox{
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/HST_Magnification_z.pdf}}\hfill
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/LSST10_Magnification_z.pdf}}\hfill
+    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
+        clip]{figures/lens_parameter_dependence/LSST1_Magnification_z.pdf}\hfill}
+  }\\ 
+\caption{Left to right: Image classification score on HST, LSST10,
+  LSST1 mock observed lensing images as a function of lensed image
+  magnification.  Top row: Each panel is color coded by the lens
+  velocity dispersion in km/s.  High velocity dispersion lens galaxies
+  are likely to produce high magnification images of the source
+  galaxies.  Magnification is the strongest indicator of how likely a
+  lensing system will be successfully classified.  Bottom row: Here,
+  we color code by the redshift of the lens galaxy.}
 \label{fig:scorevslensparams}

### 2017-03-22 ms.tex
Improved some of the wording about ease of scalability and use on a personal laptop for logistic regression + HOG.

--- 2017-03-21 ms.tex
@@
 lensing galaxy.  However, with larger training data sets, information
-from the lensing galaxy improves model performance.  \wording{Our
-  results show efficient and effective methods for automated strong
-  lensing identification with scalable linear methods that are easy to
-  parallelize with existing open source tools and are reproducible on
-  personal laptop computers.}
+from the lensing galaxy improves model performance.  Our
+results demonstrate efficient and effective methods for automated strong
+lensing identification. The simple classifier used here easily
+scales to large data sets on a computing cluster and is easily
+reproduced on a personal laptop, using existing open source tools
+in both cases.
 \end{abstract}
@@
 %  Relevance of our work
-\wording{While there has been a recent surge in the use of neural
-  networks applied to astronomy image classification problems, these
-  implementations are not readily scalable, nor are the necessary
-  computational resources and expertise easily accessible to the
+While there has been a recent surge in the use of deep neural
+networks applied to image classification problems in astronomy,
+it is not always easy to scale these techniques to large data
+sets, nor are the necessary computational resources and hardware,
+such as GPUs, easily accessible to the
 entire scientific community.  We present a supervised classification
@@
 reproducible on personal computers, as both the pipeline and the
-  data will be publicly distributed.}
+data will be publicly distributed.
 
@@
 % Benefits of our method
-\wording{We emphasize that classical linear classifiers, such as
-  logistic regression, is scalable and relatively easy to parallelize
+We emphasize that simple linear classifiers, such as
+logistic regression, are scalable and relatively easy to parallelize
 with open source tools such as {\em
 Spark}\footnote{http://spark.apache.org/}.  Initial checks
-  indicated that HOG features are well separated enough for a linear
-  classifier algorithm.  Finally, our methods enable reproducible
-  results that do not require supercomputing resources.
-
-% Impact of work
+indicate that HOG feature extraction plus a linear
+classifier captures much of the complexity in the arc finding problem.
 These results indicate that effective image classification of
-galaxy-galaxy strong lensing systems do not require large scale
-computing resources or expertise.}
+galaxy-galaxy strong lensing systems can be achieved without
+large scale computing resources, or specialized hardware like GPUs,
+but can be scaled to large datasets on a computing cluster if needed.
 

### 2017-03-22 ms.tex
Added Wentao's affiliation

@@
 \author{Camille Avestruz\altaffilmark{1-3,$\dagger$}\thanks{E-mail:
-    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, Matthew Lightman\altaffilmark{5}, Thomas E.~Collett\altaffilmark{6}}
+    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, Matthew Lightman\altaffilmark{5}, Thomas E.~Collett\altaffilmark{6}, Wentao Luo\altaffilmark{7}}
 
@@
 $^6${Institute of Cosmology and Gravitation, University of Portsmouth, Burnaby Rd, Portsmouth, PO1 3FX, UK};\\
+$^7${Center for Astronomy and Astrophysics, Shanghai Jiaotong University,
+800 Dongchuan Road, Shanghai 200240, China};\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 % Convolutional and residual
-\wording{The most advanced use of neural networks for strong lensing
+The most advanced use of neural networks for strong lensing
 classification operate directly in image space.
 \citep{petrillo_etal17} used mock Kilo Degree Survey data to train
-  convolutional neural networks, with a training set size of six
-  million images. \citet{lanusse_etal17} used state-of-the-art
-  residual learning to also work directly in the image space with
-  minimal image pre-processing.  A major strength of the
-  \citet{lanusse_etal17} implementation is that residual learning has
-  been found to be easier to train in deep neural networks, and can
-  outperform implementations of convolutional neural networks.}
+convolutional neural networks, with a training set size of six million
+images. \citet{lanusse_etal17} used state-of-the-art residual learning
+to also work directly in the image space with minimal image
+pre-processing.  A major strength of the \citet{lanusse_etal17}
+implementation is that residual learning has been found to be easier
+to train in deep neural networks, and can outperform implementations
+of convolutional neural networks.
 
@@
   lensing system will be successfully classified.  Bottom row: Here,
-  we color code by the redshift of the lens galaxy.}
+  we color code by the redshift of the lens galaxy.}\vspace{10pt}
 \label{fig:scorevslensparams}
@@
 through grant NSF PHY-1125897 and an endowment from the Kavli
-Foundation and its founder Fred Kavli.
+Foundation and its founder Fred Kavli.  NL would like to thank the
+funding support from NSFC, grant no.11503064, and Shanghai Natural
+Science Foundation, grant no. 15ZR1446700.
 \lastpagefootnotes

### 2017-03-23 ms.tex
Went through matt's new text

@@
 Euclid has prompted a need for automatic and efficient identification
-of strong lensing systems.  We present {\em (ALL) Automated Lensing
-  Learner}, a strong lensing identification pipeline that will be
-publicly released as open source software.  In this first application,
-we employ a fast feature extraction method, Histogram of Oriented
-Gradients (HOG), to capture edge patterns that are characteristic of
-strong gravitational arcs in galaxy-galaxy lensing.  We use logistic
-regression to train a supervised classifier model on the HOG of HST-
-and LSST-like images.  We use an area under the curve (AUC) of a
-Receiver Operating Characteristic curve to assess model performance;
-$AUC=1.0$ is an ideal trained classifier, and $AUC=0.5$ does not
-provide any classification information.  Our best performing models on
-a training set of 10,000 lens containing images and 10,000 non-lens
-containing images exhibit an AUC of 0.975 for an HST-like sample.
-However, for one orbit of LSST, our model only reaches an AUC of
-0.625.  For 10-year mock LSST observations, the AUC improves to 0.809.
-Model performance appears to continually improve with the size of the
+of strong lensing systems.  We present (1) {\em (ALL) Automated
+  Lensing Learner}, a strong lensing identification pipeline that will
+be publicly released as open source software, and (2) a publicly
+available mock LSST dataset with strong galaxy-galaxy lenses.  In this
+first application of the pipeline, we employ a fast feature extraction
+method, Histogram of Oriented Gradients (HOG), to capture edge
+patterns that are characteristic of strong gravitational arcs in
+galaxy-galaxy lensing.  We use logistic regression to train a
+supervised classifier model on the HOG of HST- and LSST-like images.
+We use an area under the curve (AUC) of a Receiver Operating
+Characteristic curve to assess model performance; $AUC=1.0$ is an
+ideal trained classifier, and $AUC=0.5$ does not provide any
+classification information.  Our best performing models on a training
+set of 10,000 lens containing images and 10,000 non-lens containing
+images exhibit an AUC of 0.975 for an HST-like sample.  However, for
+one orbit of LSST, our model only reaches an AUC of 0.625.  For
+10-year mock LSST observations, the AUC improves to 0.809.  Model
+performance appears to continually improve with the size of the
 training set.  Models trained on fewer images perform better in
-absence of the lens galaxy, which can decrease the false positive rate
-by blending with light from a lensed galaxy image near the central
-lensing galaxy.  However, with larger training data sets, information
-from the lensing galaxy improves model performance.  Our
-results demonstrate efficient and effective methods for automated strong
-lensing identification. The simple classifier used here easily
-scales to large data sets on a computing cluster and is easily
-reproduced on a personal laptop, using existing open source tools
-in both cases.
+absence of the lens galaxy, the removal of which can decrease the
+false positive rate due to the blending of light between source images
+and the lens galaxy.  However, with larger training data sets,
+information from the lens galaxy improves model performance.  Our
+results demonstrate efficient and effective methods for automated
+strong lensing identification. With existing open source tools, this
+example linear classifier both runs on a personal laptop and can
+easily scale to large data sets on a computing cluster.
 \end{abstract}
@@
 % Benefits of our method
-We emphasize that simple linear classifiers, such as
-logistic regression, are scalable and relatively easy to parallelize
-with open source tools such as {\em
-Spark}\footnote{http://spark.apache.org/}.  Initial checks
-indicate that HOG feature extraction plus a linear
+We emphasize that simple linear classifiers, such as logistic
+regression, are scalable and relatively easy to parallelize with open
+source tools such as {\em Spark}\footnote{http://spark.apache.org/}.
+Our work indicates that HOG feature extraction plus a linear
 classifier captures much of the complexity in the arc finding problem.
-These results indicate that effective image classification of
-galaxy-galaxy strong lensing systems can be achieved without
-large scale computing resources, or specialized hardware like GPUs,
-but can be scaled to large datasets on a computing cluster if needed.
+{\it These results indicate that effective image classification of
+  galaxy-galaxy strong lensing systems can be achieved without large
+  scale computing resources, or specialized hardware like GPUs.}
+These methods also scale for large datasets on a computing cluster, if
+needed.
 
@@
 representative of what we might expect from a an observational survey.
+We leave these additional challenges to future work.
 
@@
 Institute at the University of Chicago, and the University of Chicago
-Provost's Office. This work was also supported in part by the Kavli
-Institute for Cosmological Physics at the University of Chicago
+Provost's Office. NL would like to thank the funding support from
+NSFC, grant no.11503064, and Shanghai Natural Science Foundation,
+grant no. 15ZR1446700. This work was also supported in part by the
+Kavli Institute for Cosmological Physics at the University of Chicago
 through grant NSF PHY-1125897 and an endowment from the Kavli
-Foundation and its founder Fred Kavli.  NL would like to thank the
-funding support from NSFC, grant no.11503064, and Shanghai Natural
-Science Foundation, grant no. 15ZR1446700.
+Foundation and its founder Fred Kavli.emacs -nw 
 \lastpagefootnotes

### 2017-03-23 ms.tex

@@
 supervised classifier model on the HOG of HST- and LSST-like images.
-We use an area under the curve (AUC) of a Receiver Operating
-Characteristic curve to assess model performance; $AUC=1.0$ is an
-ideal trained classifier, and $AUC=0.5$ does not provide any
-classification information.  Our best performing models on a training
+We use the area under the curve (AUC) of a Receiver Operating
+Characteristic (ROC) curve to assess model performance; $AUC=1.0$ is an
+ideal classifier, and $AUC=0.5$ is no better than randomly guessing.
+Our best performing models on a training
 set of 10,000 lens containing images and 10,000 non-lens containing
@@
 and the lens galaxy.  However, with larger training data sets,
-information from the lens galaxy improves model performance.  Our
-results demonstrate efficient and effective methods for automated
-strong lensing identification. With existing open source tools, this
-example linear classifier both runs on a personal laptop and can
-easily scale to large data sets on a computing cluster.
+information from the lens galaxy actually improves model performance.
+Our results demonstrate an efficient and effective method for automatically
+identifying strong lenses that captures much of the complexity of the
+arc finding problem. The linear classifier both runs on a
+personal laptop and can easily scale to large data sets on a computing
+cluster, all while using existing open source tools.
 \end{abstract}
@@
 signatures probe the underlying dark matter distribution of the lens
-\citep{warrenanddye_03}, high redshift galaxy formation
-\citep{allam_etal07}, and provide a geometric test of cosmology via
-comparison of predicted arc abundances and observed abundances
-\citep{kochanek_96,chae_03,linder_04} and time-delay signals from
-multiply imaged quasars\citep{xli_etal12,suyu_etal14,suyu_etal16}.
+\citep{warrenanddye_03}, and high redshift galaxy formation
+\citep{allam_etal07}. They also provide a geometric test of cosmology via
+comparison of predicted arc abundances with observed abundances
+\citep{kochanek_96,chae_03,linder_04}, and via time-delay between signals
+from multiply imaged quasars \citep{xli_etal12,suyu_etal14,suyu_etal16}.
 
@@
 \citet{miraldaescudeandlehar_92} first suggested that massive
-ellipticals would be likely frequent strong lensing sources in optical
-surveys.  These systems exhibit a background source galaxy that the
-lens galaxy deflects into a partial of full arc shaped Einstein ring.
+ellipticals would likely be frequent strong lensing sources in optical
+surveys.  These systems contain a background source galaxy that the
+lens galaxy deflects into a partial or full arc shaped Einstein ring.
 The strong lensing signature directly probes the underlying matter.
@@
 classification of galaxy types \citep{lintott_etal08}.  Galaxy
-classification is an early successful example of in which machine
-learning algorithms successfully train models to classify astronomical
+classification is an early example in which machine
+learning algorithms successfully trained models to classify astronomical
 images with comparable performance to humans \citep{dieleman_etal15}.
@@
 potential lens galaxies \citep{marshall_etal09}.  Pattern recognition
-often incorporate cutoffs in selected parameter space distributions
+often incorporates cutoffs in selected parameter space distributions
 \citep{lenzen_etal04,joseph_etal14,paraficz_etal16}.  A number of
@@
 groups or cluster scale lens \citep{seidelandbartelmann_07}, and {\em
-  RingFinder} an analogous tool in searching for multiply imaged
+  RingFinder} is an analogous tool in searching for multiply imaged
 quasars \citep{gavazzi_etal14}.  Codes like these have been
@@
 % Classical machine learning methods
-The latter of these methods have transitioned to using ``machine
-learning'' algorithms for the pattern recognition step.  In classical
-machine learning, we can train a model to separate a dataset according
-to some desired classification scheme.  However, we still need to
-reduce the dimensionality of the problem with a feature extraction
-method.  The dominant ``features'' of that determine image
-classification are not a priori known, but determined by the
-algorithm.
+Pattern recognition methods have transitioned to using ``machine
+learning'' algorithms in place of manual cutoffs.  With
+machine learning, we can train a model to separate a dataset into
+a known set of classes, such as ``lensing systems'' and
+``non-lensing systems''. However, many classic machine learning
+algorithms do not work well in image space, i.e. directly using the
+raw pixel values of the image, but first require a process of
+\em{feature engineering}, in which domain expertise is used to
+extract variables which are more directly related to the classification
+task at hand.  An example would be the application of an edge detector.
+The optimal weights and cutoffs for these derived variables that are
+used to determine the class label of an image are found automatically
+by the algorithm.
 
 % Recent works, neural nets, and deep learning
-Much more recent works have made use of a subset tool in machine
-learning, neural networks, to classify images either from input image
+Some more recent works have made use of a subset of machine
+learning algorithms called neural networks to classify images,
+either from derived image
 parameters or directly in image space.  In \citet{estrada_etal07},
-authors used input shape parameters to train neural nets to identify
+authors used derived shape parameters to train neural nets to identify
 arc candidates.  \citet{agnello_etal15} used neural networks trained
@@
 convolutional neural networks, with a training set size of six million
-images. \citet{lanusse_etal17} used state-of-the-art residual learning
+images. \citet{lanusse_etal17} used state-of-the-art deep residual
+neural networks
 to also work directly in the image space with minimal image
 pre-processing.  A major strength of the \citet{lanusse_etal17}
-implementation is that residual learning has been found to be easier
-to train in deep neural networks, and can outperform implementations
-of convolutional neural networks.
+implementation is that in comparison to deep convolutional neural
+networks, deep residual neural networks have been found to
+be easier to train and perform better.
 
@@
 data, which will also be made publicly available.  Our goal is to
-centralize an open source pipeline that is general enough for the
-user to select or add appropriate image processing techniques to
+create a centralized open source pipeline that is general enough for
+the user to select or add appropriate image processing techniques to
 augment the features of the lensed image, train and test data with
@@
 relatively straightforward with existing open source tools.  This
-framework is easily extendable to other feature methods and machine
-learning algorithms for supervised classification.
+framework is easily extendable to other feature extraction methods
+and machine learning algorithms for supervised classification.
 
@@
 non-lens containing mock observations for running our parameter search. 
-We keep a hold-out test set of 1,000 lens containing mock observations
+We keep a hold-out set of 1,000 lens containing mock observations
 and 1,000 non-lens containing mock observations on which we evaluate
@@
 To produce simulated lensed galaxies, we first model the mass of lens
-galaxies as the Singular Isothermal Ellipsoid (SIE). This model is
+galaxies as a Singular Isothermal Ellipsoid (SIE). This model is
 both analytically tractable and is consistent with models of
@@
 
-The normalized convergence map of SIE model is defined as:
+The normalized convergence map of the SIE model is defined as:
 %-------------------------------------------------%
@@
 %-------------------------------------------------%
-where $\theta_{\rm E}$ is the Einstein Radius and $q$ is axis ratio.
+where $\theta_{\rm E}$ is the Einstein Radius and $q$ is the axis ratio.
 The Einstein radius can be calculated from the redshift of the
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:mockimages}
+\begin{figure*}[t]
 \begin{center}
@@
   worse. Visual identification of giant arcs in the LSST images in the
-  bottom row is very difficult.}
+  bottom row is very difficult.}\label{fig:mockimages}
 \end{center}
@@
 supervised classification.  Supervised classification is a class of
-machine learning where the labels of classification in the training
-set are known.  In our case, the labels are lens and non-lens
+machine learning where the class labels in the training
+set are known.  In our case, the labels are ``lens'' and ``non-lens''
 containing images.
@@
 where our feature vector is a {\em histogram of oriented gradients}
-\citep{dalalandtriggs_05} that quantifies edges in the image.  We
+(HOG) \citep{dalalandtriggs_05} that quantifies edges in the image.  We
 describe the method and parameter search in Section~\ref{sec:hog}.  We
@@
 Section~\ref{sec:regularization}.  We briefly comment that our initial
-tests with {\em Support Vector Machine} (SVM) as an alternative
+tests with a {\em Support Vector Machine} (SVM) using radial basis
+fucntions as an alternative
 machine learning algorithm yielded negligible performance improvement,
@@
 Here, we evaluate the model on each test image, predicting a
-likelihood (``score'') between 0 and 1 that this is a lens containing
+likelihood (``score'') between 0 and 1 that image contains a lensing
 system.  This ``holdout set'' is not used in any of our parameter
@@
 % HOG intro - 
-Originally created for human detection in computer vision, histogram
+Originally created for human detection in computer vision, histogram of
 oriented gradients (HOG) is a feature extraction method that computes
@@
 within that cell.  As an example, for $N_{orient}=3$, our bins are
-centered at $\theta=0, 2\pi/3, 4\pi/3$ in radians.  If a cell has no
-gradient in the vertical direction, and only a gradient across the
-horizontal direction, say in the positive x-direction with
-$\theta=\pi/2$, it will contribute 75\% of its magnitude to the
+centered at $\theta=0, 2\pi/3, 4\pi/3$ in radians.  If a cell
+only has a gradient in the
+$\theta=\pi/2$ direction, it will contribute 75\% of its magnitude to the
 $\theta=2\pi/3$ bin, and 25\% of its magnitude to the $\theta=0$ bin.
@@
 returns the final feature vector.  The division of the image and the
-quantization of orientations provide a total of 3 parameters in HOG:
+quantization of orientations are thus controlled by 3 parameters in HOG:
 $N_{orient}$, cells-per-block, and pixels-per-cell.  We discuss how we
@@
 each cell with respect to the neighboring cell.  In general, this will
-downweight arc-like edges in cells that neighbor very bright cells,
+down-weight arc-like edges in cells that neighbor very bright cells,
 such as cells that cover the central lens galaxy.  We therefore vary
@@
 additional information that an increase in $N_\text{orient}$ will
-provide.  The best case number of orientations for each dataset is
-$N_\text{orient,HST}=9$, $N_\text{orient,LSST10}=3$, \todo{and
+provide.  \todo{From the grid search, the best case number of orientations
+for each dataset is
+$N_\text{orient,HST}=9$, $N_\text{orient,LSST10}=3$, and
   $N_\text{orient,LSST1}=$.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
-\begin{figure*}[t]\label{fig:hogimages}
+\begin{figure*}[t]
 \begin{center}
@@
   magnitudes of each of the oriented edges within the visualized
-  cells.}
+  cells.}\label{fig:hogimages}
 \end{center}
@@
 the general category of {\em{classification}} in machine learning. In
-general the task is to find a function that assigns data points $x$ to
+general, the task is to find a function that assigns data points $x$ to
 one of two or more classes, denoted by the class label $y$.  This is
@@
 case, we have two classes: lens and non-lens containing images, and
-the data points $x$ are the HOG feature vectors transformed from the
-training set data.  In this paper we use the Logisitic Regression (LR)
-algorithm, for which the decision boundary is a hyperplane .  (The
+the data points $x$ are the HOG feature vectors extracted from the
+images.  In this paper we use the \em{Logisitic Regression}
+(LR) algorithm, for which the decision boundary is a hyperplane.  (The
 equivalent in the regression setting would be linear regression.) In
@@
 do not necessarily produce a linear decision boundary, such as
-Support Vector Machines (SVM), Random Forests, and Neural Networks.
-training set data \citep{hastie_09}.
+\em{Support Vector Machines} (SVM), \em{Random Forests}, and
+\em{Neural Networks} \citep{hastie_09}.
 
@@
 overfitting can become an issue. (An example of an extreme case
-of overfitting would be if you fit a degree $n$ polynomial to $n$
+of overfitting is fitting a degree $n$ polynomial to $n$
 points.  The polynomial would simply wiggle so that it goes
@@
 minimized), on a subset of the data called the {\em{training set}} and
-its performance (goodness of fit) is evaluated both on the the
-training set and a set of hold-out data called the {\em{test set}}
+its performance (goodness of fit) is evaluated both on the
+training set and a separate {\em{test set}}
 that was not used in constructing the model.
-Figure~\ref{fig:regularization} shows the performance of a model for
+Figure~\ref{fig:regularization} shows the performance of a model with
 selected HOG parameters as a function of the regularization parameter,
@@
 correctly classified, or by some other metric, such as the area under
-the Receiver Operating Characteristic curve (see
-Section~\ref{sec:ROC}).)
+the Receiver Operating Characteristic curve described in
+Section~\ref{sec:ROC}.)
 
@@
 and regularization parameters.  The models have been evaluated on a
-hold-out test set of 1,000 images that were not used in the parameter
+hold-out set of 1,000 images that were not used in the parameter
 search.  We show the mock HST, LSST1, and LSST10 results respectively
@@
 % Training behavior with C
-As expected, the training set increases and asymptotes with
+As expected, the training set AUC increases and asymptotes with
 $C_\text{LogReg}$.  With increasing model complexity, the model better
@@
 % Train time with Creg
-For fixed train size, the log of the train time roughly scales
+For fixed training set size, the log of the train time roughly scales
 linearly with the log of $C_\text{LogReg}$.  Since lower values of
@@
 \caption{AUC of the model with varying LR regularization coefficient
-  parameter, $C_{reg}$, used when training the model classifier.  We
-  use a subset of the the 10,000 training images to search over the LR
-  $C_{reg}$ parameter, training on 8,000 and testing on 1,000.  Each
+  parameter, $C_{LogReg}$, used when training the model classifier.  We
+  use a subset of the 10,000 training images to search over the LR
+  $C_{LogReg}$ parameter, training on 8,000 and testing on 1,000.  Each
   panel corresponds to a different mock observation.  From left to
@@
 In this section, we show the effects of training set size on model
-performance on the holdout test set of 1,000 images.  We also compare
+performance on the hold-out test set of 1,000 images.  We also compare
 the improvement between images that include the lens galaxy and images
@@
 with an exception of the data point corresponding to train size of
-2000.  Generally, a larger training set will require an increase in
-model complexity to capture additional information.  This is also true
-for the optimal $C_\text{LogReg}$ dependence on the number of training
-images in the nLSST10 data.  But, the required complexity is
-systematically less than for the LSST10 images.
+2000.  Generally, a larger training set allows for an increase in
+model complexity without reducing its ability to generalize.  This is
+also true for the optimal $C_\text{LogReg}$ dependence on the number
+of training images in the nLSST10 data.  But, the required complexity
+is systematically less than for the LSST10 images.
 
@@
 nLSST10 as a function of the size of the training set for the optimal
-regularization parameter for that subset training data.  Each model
+regularization parameter for that subset of the training data.  Each model
 uses features extracted with the same HOG parameterization from the
-grid search and the optimal regularization parameter for that subset
-train data.  The train time of a given model generally increases for
+grid search and the optimal regularization parameter for that subset of
+the training data.  The train time of a given model generally increases for
 increasing regularization parameter.  For the subset of train size
@@
 Figure~\ref{fig:ROCsamplesLSST10} illustrates four images from each
-paradigm for the holdout test set of LSST10.  The trained model used
-the entire 10,000 training set.  The left two columns show lens
+paradigm for the hold-out test set of LSST10.  The trained model used
+the entire 10,000 image training set.  The left two columns show lens
 systems, and the right two columns show non-lens systems.  The
@@
 threshold.  On the other hand the failed classification of the false
-negatives (the highest scoring non-lens systems) and the false
-positives (the lowest scoring lens systems) are also least sensitive
+positives (the highest scoring non-lens systems) and the false
+negatives (the lowest scoring lens systems) are also least sensitive
 to the threshold.  False negatives are typically lens systems with
@@
 We have also made use of a new sophisticated set of mock observations,
-which will also be made publicly available.  The lensing systems have
+which will be made publicly available.  The lensing systems have
 lens galaxies generated with a realistic redshift distribution and
@@
 regression, are scalable and relatively easy to parallelize with open
-source tools such as {\em Spark}\footnote{http://spark.apache.org/}.
+source tools such as {\em Apache Spark}\footnote{http://spark.apache.org/}.
 Our work indicates that HOG feature extraction plus a linear
@@
   scale computing resources, or specialized hardware like GPUs.}
-These methods also scale for large datasets on a computing cluster, if
+The methods also scale to large datasets on a computing cluster, if
 needed.
@@
 % Caveat of the mock data set
-One major caveat of our resuls is the fact that our mock data likely
+One major caveat to our resuls is the fact that our mock data likely
 does not describe the full range of lens and non-lens images that will
@@
 through grant NSF PHY-1125897 and an endowment from the Kavli
-Foundation and its founder Fred Kavli.emacs -nw 
+Foundation and its founder Fred Kavli.
 \lastpagefootnotes

### 2017-03-23 ms.tex
minor changes to matt's modifications

@@
 \citep{warrenanddye_03}, and high redshift galaxy formation
-\citep{allam_etal07}. They also provide a geometric test of cosmology via
-comparison of predicted arc abundances with observed abundances
-\citep{kochanek_96,chae_03,linder_04}, and via time-delay between signals
-from multiply imaged quasars \citep{xli_etal12,suyu_etal14,suyu_etal16}.
+\citep{allam_etal07}. Strong lenses also provide a geometric test of
+cosmology via comparison of predicted arc abundances with observed
+abundances \citep{kochanek_96,chae_03,linder_04}, and via time-delay
+between signals from multiply imaged quasars
+\citep{xli_etal12,suyu_etal14,suyu_etal16}.
 
@@
 Pattern recognition methods have transitioned to using ``machine
-learning'' algorithms in place of manual cutoffs.  With
-machine learning, we can train a model to separate a dataset into
-a known set of classes, such as ``lensing systems'' and
-``non-lensing systems''. However, many classic machine learning
-algorithms do not work well in image space, i.e. directly using the
-raw pixel values of the image, but first require a process of
-\em{feature engineering}, in which domain expertise is used to
-extract variables which are more directly related to the classification
-task at hand.  An example would be the application of an edge detector.
-The optimal weights and cutoffs for these derived variables that are
-used to determine the class label of an image are found automatically
-by the algorithm.
+learning'' algorithms in place of manual cutoffs.  With machine
+learning, we can train a model to separate a dataset into a known set
+of classes, such as ``lensing systems'' and ``non-lensing
+systems''. However, many classic machine learning algorithms do not
+work well in image space, i.e. directly using the raw pixel values of
+the image, but first require a process of \em{feature engineering}.
+{\em Feature engineering} uses domain expertise 
+to extract variables
+that are more directly related to the classification task at hand.  An
+example would be the application of an edge detector.  The optimal
+weights and cutoffs for these derived variables that are used to
+determine the class label of an image are found automatically by the
+algorithm.
 
@@
 images. \citet{lanusse_etal17} used state-of-the-art deep residual
-neural networks
-to also work directly in the image space with minimal image
-pre-processing.  A major strength of the \citet{lanusse_etal17}
+neural networks to also work directly in the image space with minimal
+image pre-processing.  A major strength of the \citet{lanusse_etal17}
 implementation is that in comparison to deep convolutional neural
-networks, deep residual neural networks have been found to
-be easier to train and perform better.
+networks, deep residual neural networks have been found to be easier
+to train and perform better (Metcalf et al., in prep).
 
 %  Relevance of our work
-While there has been a recent surge in the use of deep neural
-networks applied to image classification problems in astronomy,
-it is not always easy to scale these techniques to large data
-sets, nor are the necessary computational resources and hardware,
-such as GPUs, easily accessible to the
-entire scientific community.  We present a supervised classification
-pipeline built with open source tools, tested on mock HST and LSST
-data, which will also be made publicly available.  Our goal is to
-create a centralized open source pipeline that is general enough for
-the user to select or add appropriate image processing techniques to
-augment the features of the lensed image, train and test data with
-different machine learning techniques, and to select the sequence of
-methods that provides optimal model performance.  Results are
-reproducible on personal computers, as both the pipeline and the
-data will be publicly distributed.
+While there has been a recent surge in the use of deep neural networks
+applied to image classification problems in astronomy, it is not
+always easy to scale these techniques to large data sets, nor are the
+necessary computational resources and hardware, such as graphical
+processing units (GPUs), easily accessible to the entire scientific
+community.  We present a supervised classification pipeline built with
+open source tools.  We test the pipeline on mock HST and LSST data,
+which will also be made publicly available.  Our goal is to create a
+centralized open source pipeline that is general enough for the user
+to select or add appropriate image processing techniques to augment
+the features of the lensed image, train and test data with different
+machine learning techniques, and to select the sequence of methods
+that provides optimal model performance.  Results are reproducible on
+personal computers, as both the pipeline and the data will be publicly
+distributed.
 
@@
 tests with a {\em Support Vector Machine} (SVM) using radial basis
-fucntions as an alternative
+functions as an alternative
 machine learning algorithm yielded negligible performance improvement,

### 2017-03-23 ms.tex
Added grid search sample results for discussion

@@
 work well in image space, i.e. directly using the raw pixel values of
-the image, but first require a process of \em{feature engineering}.
-{\em Feature engineering} uses domain expertise 
-to extract variables
+the image, but first require a process of {\em feature engineering}.
+{\em Feature engineering} uses domain expertise to extract variables
 that are more directly related to the classification task at hand.  An
@@
 \hline \\ [-0.2cm]
-N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & HOG size & Score \\ [0.2cm]
+N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & Score \\ [0.2cm]
 \hline \\ [-0.2cm]
@@
 \hline \\ [-0.2cm]
-9 & (4, 4) & (3, 3) & 50. & &$0.76181\pm0.00491$\\ [0.2cm]
-9 & (4, 4) & (1, 1) & 50. & &$0.83403\pm0.00547$\\ [0.2cm]
-9 & (8, 8) & (3, 3) & 50. & &$0.85417\pm0.00851$\\ [0.2cm] 
-9 & (8, 8) & (1, 1) & 50. & &$0.86389\pm0.00687$\\ [0.2cm] 
-9 & (16, 16) & (1, 1) & 50. & & $0.88542\pm0.00680$ \\ [0.2cm]
-9 & (16, 16) & (3, 3) & 10. & &$0.89306\pm0.00687$ \\ [0.2cm]
-8 & (16, 16) & (3, 3) & 50. & &$0.90000\pm0.00170$ \\ [0.2cm]
-9 & (16, 16) & (3, 3) & 50. & &$0.90139\pm0.00804$ \\ [0.2cm]
+9 & (16, 16) & (4, 4) & 10. & $0.90141\pm 0.00658$ \\ [0.2cm]
+9 & (24, 24) & (3, 3) & 10. & $0.89266\pm 0.01033$ \\ [0.2cm]
+9 & (16, 16) & (1, 1) & 10. & $0.87484\pm 0.00671$ \\ [0.2cm]
+7 & (16, 16) & (4, 4) & 10. & $0.90031\pm 0.00956$ \\ [0.2cm]
+5 & (16, 16) & (4, 4) & 10. & $0.89453\pm 0.00840$ \\ [0.2cm]
+9 & (32, 32) & (4, 4) & 10. & $0.85828\pm 0.01004$ \\ [0.2cm]
+9 & (32, 32) & (4, 4) & 50. & $0.87344\pm 0.01267$ \\ [0.2cm]
 \hline \\ [-0.2cm]
@@
 \hline \\ [-0.2cm]
-& & & & &\\
-& & & & &\\ [0.2cm]
+3 & (5, 5) & (4, 4) & 100. & $0.64328\pm 0.00769$ \\ [0.2cm]
+4 & (5, 5) & (4, 4) & 100. & $0.62469\pm 0.00485$ \\ [0.2cm]
+3 & (5, 5) & (2, 2) & 100. & $0.63281\pm 0.00869$ \\ [0.2cm]
+5 & (5, 5) & (4, 4) & 100. & $0.62734\pm 0.00800$ \\ [0.2cm]
+3 & (3, 3) & (4, 4) & 100. & $0.59109\pm 0.00313$ \\ [0.2cm]
+3 & (3, 3) & (2, 2) & 100. & $0.57297\pm 0.00508$ \\ [0.2cm]
+4 & (4, 4) & (3, 3) & 100. & $0.63125\pm 0.01227$ \\ [0.2cm]
 \hline
@@
 \label{tab:gridsearch}
-\tablecomments{Panel (a) shows the results of a grid search across a
-  range of HOG parameters and regression coefficient \wording{with
-    training and test sets of size 1440 with the HST-like mock
-    dataset.}  Panel (b) shows the corresponding results for training
-  and test sets of \wording{size 5760 with the LSST mock dataset.}  We
-  explore different HOG parameters in each dataset due to resolution
-  and image size differences.}
+\tablecomments{Panel (a) shows a subsample of the results of a grid
+  search for HST across a range of HOG parameters and regression
+  coefficient. Panel (b) shows a subsample of the results of a grid
+  search for LSST10. Each use a data set of size $2\times8000$ for
+  cross validation to get the average scores and standard deviation.
+  We explore different HOG parameters in each dataset due to
+  resolution and image size differences.}
 \end{table}
@@
 additional information that an increase in $N_\text{orient}$ will
-provide.  \todo{From the grid search, the best case number of orientations
-for each dataset is
-$N_\text{orient,HST}=9$, $N_\text{orient,LSST10}=3$, and
-  $N_\text{orient,LSST1}=$.}
+provide.  From the grid search, the best case number of orientations
+for each dataset is $N_\text{orient,HST}=9$,
+$N_\text{orient,LSST10}=3$, and $N_\text{orient,LSST1}=5$.
 
@@
   with arc features showing up as edges across radial orientations.
-  \wording{Each of the oriented gradients within a cell is
-    color-coded by magnitude, and represented as a line in the
-    direction perpendicular to that gradient.}  The actual extracted
-  features fill a one-dimensional feature vector comprised of the
-  magnitudes of each of the oriented edges within the visualized
+  Each of the oriented gradients within a cell is color-coded by
+  magnitude, and represented as a line in the direction perpendicular
+  to that gradient.  The actual extracted features fill a
+  one-dimensional feature vector comprised of the magnitudes of each
+  of the oriented edges within the visualized
   cells.}\label{fig:hogimages}
@@
 
-Figure~\ref{fig:trainsizeLSST10} shows how the AUC and the optimal
-logistic regression coefficient depend on the log of the size of the
-training set for both the LSST10 data in solid blue lines, and the
-nLSST10 data in dashed blue lines.  The AUC for models trained on the
-LSST10 data improves almost linearly with the log of the training set
-size, increasing from AUC=0.705 to AUC=0.788 when the train size is
-increased from 500 lens/non-lens images to 8000 lens/non-lens images.
-However, for the nLSST10 data, where the lens galaxy has been removed
-from the images, the improvement is less dramatic.  With the same
-increase in training size, the AUC for nLSST10 changes from just below
-0.77 to just below 0.78.
-
-In solid red, we see that the optimal value for $C_\text{LogReg}$ for
-LSST10 roughly scales logarithmically with the log of the train size,
-with an exception of the data point corresponding to train size of
-2000.  Generally, a larger training set allows for an increase in
-model complexity without reducing its ability to generalize.  This is
-also true for the optimal $C_\text{LogReg}$ dependence on the number
-of training images in the nLSST10 data.  But, the required complexity
-is systematically less than for the LSST10 images.
+% LSST10 and nLSST10 behavior
+Figure~\ref{fig:trainsizeLSST} shows how the AUC depends on the log of
+the size of the training set for both the LSST10 (LSST1) data in the
+solid blue (red) line, and the nLSST10 (nLSST1) data in dashed blue
+(red) line.  The AUC for models trained on the LSST10 data improves
+almost linearly with the log of the training set size, increasing from
+AUC=0.705 to AUC=0.788 when the train size is increased from
+$2\times500$ lens/non-lens images to $2\times8000$ lens/non-lens
+images.  However, for the nLSST10 data, where the lens galaxy has been
+removed from the images, the improvement is less dramatic.  With the
+same increase in training size, the AUC for nLSST10 changes from just
+below 0.77 to just below 0.78.
 
@@
 
+% LSST1 and nLSST1 behavior
+In red, we see an analogous improvement for LSST1 and nLSST1.  Here,
+the crossover happens at train size of $2x1000$, where an increase in
+larger training data set size does not help improve the AUC for nLSST1.
+
 %M Model complexity, train time, and performance
@@
 
+% Train time dependence
+We illustrate the dependence of train time on both the size of the
+training set and model complexity in Figures~\ref{fig:traintimeLSST10}
+and \ref{fig:traintimeLSST1}.  In red,
+Figure~\ref{fig:traintimeLSST10} shows that the optimal values for
+$C_\text{LogReg}$.  For LSST10, $C_\text{LogReg}$ roughly scales
+logarithmically with the log of the train size, with an exception of
+the data point corresponding to train size of 2000.  Generally, a
+larger training set allows for an increase in model complexity without
+reducing its ability to generalize.  This is also true for the optimal
+$C_\text{LogReg}$ dependence on the number of training images in the
+nLSST10 data.  But, the required complexity is systematically less
+than for the LSST10 images.
+
 % Train time
-Figure~\ref{fig:traintimeLSST10} shows the train time for LSST10 and
-nLSST10 as a function of the size of the training set for the optimal
-regularization parameter for that subset of the training data.  Each model
-uses features extracted with the same HOG parameterization from the
-grid search and the optimal regularization parameter for that subset of
-the training data.  The train time of a given model generally increases for
-increasing regularization parameter.  For the subset of train size
-$N_\text{train}=2000$ in LSST10, the optimal regularization parameter
-happened to be $C_{LogReg}=100$, whereas it was $C_{LogReg}=500$ for
-the subset of trainsize 1000, and $C_{LogReg}=1000$ for the subset of
-trainsize 4000.  This makes the train time increase at train size
+In blue, Figure~\ref{fig:traintimeLSST10} also shows the train time
+for LSST10 and nLSST10 as a function of the size of the training set
+for the optimal regularization parameter for that subset of the
+training data.  Each model uses features extracted with the same HOG
+parameterization from the grid search and the optimal regularization
+parameter for that subset of the training data.  The train time of a
+given model generally increases for increasing regularization
+parameter.  For the subset of train size $N_\text{train}=2000$ in
+LSST10, the optimal regularization parameter happened to be
+$C_{LogReg}=100$, whereas it was $C_{LogReg}=500$ for the subset of
+trainsize 1000, and $C_{LogReg}=1000$ for the subset of trainsize
+4000.  This makes the train time increase at train size
 $N_\text{train}=2000$ for LSST10 less dramatic than the average
@@
 
+% Train time behavior for LSST1 and nLSST1
+\wording{For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
+  relationships between train time and train size in blue, and the
+  optimal regulariztion parameter (or model complexity) in red.
+  Contrary to what we found when comparing LSST10 to nLSST10, nLSST1
+  requires more model complexity than LSST1.  Recall that LSST1 and
+  nLSST1 correspond to single epoch simulated exposures with the best
+  seeing; these images exhibit better resolution but worse signal to
+  noise.  The switch in required model complexity corresponds to a
+  trade-off between features from the lens galaxy providing additional
+  information or swamping the signal from a strong lensing arc.}
+
 % AUC vs. regularization on larger train/test set with comparable
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/trainsize/LSST10_with_nLSST10.pdf}
+\includegraphics[width=\columnwidth]{figures/trainsize/combined_LSST10_with_nLSST10.pdf}
 \caption{Solid (dotted) blue line: AUC for models with varying size of
   the training set for LSST10 (nLSST10).  Solid (dotted) red line:
-  Optimal regularization parameter for training on the train size for
-  LSST10 (nLSST10). The improvement of AUC scales linearly with the
-  log of the training set size, but train time roughly scales
-  logarithmically.  Note, LSST10 requires more model complexity to
-  exceed the performance of nLSST10.}\label{fig:trainsizeLSST10}
+  Same for LSST1. The improvement of AUC scales roughly linearly with
+  the log of the training set size.  However, LSST10 and LSST1 have a
+  steeper improvement with data training size.  The performance of
+  nLSST10 and nLSST1 models trained on smaller training data sets is
+  better than the respective LSST10 and LSST1 models trained on the
+  same size data, but the LSST10 and LSST1 models outperform with
+  larger size training data set.}\label{fig:trainsizeLSST}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\columnwidth]{figures/traintime/LSST10.pdf}
+  \includegraphics[width=\columnwidth]{figures/traintime/LSST10.pdf}}
 \caption{Solid (dotted) blue line: Train time for models with varying
   size of the training set for LSST10 (nLSST10).  Train time roughly
-  scales logarithmically.  Note, LSST10 requires more model complexity
-  to exceed the performance of nLSST10, and therefore requires more
+  scales logarithmically with the train size, but the train time is
+  also affected by model complexity.  Solid (dotted) red line: Best
+  regularization parameter as a function of train size.  Note, LSST10
+  requires more model complexity to exceed the performance of nLSST10
+  (see blue solid and dotted lines in
+  Figure~\ref{fig:trainsizeLSST}), and therefore requires more
   training time for continual increase in
-  performance.}\label{fig:traintimeLSST10}
+  performance. }\label{fig:traintimeLSST10}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%            
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=\columnwidth]{figures/traintime/LSST1.pdf}}
+\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for LSST1.
+  Here, nLSST1 requires more model complexity than LSST1.  Note, that
+  LSST1 and nLSST1 have better seeing but reduced overall signal to
+  noise than LSST10 and nLSST10.  This corresponds to better
+  resolution, and therefore sharper edge features that prominently
+  corespond to arcs.}\label{fig:traintimeLSST1}
 \end{center}
@@
 equivalent improvement to the study illustrated in
-Figure~\ref{fig:trainsizeLSST10}.
+Figure~\ref{fig:trainsizeLSST}.
 
@@
 performance on images containing the lens galaxy to improve further
-with larger training sets (see Figure~\ref{fig:trainsizeLSST10}).
+with larger training sets (see Figure~\ref{fig:trainsizeLSST}).
 
@@
 systems, and the right two columns show non-lens systems.  The
-annotation in the top left corner of each images shows the score,
-\todo{and the letters in the bottom right label the paradigm of
-  performance.}
+annotation in the top left corner of each images shows the score.
 
@@
 $z\gsim0.5$ (lighter colors in bottom row) and/or lens galaxies with
-velocity dispersions higher than $\sigma_v\lsim230.$~km/s (darker
+velocity dispersions larger than $\sigma_v\gsim230.$~km/s (darker
 colors in right figure).  Note that lensing galaxies with smaller

### 2017-03-23 ms.tex
Fixed minor em bugs and table alignment issue

@@
 \hline \\ [-0.2cm]
-N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & Score \\ [0.2cm]
+N$_{orient}$ & Pixels/Cell & Cells/Block & C$_{reg}$ & Score & \\ [0.2cm]
 \hline \\ [-0.2cm]
@@
 \hline \\ [-0.2cm]
-9 & (16, 16) & (4, 4) & 10. & $0.90141\pm 0.00658$ \\ [0.2cm]
-9 & (24, 24) & (3, 3) & 10. & $0.89266\pm 0.01033$ \\ [0.2cm]
-9 & (16, 16) & (1, 1) & 10. & $0.87484\pm 0.00671$ \\ [0.2cm]
-7 & (16, 16) & (4, 4) & 10. & $0.90031\pm 0.00956$ \\ [0.2cm]
-5 & (16, 16) & (4, 4) & 10. & $0.89453\pm 0.00840$ \\ [0.2cm]
-9 & (32, 32) & (4, 4) & 10. & $0.85828\pm 0.01004$ \\ [0.2cm]
-9 & (32, 32) & (4, 4) & 50. & $0.87344\pm 0.01267$ \\ [0.2cm]
+9 & (16, 16) & (4, 4) & 10. & $0.90141\pm 0.00658$ &\\ [0.2cm]
+9 & (24, 24) & (3, 3) & 10. & $0.89266\pm 0.01033$ &\\ [0.2cm]
+9 & (16, 16) & (1, 1) & 10. & $0.87484\pm 0.00671$ &\\ [0.2cm]
+7 & (16, 16) & (4, 4) & 10. & $0.90031\pm 0.00956$ &\\ [0.2cm]
+5 & (16, 16) & (4, 4) & 10. & $0.89453\pm 0.00840$ &\\ [0.2cm]
+9 & (32, 32) & (4, 4) & 10. & $0.85828\pm 0.01004$ &\\ [0.2cm]
+9 & (32, 32) & (4, 4) & 50. & $0.87344\pm 0.01267$ &\\ [0.2cm]
 \hline \\ [-0.2cm]
@@
 \hline \\ [-0.2cm]
-3 & (5, 5) & (4, 4) & 100. & $0.64328\pm 0.00769$ \\ [0.2cm]
-4 & (5, 5) & (4, 4) & 100. & $0.62469\pm 0.00485$ \\ [0.2cm]
-3 & (5, 5) & (2, 2) & 100. & $0.63281\pm 0.00869$ \\ [0.2cm]
-5 & (5, 5) & (4, 4) & 100. & $0.62734\pm 0.00800$ \\ [0.2cm]
-3 & (3, 3) & (4, 4) & 100. & $0.59109\pm 0.00313$ \\ [0.2cm]
-3 & (3, 3) & (2, 2) & 100. & $0.57297\pm 0.00508$ \\ [0.2cm]
-4 & (4, 4) & (3, 3) & 100. & $0.63125\pm 0.01227$ \\ [0.2cm]
+3 & (5, 5) & (4, 4) & 100. & $0.64328\pm 0.00769$ &\\ [0.2cm]
+4 & (5, 5) & (4, 4) & 100. & $0.62469\pm 0.00485$ &\\ [0.2cm]
+3 & (5, 5) & (2, 2) & 100. & $0.63281\pm 0.00869$ &\\ [0.2cm]
+5 & (5, 5) & (4, 4) & 100. & $0.62734\pm 0.00800$ &\\ [0.2cm]
+3 & (3, 3) & (4, 4) & 100. & $0.59109\pm 0.00313$ &\\ [0.2cm]
+3 & (3, 3) & (2, 2) & 100. & $0.57297\pm 0.00508$ &\\ [0.2cm]
+4 & (4, 4) & (3, 3) & 100. & $0.63125\pm 0.01227$ &\\ [0.2cm]
 \hline
@@
 \label{tab:gridsearch}
+
 \tablecomments{Panel (a) shows a subsample of the results of a grid
@@
 the data points $x$ are the HOG feature vectors extracted from the
-images.  In this paper we use the \em{Logisitic Regression}
+images.  In this paper we use the {\em Logisitic Regression}
 (LR) algorithm, for which the decision boundary is a hyperplane.  (The
@@
 do not necessarily produce a linear decision boundary, such as
-\em{Support Vector Machines} (SVM), \em{Random Forests}, and
-\em{Neural Networks} \citep{hastie_09}.
+{\em Support Vector Machines} (SVM), {\em Random Forests}, and
+{\em Neural Networks} \citep{hastie_09}.
 

### 2017-03-23 ms.tex
Final edits before circulating

@@
 % Train time behavior for LSST1 and nLSST1
-\wording{For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
+For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
 relationships between train time and train size in blue, and the
@@
 trade-off between features from the lens galaxy providing additional
-  information or swamping the signal from a strong lensing arc.}
+information or swamping the signal from a strong lensing arc.
 

### 2017-03-27 ms.tex

@@
 Lemont, IL 60439};\\
-$^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
+$^5${JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
 $^6${Institute of Cosmology and Gravitation, University of Portsmouth, Burnaby Rd, Portsmouth, PO1 3FX, UK};\\

### 2017-03-28 ms.tex
Added the minor changes from Tom's comments

--- 2017-03-23 ms.tex
@@
 images exhibit an AUC of 0.975 for an HST-like sample.  However, for
-one orbit of LSST, our model only reaches an AUC of 0.625.  For
+one exposure of LSST, our model only reaches an AUC of 0.625.  For
 10-year mock LSST observations, the AUC improves to 0.809.  Model
@@
 cosmology via comparison of predicted arc abundances with observed
-abundances \citep{kochanek_96,chae_03,linder_04}, and via time-delay
+abundances \citep{kochanek_96,chae_03,linder_04}, via time-delay
 between signals from multiply imaged quasars
-\citep{xli_etal12,suyu_etal14,suyu_etal16}.
+\citep{xli_etal12,suyu_etal14,suyu_etal16,bonvin_etal17}, and via
+distance ratios in lenses with sources at multiple redshifts
+\citep{jullo_etal10,collett_etal12,collettandauger_14}.
 
@@
 However, future datasets like Euclid \citep{oguriandmarshall_10} and
-LSST expect to find tens of thousands galaxy-scale strong lenses
-\citep{pawase_etal12}.  The volume of upcoming data challenges the
+LSST expect to find hundreds of thousands galaxy-scale strong lenses
+\citep{collett_15}.  The volume of upcoming data challenges the
 scalability of a pure citizen science approach.
@@
 test data sets have $50\%$ lensed and $50\%$ unlensed images, which is
-not expected in observations.  The ROC curve metric is insensitive to
-the ratio, but is sensitive to the sampling.  Given alternative lens
-and non-lens sample splittings, our true positive and false positive
-rates in the ROC curves would stay the same, making the ROC curve a
-more standard metric in the literature.  On the other hand, the ROC
-curves show a representative rate for lens and source distributions
-that are evenly sampled.  We do {\it not} expect this sampling to be
-representative of what we might expect from a an observational survey.
-We leave these additional challenges to future work.
+not expected in observations.
+
+% Realistic ratios
+For images selected for a massive elliptical, the number of non-lenses
+will outnumber lenses by at least 1000 to 1.  Therefore, a sample that
+is $50\%$ pure requires a classifier with a false positive rate of
+0.001.  Looking at the green line in Figure~\ref{fig:PRcompilation}, a
+classification threshold for a pure sample only encapsulates
+$\sim10\%$ (in recall) of all of our lenses before contamination from
+non-lenses leaks into the selection.  A maximally large and pure
+sample from our method would require further filtering, e.g. by
+citizen science.
+
+% ROC curve metric
+The ROC curve metric is insensitive to the ratio, but is sensitive to
+the sampling.  Given alternative lens and non-lens sample splittings,
+our true positive and false positive rates in the ROC curves would
+stay the same, making the ROC curve a more standard metric in the
+literature.  On the other hand, the ROC curves show a representative
+rate for lens and source distributions that are evenly sampled.  We do
+{\it not} expect this sampling to be representative of what we might
+expect from a an observational survey.  We leave these additional
+challenges to future work.
 

### 2017-03-28 ms.tex
Changed LSST1 to LSST-best

@@
 of lens and non-lens containing systems: (1) HST-like observations,
-(2) LSST-like observations over the span of one year, and (3)
-LSST-like observations over the span of ten years.  We respectively
-label these observations as HST, LSST1, and LSST10.
+(2) best single exposure LSST-like observations, and (3) LSST-like
+observations over the span of ten years.  We respectively label these
+observations as HST, LSST-best, and LSST10.
 
@@
 strategies to use the simulated exposures. First, we build one
-single-epoch image for each field (hereafter labeled as LSST1) by
+single-epoch image for each field (hereafter labeled as LSST-best) by
 keeping only the best seeing exposure.  Second, we build another
-``worst-case'' stacked image by degrading all individual exposures to
-match the one with the worst seeing and co-add all exposures to a
-single image (hereafter labeled as LSST10).  These two sets of images
-will allow us to investigate the trade-off between resolution and
-signal-to-noise for our automated lens search.
+``worst-case'' stacked image by degrading all individual exposures,
+ten per filter per year, to match the one with the worst seeing and
+co-add all exposures to a single image (hereafter labeled as LSST10).
+These two sets of images will allow us to investigate the trade-off
+between resolution and signal-to-noise for our automated lens search.
 
@@
 LSST10.  The right-most column corresponds to the simulated systems of
-LSST1.  These images have resolution $45\times45~{\rm pixels}^2$ with
+LSST-best.  These images have resolution $45\times45~{\rm pixels}^2$ with
 $0.18$~arcsec/pixel.  LSST10 images visually exhibit the improved
 signal to noise ratio, recovering the arc feature, albeit at a much
-lower resolution than with the HST-like image or the LSST1 image.  The
-top images of LSST10 and LSST1 show a visible lensed source galaxy
-image.  The bottom images are washed out in the bottom row, where the
-magnification of the source galaxy is not as large.  The ground based
-noise, PSF, and limited resolution of the LSST1 make visual giant arc
-identification difficult, except in systems with the most magnified
-source galaxies.
+lower resolution than with the HST-like image or the LSST-best image.
+The top images of LSST10 and LSST-best show a visible lensed source
+galaxy image.  The bottom images are washed out in the bottom row,
+where the magnification of the source galaxy is not as large.  The
+ground based noise, PSF, and limited resolution of the LSST-best make
+visual giant arc identification difficult, except in systems with the
+most magnified source galaxies.
 
@@
 \includegraphics[width=2\columnwidth]{figures/tiles/compilations/telescope_compilation.pdf}
-\caption{Left to right show example mock HST, LSST 10 year, and LSST 1
-  year images.  The top row corresponds to a lensing system with a
+\caption{Left to right show example mock HST, LSST 10 year, and
+  LSST-best images.  The top row corresponds to a lensing system with a
   very visible arc signature, and the bottom row to a lensing system
@@
 galaxies on the performance of our lens identification pipeline.  We
-generate another set of each HST, LSST1, and LSST10 images without the
-lens galaxy.  We respectively label these nHST, nLSST1, and nLSST10.
+generate another set of each HST, LSST-best, and LSST10 images without the
+lens galaxy.  We respectively label these nHST, nLSST-best, and nLSST10.
 
@@
 for each dataset is $N_\text{orient,HST}=9$,
-$N_\text{orient,LSST10}=3$, and $N_\text{orient,LSST1}=5$.
+$N_\text{orient,LSST10}=3$, and $N_\text{orient,LSST-best}=5$.
 
@@
 hold-out set of 1,000 images that were not used in the parameter
-search.  We show the mock HST, LSST1, and LSST10 results respectively
+search.  We show the mock HST, LSST-best, and LSST10 results respectively
 in red, blue, and green.  Solid lines correspond to a model trained
@@
 Figure~\ref{fig:regularization} shows the model performance as a
-function of regularization parameter for each data set HST, LSST, and
+function of regularization parameter for each data set HST, LSST-best, and
 LSST10.  The solid and dotted blue lines respectively correspond to
@@
 Figure~\ref{fig:trainsizeLSST} shows how the AUC depends on the log of
-the size of the training set for both the LSST10 (LSST1) data in the
-solid blue (red) line, and the nLSST10 (nLSST1) data in dashed blue
+the size of the training set for both the LSST10 (LSST-best) data in the
+solid blue (red) line, and the nLSST10 (nLSST-best) data in dashed blue
 (red) line.  The AUC for models trained on the LSST10 data improves
@@
 % LSST1 and nLSST1 behavior
-In red, we see an analogous improvement for LSST1 and nLSST1.  Here,
-the crossover happens at train size of $2x1000$, where an increase in
-larger training data set size does not help improve the AUC for nLSST1.
+In red, we see an analogous improvement for LSST-best and nLSST-best.
+Here, the crossover happens at train size of $2x1000$, where an
+increase in larger training data set size does not help improve the
+AUC for nLSST-best.
 
@@
 % Train time behavior for LSST1 and nLSST1
-For LSST1, Figure~\ref{fig:traintimeLSST1} shows the same
+For LSST-best, Figure~\ref{fig:traintimeLSST1} shows the same
 relationships between train time and train size in blue, and the
 optimal regulariztion parameter (or model complexity) in red.
-Contrary to what we found when comparing LSST10 to nLSST10, nLSST1
-requires more model complexity than LSST1.  Recall that LSST1 and
-nLSST1 correspond to single epoch simulated exposures with the best
+Contrary to what we found when comparing LSST10 to nLSST10, nLSST-best
+requires more model complexity than LSST-best.  Recall that LSST-best and
+nLSST-best correspond to single epoch simulated exposures with the best
 seeing; these images exhibit better resolution but worse signal to
@@
   the training set for LSST10 (nLSST10).  Solid (dotted) red line:
-  Same for LSST1. The improvement of AUC scales roughly linearly with
-  the log of the training set size.  However, LSST10 and LSST1 have a
+  Same for LSST-best. The improvement of AUC scales roughly linearly with
+  the log of the training set size.  However, LSST10 and LSST-best have a
   steeper improvement with data training size.  The performance of
-  nLSST10 and nLSST1 models trained on smaller training data sets is
-  better than the respective LSST10 and LSST1 models trained on the
-  same size data, but the LSST10 and LSST1 models outperform with
+  nLSST10 and nLSST-best models trained on smaller training data sets is
+  better than the respective LSST10 and LSST-best models trained on the
+  same size data, but the LSST10 and LSST-best models outperform with
   larger size training data set.}\label{fig:trainsizeLSST}
@@
   \includegraphics[width=\columnwidth]{figures/traintime/LSST1.pdf}}
-\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for LSST1.
-  Here, nLSST1 requires more model complexity than LSST1.  Note, that
-  LSST1 and nLSST1 have better seeing but reduced overall signal to
+\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for LSST-best.
+  Here, nLSST-best requires more model complexity than LSST-best.  Note, that
+  LSST-best and nLSST-best have better seeing but reduced overall signal to
   noise than LSST10 and nLSST10.  This corresponds to better
@@
 \caption{Left to right: Image classification score on HST, LSST10,
-  LSST1 mock observed lensing images as a function of lensed image
+  LSST-best mock observed lensing images as a function of lensed image
   magnification.  Top row: Each panel is color coded by the lens
@@
 $\sim10\%$ (in recall) of all of our lenses before contamination from
-non-lenses leaks into the selection.  A maximally large and pure
-sample from our method would require further filtering, e.g. by
-citizen science.
+non-lenses leaks into the selection.  While information from other
+bands will certainly improve the model performance, a maximally large
+and pure sample from our method would likely require further
+filtering, e.g. by citizen science.
 

### 2017-03-30 ms.tex
Added some boldface and additional edits to text.  Last bit is to address the HST PSF

@@
 \newcommand{\todo}[1]{{\bf\color{blue} #1}}
+\newcommand{\edit}[1]{{\bf #1}}
 %%%%%%%%%% User defined symbol %%%%%%
@@
 patterns that are characteristic of strong gravitational arcs in
-galaxy-galaxy lensing.  We use logistic regression to train a
+galaxy-galaxy \edit{strong} lensing.  We use logistic regression to train a
 supervised classifier model on the HOG of HST- and LSST-like images.
@@
 images exhibit an AUC of 0.975 for an HST-like sample.  However, for
-one exposure of LSST, our model only reaches an AUC of 0.625.  For
+\edit{one exposure} of LSST, our model only reaches an AUC of 0.625.  For
 10-year mock LSST observations, the AUC improves to 0.809.  Model
@@
 abundances \citep{kochanek_96,chae_03,linder_04}, via time-delay
-between signals from multiply imaged quasars
+between signals from multiply imaged quasars \edit{
 \citep{xli_etal12,suyu_etal14,suyu_etal16,bonvin_etal17}, and via
 distance ratios in lenses with sources at multiple redshifts
-\citep{jullo_etal10,collett_etal12,collettandauger_14}.
+\citep{jullo_etal10,collett_etal12,collettandauger_14}.}
 
@@
 distribution of strong lenses, such as early-type galaxies (ETGs),
-necessitates large samples of galaxy-galaxy lensing systems.
+necessitates large samples of galaxy-galaxy \edit{strong} lensing systems.
 \citet{miraldaescudeandlehar_92} first suggested that massive
@@
 However, future datasets like Euclid \citep{oguriandmarshall_10} and
-LSST expect to find hundreds of thousands galaxy-scale strong lenses
-\citep{collett_15}.  The volume of upcoming data challenges the
+LSST expect to find \edit{hundreds of thousands galaxy-scale strong lenses
+\citep{collett_15}.}  The volume of upcoming data challenges the
 scalability of a pure citizen science approach.
@@
 observations over the span of ten years.  We respectively label these
-observations as HST, LSST-best, and LSST10.
+observations as HST, \edit{LSST-best}, and LSST10.
 
@@
 \begin{equation}
-\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)\frac{D_{ls}}{D_{s}}, 
+\theta_{\rm E} = 4\pi\left(\frac{\sigma_v}{c}\right)^2\frac{D_{ls}}{D_{s}}, 
 \end{equation}
@@
 
-We choose $\sigma_v$, $q$, and $\phi$ randomly from typical ranges of
-observed galaxies: $\sigma_v \in [200, 320]~km/s$, $q \in [0.5, 1.0]$,
-and $\phi \in [0, 360]$.  We obtain the redshift of the lens galaxy by
-matching the velocity dispersion from our simulations to the catalog
-of elliptical galaxies in the COSMOS survey from \citet{zahid_etal15},
-resulting in lens galaxy redshifts in the range, $z_l \in [0.2,0.7]$.
+We choose $\sigma_v$, $q$, and $\phi$ \edit{randomly (flat prior) from
+typical ranges of observed galaxies: $\sigma_v \in [200, 320]~km/s$,
+$q \in [0.5, 1.0]$, and $\phi \in [0, 360]$.  While a flat prior is
+not realistic, we use this as a starting point to test our pipeline
+(see Section~\ref{sec:conclusions} for more details on future
+work)}. We obtain the redshift of the lens galaxy by matching the
+velocity dispersion from our simulations to the catalog of elliptical
+galaxies in the COSMOS survey from \citet{zahid_etal15}, resulting in
+lens galaxy redshifts in the range, $z_l \in [0.2,0.7]$.
 
@@
 UDS catalog \citep{galametz_etal13}.  We rescale these background
-source galaxies, set the source redshift to $z_s=0.2$, and select
-source positions near caustics of the lensing system.  We then fix the
-projected position of the lens galaxy at the center of the field of
-view for each image.
+source galaxies, set the source redshift to \edit{$z_s=2$, and select
+  source positions near caustics of the lensing system.  The selected
+  positions are within a $2''\times2''$ square box centered on the
+  lens galaxy center of mass.} We then fix the projected position of
+the lens galaxy at the center of the field of view for each image.
 
@@
 The final part is to perform the mock observation from the ideal
-images produced in the previous step. For HST-like observations,
-galaxies along the line of sight already include noise and a point
-spread function (PSF).  We therefore stack and magnitude calibrate all
-components to produce the final HST-like images, which are
-$300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.
+images produced in the previous step.  \edit{Both our HST- and
+  LSST-like observations are monochromatic, respectively using the
+  F606W and the g-band.} For HST-like observations, galaxies along the
+line of sight already include noise and a point spread function (PSF).
+We therefore stack and magnitude calibrate all components to produce
+the final HST-like images, which are $300\times300~{\rm pix}^2$ with
+$0.03$~arcsec per pixel.
 
@@
 strategies to use the simulated exposures. First, we build one
-single-epoch image for each field (hereafter labeled as LSST-best) by
+single-epoch image for each field (hereafter labeled as \edit{LSST-best}) by
 keeping only the best seeing exposure.  Second, we build another
@@
 LSST10.  The right-most column corresponds to the simulated systems of
-LSST-best.  These images have resolution $45\times45~{\rm pixels}^2$ with
+\edit{LSST-best}.  These images have resolution $45\times45~{\rm pixels}^2$ with
 $0.18$~arcsec/pixel.  LSST10 images visually exhibit the improved
 signal to noise ratio, recovering the arc feature, albeit at a much
-lower resolution than with the HST-like image or the LSST-best image.
-The top images of LSST10 and LSST-best show a visible lensed source
+lower resolution than with the HST-like image or the \edit{LSST-best} image.
+The top images of LSST10 and \edit{LSST-best} show a visible lensed source
 galaxy image.  The bottom images are washed out in the bottom row,
 where the magnification of the source galaxy is not as large.  The
-ground based noise, PSF, and limited resolution of the LSST-best make
+ground based noise, PSF, and limited resolution of the \edit{LSST-best} make
 visual giant arc identification difficult, except in systems with the
@@
 \caption{Left to right show example mock HST, LSST 10 year, and
-  LSST-best images.  The top row corresponds to a lensing system with a
+  \edit{LSST-best} images.  The top row corresponds to a lensing system with a
   very visible arc signature, and the bottom row to a lensing system
@@
 galaxies on the performance of our lens identification pipeline.  We
-generate another set of each HST, LSST-best, and LSST10 images without the
-lens galaxy.  We respectively label these nHST, nLSST-best, and nLSST10.
+generate another set of each HST, \edit{LSST-best}, and LSST10 images without the
+lens galaxy.  We respectively label these nHST, n\edit{LSST-best}, and nLSST10.
 
@@
 for each dataset is $N_\text{orient,HST}=9$,
-$N_\text{orient,LSST10}=3$, and $N_\text{orient,LSST-best}=5$.
+$N_\text{orient,LSST10}=3$, and $N_\text{orient,\edit{LSST-best}}=5$.
 
@@
 hold-out set of 1,000 images that were not used in the parameter
-search.  We show the mock HST, LSST-best, and LSST10 results respectively
+search.  We show the mock HST, \edit{LSST-best}, and LSST10 results respectively
 in red, blue, and green.  Solid lines correspond to a model trained
@@
 Figure~\ref{fig:regularization} shows the model performance as a
-function of regularization parameter for each data set HST, LSST-best, and
+function of regularization parameter for each data set HST, \edit{LSST-best}, and
 LSST10.  The solid and dotted blue lines respectively correspond to
@@
 \includegraphics[width=.66\columnwidth]{figures/Creg/HST.pdf}
-\includegraphics[width=.66\columnwidth]{figures/Creg/LSST1.pdf}
+\includegraphics[width=.66\columnwidth]{figures/Creg/LSST-best.pdf}
 \includegraphics[width=.66\columnwidth]{figures/Creg/LSST10.pdf}
@@
 Figure~\ref{fig:trainsizeLSST} shows how the AUC depends on the log of
-the size of the training set for both the LSST10 (LSST-best) data in the
-solid blue (red) line, and the nLSST10 (nLSST-best) data in dashed blue
+the size of the training set for both the LSST10 (\edit{LSST-best}) data in the
+solid blue (red) line, and the nLSST10 (n\edit{LSST-best}) data in dashed blue
 (red) line.  The AUC for models trained on the LSST10 data improves
@@
 % LSST1 and nLSST1 behavior
-In red, we see an analogous improvement for LSST-best and nLSST-best.
+In red, we see an analogous improvement for \edit{LSST-best} and n\edit{LSST-best}.
 Here, the crossover happens at train size of $2x1000$, where an
 increase in larger training data set size does not help improve the
-AUC for nLSST-best.
+AUC for n\edit{LSST-best}.
 
@@
 % Train time behavior for LSST1 and nLSST1
-For LSST-best, Figure~\ref{fig:traintimeLSST1} shows the same
+For \edit{LSST-best}, Figure~\ref{fig:traintimeLSST1} shows the same
 relationships between train time and train size in blue, and the
 optimal regulariztion parameter (or model complexity) in red.
-Contrary to what we found when comparing LSST10 to nLSST10, nLSST-best
-requires more model complexity than LSST-best.  Recall that LSST-best and
-nLSST-best correspond to single epoch simulated exposures with the best
+Contrary to what we found when comparing LSST10 to nLSST10, n\edit{LSST-best}
+requires more model complexity than \edit{LSST-best}.  Recall that \edit{LSST-best} and
+n\edit{LSST-best} correspond to single epoch simulated exposures with the best
 seeing; these images exhibit better resolution but worse signal to
@@
   the training set for LSST10 (nLSST10).  Solid (dotted) red line:
-  Same for LSST-best. The improvement of AUC scales roughly linearly with
-  the log of the training set size.  However, LSST10 and LSST-best have a
+  Same for \edit{LSST-best}. The improvement of AUC scales roughly linearly with
+  the log of the training set size.  However, LSST10 and \edit{LSST-best} have a
   steeper improvement with data training size.  The performance of
-  nLSST10 and nLSST-best models trained on smaller training data sets is
-  better than the respective LSST10 and LSST-best models trained on the
-  same size data, but the LSST10 and LSST-best models outperform with
+  nLSST10 and n\edit{LSST-best} models trained on smaller training data sets is
+  better than the respective LSST10 and \edit{LSST-best} models trained on the
+  same size data, but the LSST10 and \edit{LSST-best} models outperform with
   larger size training data set.}\label{fig:trainsizeLSST}
@@
 \begin{center}
-  \includegraphics[width=\columnwidth]{figures/traintime/LSST1.pdf}}
-\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for LSST-best.
-  Here, nLSST-best requires more model complexity than LSST-best.  Note, that
-  LSST-best and nLSST-best have better seeing but reduced overall signal to
+  \includegraphics[width=\columnwidth]{figures/traintime/LSST-best.pdf}}
+\caption{Same as Figure~\ref{fig:traintimeLSST10}, but for \edit{LSST-best}.
+  Here, n\edit{LSST-best} requires more model complexity than \edit{LSST-best}.  Note, that
+  \edit{LSST-best} and n\edit{LSST-best} have better seeing but reduced overall signal to
   noise than LSST10 and nLSST10.  This corresponds to better
@@
 lens-model parameter with our trained model performance, with a
-secondary and related correlation with lens galaxy velocity
-dispersion.  The more strongly lensed an image is, the larger its
-magnification, and the easier it is for our trained model to classify.
+secondary and related correlation with lens galaxy velocity dispersion
+that is encapsulated in the Einstein radius.  The more strongly lensed
+an image is, the larger its magnification, and the easier it is for
+our trained model to classify.
 
@@
 In Figure~\ref{fig:scorevslensparams}, we show the classification
-score as a function of image magnification of the source galaxy in
-each of our samples.  In the top panel, each data point is color-coded
-by the velocity dispersion of the lensing galaxy.  In the bottom
-panel, the color-coding is by the redshift of the lens galaxy.  In
-either an HST-like or LSST-like observation, lensing systems with
-images that have magnification $\gsim7$ will almost certainly be
-classified as positive with threshold scores above $\gsim0.5$.  These
-systems are also those that are most easily classified by eye.
-However, our trained model has varying performance for systems with
-lower magnifications.
+\edit{score as a function of Einstein radius and image magnification
+  of the source galaxy in each of our samples.} In either an HST-like
+or LSST-like observation, lensing systems with images that have
+magnification $\gsim7$ will almost certainly be classified as positive
+with threshold scores above $\gsim0.5$.  These systems are also those
+that are most easily classified by eye.  However, our trained model
+has varying performance for systems with lower magnifications.
 
@@
 classification threshold scores $\gsim0.5$.  These highly magnified
-systems typically have lenses that are at higher redshifts of
-$z\gsim0.5$ (lighter colors in bottom row) and/or lens galaxies with
-velocity dispersions larger than $\sigma_v\gsim230.$~km/s (darker
-colors in right figure).  Note that lensing galaxies with smaller
+systems typically have lenses that are at higher redshifts of and/or
+lens galaxies with velocity dispersions larger than
+$\sigma_v\gsim230.$~km/s.  Note that lensing galaxies with smaller
 velocity dispersions are less massive and therefore have a smaller
@@
 most relevant, and the distribution of image magnification in a data
-set will impact trained model performance.  We did not find
+set will impact trained model performance.  We did not find strong
 correlations in model performance with other lens parameters.  It is
 also useful to keep in mind that lensed galaxy images with
-magnification $\lsim5$ (e.g. slightly stretched spherical galaxies)
-are often visually indistinguishable from elliptical galaxies along
-the line of sight.
+magnification $\lsim 5$ are often visually indistinguishable from
+\edit{edge-on disk galaxies along the line of sight, which can lead to
+  false positives, features from which our model has learned to
+  downweight.  Note that the model would be more sensitive to systems
+  with lower magnification without galaxies along the line of sight.}
 
@@
     \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
-        clip]{figures/lens_parameter_dependence/HST_Magnification_Velocity_Dispersion.pdf}}\hfill
+        clip]{figures/lens_parameter_dependence/HST_Einstein_Radius_z.pdf}}\hfill
     \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
-        clip]{figures/lens_parameter_dependence/LSST10_Magnification_Velocity_Dispersion.pdf}}\hfill
+        clip]{figures/lens_parameter_dependence/LSST10_Einstein_Radius_z.pdf}}\hfill
     \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
-        clip]{figures/lens_parameter_dependence/LSST1_Magnification_Velocity_Dispersion.pdf}\hfill}
+        clip]{figures/lens_parameter_dependence/LSST-best_Einstein_Radius_z.pdf}\hfill}
   }\\ 
@@
     \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
-        clip]{figures/lens_parameter_dependence/LSST1_Magnification_z.pdf}\hfill}
+        clip]{figures/lens_parameter_dependence/LSST-best_Magnification_z.pdf}\hfill}
   }\\ 
 \caption{Left to right: Image classification score on HST, LSST10,
-  LSST-best mock observed lensing images as a function of lensed image
-  magnification.  Top row: Each panel is color coded by the lens
-  velocity dispersion in km/s.  High velocity dispersion lens galaxies
-  are likely to produce high magnification images of the source
-  galaxies.  Magnification is the strongest indicator of how likely a
-  lensing system will be successfully classified.  Bottom row: Here,
-  we color code by the redshift of the lens galaxy.}\vspace{10pt}
+  \edit{LSST-best} mock observed lensing images as a function of Einstein
+  radius (top) and magnification (bottom). Magnification is the
+  strongest indicator of how likely a lensing system will be
+  successfully classified.  The Einstein radius has a weaker
+  correlation with how easily a lensing system might be classified,
+  since it contains information on both the velocity dispersion of the
+  lens and the redshifts of the lens and source galaxies.  High
+  velocity dispersion lens galaxies are likely to produce high
+  magnification images of the source galaxies.  }\vspace{10pt}
 \label{fig:scorevslensparams}
@@
 associated with a lensed image.  Also, the redshift of the source
-galaxies have been fixed to $z_s=.2$.  We will address these
+galaxies have been fixed to $z_s=2$.  We will address these
 shortcomings in subsequent work.
@@
 % Realistic ratios
-For images selected for a massive elliptical, the number of non-lenses
+\edit{For images selected for a massive elliptical, the number of non-lenses
 will outnumber lenses by at least 1000 to 1.  Therefore, a sample that
@@
 and pure sample from our method would likely require further
-filtering, e.g. by citizen science.
+filtering, e.g. by citizen science.}
 

### 2017-04-03 ms.tex
almost done with edits to responses to co-authors

@@
   LSST-like observations are monochromatic, respectively using the
-  F606W and the g-band.} For HST-like observations, galaxies along the
-line of sight already include noise and a point spread function (PSF).
-We therefore stack and magnitude calibrate all components to produce
-the final HST-like images, which are $300\times300~{\rm pix}^2$ with
-$0.03$~arcsec per pixel.
+  F606W and the g-band.  We stack the lens galaxy, source image, and
+  galaxies along the line of sight.  While we adjust the source size
+  and magnitude to correspond to the change $D_s$ when placed at
+  $z_s$, we do not adjust colors.  The distribution of lens properties
+  is not realistic with a constant $z_s$, but provides a sufficient
+  start in covering the feature space to test supervised
+  classification methods.  Incorporating the lens, source image, line
+  of sight galaxies, and noise are particularly crucial in methods
+  that use edge features.}
+
+For HST-like observations, \edit{the stacked component for galaxies
+  along the line of sight already includes noise} and a point spread
+function (PSF).  We therefore stack and magnitude calibrate all
+components to produce the final HST-like images, which are
+$300\times300~{\rm pix}^2$ with $0.03$~arcsec per pixel.
 
@@
 sampling a smaller range of potential contaminants that are not
-associated with a lensed image.  Also, the redshift of the source
-galaxies have been fixed to $z_s=2$.  We will address these
-shortcomings in subsequent work.
+associated with a lensed image.  \edit{A limitation of the
+  CANDELS sources is that the sources are observed with HST seeing,
+  and would not resolve the clumpiness within a true HST arc.}  Also,
+the redshift of the source galaxies have been fixed to $z_s=2$.  We
+will address these shortcomings in subsequent work.
 

### 2017-04-03 replies_1.tex
almost done with edits to responses to co-authors

\documentclass{article}
%\usepackage{pdftex}
%\usepackage{epsf}
\usepackage{graphicx}
%\input epsf

% less/greater or approximately equal definitions
%\def\lesssim{\mathrel{\mathpalette\fun <}}
%\def\gtrsim{\mathrel{\mathpalette\fun >}}
%\def\lesssim{ _<\atop{^\sim}}
%\def\gtrsim{ _>\atop{^\sim}}
%\def\Msun{M$_{\odot}${\ }}
%\def\Mvir{M$_{vir}${\ }}
%\def\rvir{$r_{vir}${\ }}

\oddsidemargin 30pt
\evensidemargin 30pt
\marginparwidth 29pt
\textwidth 427pt
\headsep 0pt
\headheight 0pt
\textheight 680pt
\topmargin 0pt
\parskip 5pt
\parindent 0pt

\begin{document}

\vspace{0.5cm}

{\bf 1) Simulated sources, 2.1.3. Why are your sources all at redshift 0.2?!? that's
in front of all your lenses - so what's going on? Is that a typo for zs=2
(which would be a fair enough starting point) Otherwise sources at zs=0.2
will be much too large.}

Yes, thank you for pointing this out - it is a typo for zs=2.0.
Highlighted changes in bold.

{\bf 
2) Do you k-correct the magnitude and colours of the sources when you
change their redshifts?
}

Nan had corrected the size a magnitude of the sources corresponding to
the change in cosmological distance, Ds, as their redshifts were
adjusted to zs.  However, all simulated images are monochromatic, and
colors were not shifted.  While the distribution of lens properties
are already not realistic (e.g. constant source redshift), they
provide a sufficient start in covering feature space (los+lens+source
image galaxies) to test supervised machine learning methods and
particularly methods that use edge features.  We have altered the
first paragraph of 2.1.4 for clarity, and changes are in bold.

{\bf 
a) 'positions near the caustics' is too vague - what range of source positions
do you allow? are you focussing solely on lenses with fairly high
magnification?
}

Thank you for pointing this out.  The sources are located within a
square box centering at the center of the images (mass center as
well). The size of the box is $(-1'', 1'')\times(-1'', 1'')$ (a
$2''\times2''$ box).  This information is added in bold in 2.1.3.

We use the same auxiliary response file (ARF) and redistribution matrix file
(RMF) for both generating photon maps and in generating best fit
spectra, and have included this information in our description of both
photon map generation and spectral fitting.

{\bf 4) You should point out that the CADNELS sources are observed
  under the HST seeing, but lensing magnifies small regions. You
  therefore can't simulate the clumpiness that HST imaging of lensed
  arcs tends to show.  }

You are right on the seeing of CANDELS sources, clumpiness will not be
presented in the lensed images. and this is one shortage in the
simulation.  This has been added in bold in the discussion of caveats
in section 4.

{\bf 5) For the same reason, you do need to convolve the simulated HST
  lensed images with a HST psf, and you need to sort out the noise
  properties. The first paragraph of 2.1.4 has me very confused as to
  what you're actually doing, and if it's right or not.}

To clarify the first paragraph of 2.1.4 first, the mock images combine
four components from the field of view: lensed arcs, the lens galaxy,
galaxies along the line of sight, and noise.

Regarding the noise and PSF for the mock HST images, we extracted the
images on the line sight from Hubble Ultra Deep Field, so PSF and
noise are incorporated in the field of view of the mock HST images.

{\bf 
Note that I agree with the further analysis and conclusions that measuring
the wrong abundance will bias the temperature and density profiles in such
a way as to produce systematically wrong results in the mass and gas
fraction in the outskirts. However I am not convinced that this
mis-measurement is always present in CCD spectral analysis of the typical
cluster outskirts ICM, or that it is always mis-measured in the same sense
(i.e. abundance is always underestimated for moderate metal abundance at $\sim
1$~keV).
}

We have explained the systematic mis-measurement of the abundance as a
result of a higher-temperature component in the multi-temperature gas in
the outskirts.  We agree that the abundance will not necessarily be
biased in the same direction for a given low temperature and moderate
metal abudnace, but in our cluster's outskirts, it is the presence of
a higher temperature phase that results in a systematic
under-measurement.  This point is now reflected in the text.

{\bf 
Section 2.2.1, paragraph 1
``$3\times  R_{\rm vir}$'' $\rightarrow R_{200c}$ is used elsewhere in the manuscript so should be used
here since it is a quantitative value.
}
The projection depth is now also given in terms of ${R}_{200c}$

{\bf 
Section 2.2.2, paragraph 3
``limited flux of $\sim 3 \times 10^{-15}$~erg s$^{-1}$ cm$^{-3}$'' should be ``cm$^{-2}$'' if this
is indeed flux.
}
This is indeed flux - the units are now corrected.

{\bf 
``where we put our clusters at'' $\rightarrow$ delete ``at''
}
The clause has been reworded.
{\bf 
Section 2.2.2 (general)
please specify the abundance table used (e.g. Anders and Grevesse)
}
Yes, for both generating the flux maps and in spectral fitting. This
information has also been added.

{\bf 
Figure 1
What do the green annular sections correspond to? If nothing, they should
be removed. Also, The very small green circles projected over the bright
cluster are a bit hard to see. Finally, please comment on why there are
some blobs not rejected (e.g. just above CL6 in the x and y views, and the
extended filament). Are they just below the threshold for removal?
}

I have added information in the caption, and also the discussion of
Figure 1.  The green annular sections correspond to identified
filamentary regions with X-ray surface brightness above the average in
the whole annular bin (as described in 2.2.2, also reworded for clarity).

{\bf 
Figure 2
This figure is not reference in the text and should be somewhere in Section
2.2.3. Also, since this is a quantity calculated in bins, it would be
helpful to show uncertainties so that the importance of removing these
substructures can be judged. In the caption please specify which cluster
this corresponds to.
}

Figure has been redone with uncertainties in the ratio, and is
discussed in 2.2.3.

{\bf 
Figure 3
Caption is confusing; suggest changing the first line to ``(Left) The
projected X-ray temperature from spectral fitting and (right) the
corresponding projected 3-D density profile for CL7.'' Then lower down delete
``Right: The recovered gas density profile.''
}

Modified.

{\bf 
Figure 4
This figure has a number of issues:
1) x error bars are overlapping, so they are either drawn twice as large as
they should be or for some reason the spectral bins are not independent.
If the latter, please explain why.
2) The residual panel should be plotted as datapoints with error bars, not
solid lines. As shown, it is impossible to judge whether the residuals are
statistically significant.
3) Fitted $T_X$ values need uncertainties quoted, also to show whether the
difference is statistically significant.
4) The y-axis values are hard to believe given the units; this would imply
that there are ~ 10 billion counts in the full 2.4 Msec spectrum in just this
annulus beyond $R_{200c}$, far more than a typical (real) observation. This
is symptomatic of my concern in major issue 2(c) above, so further
clarification of how this mock observation is performed is needed.
}

I've corrected the x-errorbars, added uncertainties to the best fit
X-ray temperature, and modified the axes from $\mathrm{s^{-1}keV^{-1}}$ to
$\mathrm{keV^{-1}}$.

{\bf 
It would be illuminating to non-expert readers to show a high-resolution
spectrum of a mekal emission model at 1~keV and (e.g.) 6~keV, to show (a)
the complications in the lines in this energy range that are smeared out by
the CCD resolution, and (b) how this really matters for cluster outskirts
where kT is fairly low. This is mentioned elsewhere in the manuscript, but
a picture is worth a thousand words.
}

We have referred the reader to both Bohringer and Werner 2010 and
Mazzotta et al, 2004 for figures with spectral models.

{\bf 
Figure 5
Upper right panel: is the ``$f_{T_{X,{\rm proj}}}$'' the same sort of ``fit/fix'' mentioned
in the caption? The text in Section 3.2, paragraph 5 suggests this (also
`note the runaway parenthesis there). This needs to be clarified, perhaps
with a different label including ``fit/fix'' explicitly or some of the text
from that paragraph placed in the caption.
Lower left panel: Error bars would be very useful to judge whether the
differences are significant.
}

Errorbars have been added and the caption is clarified.

{\bf 
Section 3.2, paragraph 7 and bullet point 3 in the summary
``temperature profile...does not accurately describe the thermal
behavior at larger radii.''
I disagree; as shown in Fig 5 upper right, the data points are almost fully
consistent with the model profiles within the error bars. Again, error
bars in the lower plot would qualitatively show this.
}

While consistent with the errorbars, the shape of the best-fit
projected X-ray temperature profile does not capture the emerging
trend of the decreasing slope in the projected X-ray data.  We
interpret this as another indication of the complicated temperature
structure in cluster outskirts and have commented on this in the
section.

{\bf 
Section 3.2, paragraph 8
``... to have the statistical uncertainty...''
$\rightarrow$ ``...to have the same statistical uncertainty...''
}

Modified.

{\bf 
Section 3.2, paragraphs 9 and 11 (last)
Variations in a number of profiles are quoted, but how do these values
compare to the propagated statistical error of the measurements or inferred
values? i.e., are they significant variations?
}

I have added errorbars to the variations in X-ray temperature and
binned EMM.

{\bf 
Figure 6
This figure has the same issues as Figure 4, and they should be addressed.
}

I have made similar changes as figure 4, but adding errorbars to the
residuals for the data makes the plot rather overloaded.  As the residuals
are the difference between the mock photon spectrum and each of the
model spectra, the errors in the upper panel directly translate to
what would be in the lower panel.

{\bf 
Section 3.3, last paragraph
The effects of extrapolating the abundance to radii where it can't be
measured is a key point, because (1) essentially all Suzaku observational
studies do this, and (2) it *will* cause a bias notwithstanding my concerns
in major issue 1. I think this should be stressed more in the summary,
perhaps as a bullet point.
}

This effect has now been emphasized in the abstract, section 3.3, and
in the summary bullet points.

{\bf 
Section 3.4, paragraph 4
Should this be an abundance ``5 times lower", not "higher''? That is what
Figure 9 right suggests.
}

Yes, modified.

{\bf 
Section 3.4, paragraph 5
``...where photon statistics are poor.''Also at small radii the temperature
is quite a bit hotter, and the metal abundance becomes more separated from
temperature in the spectral fit. This should be mentioned.
}

Added.

{\bf 
Section 3.5, paragraph 3
``...but different...'' $\rightarrow$ ``...but differ...''
}

Modified.

{\bf 
Section 4, last paragraph
Footnotes for SMART-X and Athena don't appear.
}

These appear in our compilations of the manuscript, but we will ask
the journal editor to help make sure these appear in the ApJ compiled version.

\end{document}
